### 2022-05-21 paper/paper_marcel_pommer.tex
paper and first code

% SIAM Article Template
% remove review to surprass the wtermark at the end of every page
%\documentclass[review,hidelinks,onefignum,onetabnum]{siamart220329}

\documentclass[hidelinks,onefignum,onetabnum]{siamart220329}
% Information that is shared between the article and the supplement
% (title and author information, macros, packages, etc.) goes into
% ex_shared.tex. If there is no supplement, this file can be included
% directly.

\input{ex_shared}

% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={Explaining NonLinear Classification Ddecisions with Deep Taylor Decompositions an analyysis},
  pdfauthor={Marcel Pommer}
}
\fi

% The next statement enables references to information in the
% supplement. See the xr-hyperref package for details.

%\externaldocument[][nocite]{ex_supplement}

% FundRef data to be entered by SIAM
%<funding-group specific-use="FundRef">
%<award-group>
%<funding-source>
%<named-content content-type="funder-name"> 
%</named-content> 
%<named-content content-type="funder-identifier"> 
%</named-content>
%</funding-source>
%<award-id> </award-id>
%</award-group>
%</funding-group>

\begin{document}

\maketitle

% REQUIRED
\begin{abstract}
During the last decade Deep Neural Networks (DNNs) as well as other sophisticated machine learning models gained substantially on relevance, due to so far unreached performance in a variety of topics like image recognition, classification or natural language processing, to name only a few. Despite their great performance those, mostly non linear models, lack of one important aspect, the explainability of the results. Montavon et al. introduce in their paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} a new technique, the deep taylor decomposition, to map the relevance of the output on the input features, i.e. quantify the influence of each input variable on the output. They demonstrate the results on two image recognition data sets, the MNIST and the ILSVRC, creating heatmaps to display the relevance of the single pixel. I recreate the procedure in Python and apply the deep taylor decomposition to a non image recognition data set, namely the titanic dataset.
\end{abstract}

% REQUIRED
\begin{keywords}
Explainability, Deep Neural Networks, Image Recognition
\end{keywords}

% REQUIRED
\begin{MSCcodes}
62H35, 93B15
\end{MSCcodes}

\section{Introduction}
The raise of machine learning, combined with steadily growing computational power revolutionized many so far hard to graps tasks like image recognition in order to push the development of self driving cars, help to diagnose deseases or automate classification problems. One can think of a variety of different models like random forests, boosting or deep neural networks and maybe even of more applications in our daily lives, beginning with the advertisement displayed in our browser, or the netflix recommendations going to automated voice recgonition and translation to comunicate with people all over the world. Those new techniques became quite famous during the last decade due to their overperformance in nearly ever field, however due to their complexity, they are not yet fully mathematicaly explained and only few really understand those models in their full depths. This leads to one of the major drawback of those comparably new non linear models like deep neural networks. The paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} [XXX] by Montavon et al. tries to tackle this problem by extending the explainability of deep neural networks using taylor expansion. The main idea is to backpropagate the relevance of the output back to the input features. In the end, each input feature can be assigned a real valued non negative number, expressing its contribution to the output variable. The authors apply their technique to a variety of exmaples from the MNIST [XXX] dataset as well as the ILSVRC [XXX] dataset. The approach results in relevance distribution from the output variable to the input pixels, which can be graphically displayed in a heatmap, mapping relevance on pixels. In figure 1 one can see a tractable example, in which a neural network detects a `0` while distrected by a `5`. The contribution of the single neurons of (all) hidden layers to the output is independently distributed on a backward pass to the input pixels. We denote the neurons with $x_i$ and the respective contributions with $R_i$. The result is a heatmap, indicating which pixels contributed with which intensity to the decision of the neural network.
\begin{figure}[ht]
	\centering
      \includegraphics[width=1\textwidth]{images/fig._1_example}
	\caption{Example: Detecting 0 while distrecting other numbers are in place with a neural network}
	\label{fig.1}
\end{figure}
Montavon et al. focus on image recognition in their paper, but highlight, that the procedure can be broadcasted to any input space and feature set. In my analysis of the application of the algorithm I will focus on the titanic [XXX] dataset which is very tractable and easy to understand and interpret.

% The outline is not required, but we show an example here.
The paper is organized as follows. The main results are in
\ref{sec:main}, the application on a simple neural network and algorithms in  section \ref{sec:alg}, examples on the MNIST data set and experiments on the titanic dataset in section \ref{sec:exp}, and the conclusion follows in section \ref{sec:conclusions}.

\section{Main results}
\label{sec:main}

In this section I will describe the general idea of the deep taylor decomposition, present the definitions and theorems as well as some handy examples. Since the authors focus on image recognition in their analysis I will follow this methodology, however in section \ref{sec:experiments} I will transfer all results to a simple regression task. In the context of image classification, we define the d-dimensional input $x \in\mathbb{R}^d$, where the image pixels ($p$) can be represented as $x=\{x_p\}$. The function $f(x):\mathbb{R}^d \to \mathbb{R}^+$ quantifies either the probability of an object in the picture or the quantity of the object in question. This means, that a value $f(x)>0$ indicates that either the probability of the obect being in the picture is bigger than $0$ or, that at least one occurence of the object was detected. The aim of the deep taylor decomposition is to assign a relevance score $R_p(x)$ to each pixel $p$ in the input space. The relevance score quantifies the explanatory power of each pixel, i.e. the higher the relevance score the more important was the pixel for the classification. If the result is plotted in an image or to say heatmap as displayed in figure 1 the pixels which led to the classification decision are highligthed. The creation of a heatmap is only possible in the context of image recognition. If, as in section \ref{sec:experiments}, we have a classical classification problem the output is a table with the feature label and the corresponding relevance. In practice some conditions can help to further define and understand the relevance score. In the context of heatmaps, but also in other cases, the authors describe three properties.

\begin{definition}[conservative]\label{thm:conservative}
A heatmapping $R(x)$ is \underline{conservative} if the sum
of assigned relevances in the pixel space corresponds to the
total relevance detected by the model, that is
  \begin{displaymath}
    \forall x: f(x) = \sum_p R_p(x)
  \end{displaymath}
\end{definition}
In other words, the sum of the relevance of all pixels should align with the output, so the probability or quantity of the object in question. Coming back to figure 1, if the output of the neural network defines a probability of 90 \% the sum of the relevance of all pixels should be 90 \% or 0.9 as well. Definition \ref{thm:conservative} ensures that all relevance detected by the model can be explained by the input variables. There is no classification without explainability by the inputs.

\begin{definition}[positiv]\label{thm:positiv}
A heatmapping $R(x)$ is \underline{positiv} if all values
forming the heatmap are greater or equal to zero, that is:
  \begin{displaymath}
    \forall x, p: R_p(x) \geq 0
  \end{displaymath}
\end{definition}
This property ensures, that relevance cannot be negative in a sense that two pixels cancel each other out. In other words, an input feature either has a positive impact on the desicion made, or no impact at all, but there are no contradictionary evidence.\\
In the following we verify those two properties for resulting heatmaps, which is why we introduce theroem \ref{thm:consistent}, which defines a heatmap as \textit{consistent} if definition \ref{thm:conservative} and definition \ref{thm:positiv} are both fullfilles, or in other word:
\begin{definition}[consistent]\label{thm:consistent}
A heatmapping $R(x)$ is \underline{consistent} if it is \textit{conservative} \underline{and} \textit{positive}.
\end{definition}
We will use definition \ref{thm:consistent} to access the correctness of heatmaps, but it has to be mentioned that many relevance rules might confirm with the definition of \textit{consistency}, however its not a measure for the quality of the algorithm, which can be seen in the following example of a uniformly relevance over all pixels:
\begin{displaymath}
    \forall p: R_p(x) = \frac{1}{d} f(x),
\end{displaymath}
where $d$ denotes the number of pixels. Although, the heatmap will comply with definition \ref{thm:consistent} it will result in an all black image giving no further information on the relation between input and output.

\section{Algorithms}
\label{sec:alg}
The deep taylor decomposition is based on the first order taylor expansion at a root point $\tilde{x}$, such that $f(\tilde{x})=0$:
\begin{align}
    f(x)=f(\tilde{x}) + \left( \frac{\partial f}{\partial x}\big|_{x=\tilde{x}}\right)^T \cdot (x-\tilde{x}) + \epsilon
    = 0 + \sum_p \frac{\partial f}{\partial x_p}\big|_{x=\tilde{x}} \cdot (x_p-\tilde{x_p}) + \epsilon   \label{eq:taylorDecomp},
\end{align}
where the sum over all pixels derivative is defined as the redistributed relevance:
\begin{align*}
    R(x)=\frac{\partial f}{\partial x}\big|_{x=\tilde{x}} \odot (x-\tilde{x}),
\end{align*}
and $\odot$ is defined as element wise multiplication. The finding of the root point is agreat challenge an far from obvious. In figure 2 we can see a picture of the monopterus in Munich, where the root point is simply a variant of the picture where the building is blurrred.
\begin{figure}[ht]
	\centering
      \includegraphics[width=1\textwidth]{images/fig._2_example_root_point}
	\caption{Example: Root point in an image.}
	\label{fig.2}
\end{figure}
Since an image possibly can have more than one root point the choice is crucial and a good root point deviates from the original point $x$ as few as possible, i.e. minimizing the obective:
\begin{align*}
    \min_{\xi} ||\xi-x||^2 \text{ subject to } f(\xi) \text{     and   }\xi \in \mathbb{X},
\end{align*}
where $\mathbb{X}$ is the input domain.\\
Next we focus on the deep taylor decomposition, where we consider the mapping of neurons in one layer to each neuron in the next layer, assuming a relation explainable by some relevance function $R_j(\{x_i\})$. If this assumption holds and we further can identify a root point $\{\tilde{x_i}\}$ such that $R_j(\{\tilde{x_i}\}=0$ we can write equation \ref{eq:taylorDecomp}:
\begin{align*}
    \sum_j R_j= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\big|_{\{\tilde{x_i}\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}\}) + \epsilon
    = \sum_i \sum_j \frac{\partial R_j}{\partial x_i}\big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x_i}) + \epsilon
\end{align*}
If definition \ref{thm:consistent} holds, the relevances is guaranteed to be conserved in each layer, i.e. $R_f=...=\sum_j R_j=...=\sum_p R_p$ and $R_f,...,\{R_j\},...\{R_p\} \geq 0$.\\
Further I will present two different approaches, the $\omega^2$-rule and the $z$-rule.\\
As a starting point we consider a simple detection pooling neural network with a reluctified linear activation function, i.e.
\begin{align*}
x_j = \max(0, \sum_i x_iw_{i,j} + b_j)
x_k = \sum_j x_j,
\end{align*}
where $\{x_i\}$ is a d-dimensional input and $\theta = \{w_{i,j},b_j\}$ are weights and bias. Tu guarantee the exististence of a root point in the origin $b_j\leq0$. the relevance of the top layer is due to the pooling $R_k=\sum_j x_j$ and can be redistributed to the next layer according to the taylor decomposition
\begin{align*}
R_j = \frac{\partial R_k}{\partial x_j}|_{\{\tilde{x}_J\}} \cdot (x_j - \tilde{x}_j) 
\end{align*}
If either $\sum_j\tilde{x}_j=0$ and $\forall j: \tilde{x}_j \geq0$ we need to chose $\{\tilde{x}_j\}$ resulting in $R_j = x_j$, since $\\frac{\partial R_k}{\partial x_j} = 1$. Redistributing the relevance to the next layer using the taylor decomposition leads to 
\begin{align*}
R_j = \sum_j\frac{\partial R_j}{\partial x_i}|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)}) 
\end{align*}
which is the starting point for the further analysis.

\subsection{Unconstrained Input Space and $\omega^2$-Rule}
\label{sec:wRule}
If we consider an unconstrained input space one can chose the nearest root point in the Euclidean sense. Considering the rectified linear activation the intersection of the equation $\sum_i \tilde{x}_i^{(j)} w_{i,j}+b_j$ and the line of maximum descent defined by the derivative $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tw_j$, where $w_i$ ist the weight vector and $t \in \mathbb{R}$. The root point is then given by $\{\tilde{x}_i\}^{(j)} = \{x_i - \frac{w_{ij}}{\sum_i w_{ij}^2}(\sum_i x_i w_{ij}+b_j)\}$ which leads by pluggin in the propagation rule to
\begin{align*}
R_i = \sum_j\frac{w_{ij}^2}{\sum_i w_{ij}^2} R_j
\end{align*}

\begin{proposition}[w-Rule consistency]\label{prop:wconsistency}
$\forall g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent in the sense of Definition 3.
\end{proposition}

\subsection{Constrained Input Space and the z-Rules}
\label{sec:zRule}
Since in many cases the input domain is restricted like in the cae of images where usually the value of a pixel is in $[0, 255]$ it is only logical to consider a rule for bounded input spaces as well.Montavon et. al present in their paper two possible spaces, first $\mathbb{X} = \mathbb{R}_x^d$, so the space of positive but unbounded values and $\mathbb{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\}$, where $l_i$ and $h_i$ are the respective lower and higher bounds for each input feature. I will only cover the first case since logic and results are quiet similar and the domain corresponds to the rectified linear activation. Hence we already know of one root at the origin we search on the segment $(\{x_i 1_{w_{ij}<0}\},\{x_i\})$ and thus the direction of the segment is given by 
\begin{align*}
v_i^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}
\end{align*}
If we follow the same logic is in section but change the line of maximum descent to $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tx_i 1_{w_{ij}\geq0}$ we get the following relevance propagation rule
\begin{align*}
R_i = \sum_j\frac{x_i 1_{w_{ij}\geq0}}{\sum_{i´} x_{i´} 1_{w_{i´j}\geq0}} R_j
\end{align*}
\begin{proposition}[z-Rule consistency]\label{prop:zconsistency}
$\forall g \in G$, the deep Taylor decomposition with the z-rule is consistent in the sense of Definition 3.
\end{proposition}

\subsection{Deep Neural Networks}
Many neural network solutions are highly complicated and use coplex deep architectures. To also apply the rules from \ref{sec:zRule} and \ref{sec:wRule} we need to make the mapping from the higher to the lower layers, i.e. a mapping from given neurons to the relevance of a neuron in a higher layer for which the authors introduce relevance models. The Min-Max and the Training-Free relevance model are introduced in the paper, however I will only cover the first. It is defined as 
\begin{align*}
y_j = \max(0, \sum_i x_i v_{ij} + a_j)\\
\hat{R}_k = \sum_j y_j,
\end{align*}
where $a_j = min(0,\sum_lR_lv_{lj} + d_j)$ is negative bias where the sum runs over the detection neurons from the upper layer and $R_l$ are the corresponding relevances. After estimation of the paramters $\{v_{ij}, v_{lj}, d_j\}$ by minimizing $min\langle(\hat{R}_k - R_k)^2\rangle$, where $R_k$ and $\hat{R}_k$ are the trueand predicted relevance, we end up with the same problem as in section \ref{sec:main}. So we end up with the same rules and compute $R_j = y_j$ and $R_i = \sum_j \frac{q_{ij}}{\sum_{i´}q_{i´j}} R_j$, where $q_{ij} = \{v_{ij}^2, x_iv_{ij}\}$ depending on the model. In contrast to the problem before we are due to solving of the minimization problem only approximately conservative.

\section{Experiment}
\label{sec:exp}
As mentioned in the beginning the authors focus on image recognition and present examples from the MNIST and the ILSVRC data sets. I will only present one example from the MNIST data set and conclude with a self made example from the titanic data set.

\section{Conclusion}
\label{sec:conclusions}

\bibliographystyle{siamplain}
\bibliography{references}
\end{document}

### 2022-05-21 code/Neural_Network.py

@@ -1,0 +1,63 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Sun May  1 17:57:47 2022
+
+@author: Marcel Pommer
+"""
+from tensorflow.keras.callbacks import EarlyStopping
+from tensorflow.keras.layers import Dense
+from tensorflow import keras
+import tensorflow as tf
+import pandas as pd
+seed = 1864
+tf.random.set_seed(seed)
+import numpy as np
+np.random.seed(seed)
+
+class NN:
+    
+    def __init__(self, x_train, y_train):
+        self.x_train = x_train
+        self.y_train = y_train
+        
+    def fit(self, layers, neurons):
+
+        model = keras.Sequential()
+        for l in range(layers):
+            model.add(Dense(neurons[l-1], input_dim=self.x_train.shape[1], activation = "ReLU"))
+            
+        model.add(Dense(1, activation='ReLU', name='output'))
+
+        model.compile(loss="mean_squared_error", optimizer= "adam", metrics=['mean_absolute_error','mean_squared_error'])
+
+        es = EarlyStopping(monitor='val_loss', mode='min',min_delta=1e-12, patience=100, restore_best_weights=True)
+                            
+        history = model.fit(self.x_train, self.y_train, epochs=500, batch_size=1, verbose=0, validation_split=0.2, callbacks=[es])
+
+        mae = pd.DataFrame(history.history).copy()
+        
+        self.model = model
+
+    def getModel(self):
+        return self.model
+    
+    def predict(self, x):
+        prediction = self.model.predict(x)
+        
+        return prediction      
+        
+        
+    def trainResult(self):
+        train_result = self.model.predict(self.x_train).round()
+
+        train = [1 if x ==y else 0 for (x,y) in zip(train_result,self.y_train)]
+        
+        return print(sum(train)/len(train))
+
+    def testResult(self, x_test, y_test):
+        test_result = self.model.predict(x_test).round()
+
+        test = [1 if x ==y else 0 for (x,y) in zip(test_result,y_test.iloc[:,1])]
+        
+        return print(sum(test)/len(test))
+

### 2022-05-21 code/Titanic.py

@@ -1,0 +1,162 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Jan  7 10:01:11 2022
+
+@author: Marcel Pommer
+"""
+
+from sklearn.linear_model import LogisticRegression
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn.svm import SVC
+from sklearn.neural_network import MLPClassifier
+from sklearn.tree import DecisionTreeClassifier
+from sklearn.ensemble import RandomForestClassifier
+from sklearn.ensemble import GradientBoostingClassifier
+from lightgbm import LGBMClassifier
+from sklearn.preprocessing import OneHotEncoder
+from sklearn.model_selection import KFold
+import pandas as pd
+import numpy as np
+import sklearn
+import seaborn as sns
+pd.set_option('display.max_rows', 15)
+pd.set_option('display.max_columns', 15)
+pd.set_option('display.width', 200)
+pd.set_option('display.float_format', lambda x: "%.2f" % x)
+
+df_gender_submission = pd.read_csv("data/Titanic/titanic/gender_submission.csv")
+df_train = pd.read_csv("data/Titanic/titanic/train.csv")
+df_test = pd.read_csv("data/Titanic/titanic/test.csv")
+
+df_gender_submission.head()
+df_train.head()
+df_test.head()
+
+df_train_reduced = df_train.drop(labels=['Name', "Ticket", "Cabin"], axis=1)
+df_test_reduced = df_test.drop(labels=['Name', "Ticket", "Cabin"], axis=1)
+
+df_train_reduced.describe()
+
+df_train_reduced.isnull().sum()
+df_test_reduced.isnull().sum()
+
+
+ageMeanDad = int(df_train_reduced[(df_train_reduced["Survived"]==0)][[ "Age"]].mean())
+ageMeanSurvived = int(df_train_reduced[(df_train_reduced["Survived"]==1)][[ "Age"]].mean())
+df_train_reduced[["Age"]].mean()
+
+df_train_reduced[["Age"]] = df_train_reduced[["Age"]].replace(np.NaN, -1)
+df_train_reduced.loc[(df_train_reduced.Survived ==0) &(df_train_reduced.Age == -1), 'Age'] = ageMeanDad
+df_train_reduced.loc[(df_train_reduced.Survived ==1) &(df_train_reduced.Age == -1), 'Age'] = ageMeanSurvived
+
+
[…]

### 2022-05-21 code/dataReading.py

@@ -1,0 +1,92 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Sun May  1 12:10:49 2022
+
+@author: Marcel Pommer
+"""
+
+from sklearn.preprocessing import OneHotEncoder
+import pandas as pd
+import numpy as np
+from sklearn.preprocessing import StandardScaler, MinMaxScaler
+pd.set_option('display.max_rows', 15)
+pd.set_option('display.max_columns', 15)
+pd.set_option('display.width', 200)
+pd.set_option('display.float_format', lambda x: "%.2f" % x)
+
+
+def data_reading_transformation(path_url, minmaxscaler=False):
+    df_gender_submission = pd.read_csv(path_url + "/gender_submission.csv")
+    y_test = df_gender_submission
+    df_train = pd.read_csv(path_url + "/train.csv")
+    df_test = pd.read_csv(path_url + "/test.csv")
+    
+    df_train_reduced = df_train.drop(labels=['Name', "Ticket", "Cabin"], axis=1)
+    df_test_reduced = df_test.drop(labels=['Name', "Ticket", "Cabin"], axis=1)
+        
+    
+    ageMeanDad = int(df_train_reduced[(df_train_reduced["Survived"]==0)][[ "Age"]].mean())
+    ageMeanSurvived = int(df_train_reduced[(df_train_reduced["Survived"]==1)][[ "Age"]].mean())
+       
+    #!!! not performant 
+    df_train_reduced[["Age"]] = df_train_reduced[["Age"]].replace(np.NaN, -1)
+    df_train_reduced.loc[(df_train_reduced.Survived ==0) &(df_train_reduced.Age == -1), 'Age'] = ageMeanDad
+    df_train_reduced.loc[(df_train_reduced.Survived ==1) &(df_train_reduced.Age == -1), 'Age'] = ageMeanSurvived
+    
+    
+    meanAge = int(df_test_reduced.loc[(df_test_reduced.Age >0), 'Age'].mean())
+    df_test_reduced[["Age"]] = df_test_reduced[["Age"]].replace(np.NaN, meanAge)
+    
+    
+    meanFare = df_test_reduced.loc[(df_test_reduced.Fare >0), 'Fare'].mean()
+    df_test_reduced[["Fare"]] = df_test_reduced[["Fare"]].replace(np.NaN, meanFare)
+   
+    # most embarked at S, replace nan with S (southhampton)
[…]

### 2022-05-21 code/explainability_abstract_class.py

@@ -1,0 +1,74 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Sat May  7 12:52:03 2022
+
+@author: Marcel Pommer
+"""
+
+import abc 
+from abc import abstractmethod
+from tabulate import tabulate
+
+class explainability(metaclass=abc.ABCMeta):
+    
+    def __init__(self, model, result):
+        self.model = model
+        self.result = result
+        
+        
+    @abstractmethod
+    def fit(self):
+        pass
+    
+    
+    def returnModel(self):
+        return self.model
+    
+    
+    def returnResult(self):
+        return self.result
+        
+            
+    def printExplainability(self, feature_names):
+        
+        table = [["feature", "absolute relevance", "relevance in perc"]]
+        
+        relevance = self.fit()
+        result = self.returnResult()
+        for index, name in enumerate(feature_names):
+            value = [name, round(relevance[index],4), f"{round(relevance[index]/result[0], 4)*100} %"]
+            table.append(value)
+            
+        print(tabulate(table))
+            
+    def isConservative(self):
+        relevance = self.fit()
+        
+        bol = abs(sum(relevance)-self.result)<0.01
+        if bol:
+            print("The model is conservative with a threshold of 1 %")
+        else:
+            print("The model is not conservative with a threshold of 1 %")
+        
+    def isPositive(self):
+        relevance = self.fit()
+        
+        bol = (relevance >=-0.001).all()
+        if bol:
+            print("The model is positive with a threshold of 0.1 %")
+        else:
+            print("The model is not positive with a threshold of 0.1 %")
+    
+    def isConsistent(self):
+        relevance = self.fit()
+        
+        positive = (relevance >=-0.001).all()
+        conservative = abs(sum(relevance)-self.result)<0.01
+        if positive and conservative:
+            print("The model is consistent!")
+        else:
+            print("The model is not consistent!")
+    
+    
+    
+    

### 2022-05-21 code/main_execution.py

@@ -1,0 +1,64 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Sun May  1 17:50:10 2022
+
+@author: Marcel
+"""
+ 
+from dataReading import data_reading_transformation
+from omega_squared import omega_squared
+from Neural_Network import NN
+import numpy as np
+
+path = "../../../data/Titanic/titanic"
+
+minmaxscaler=True
+
+x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(path, minmaxscaler)
+
+neural_net = NN(x_train, y_train)
+
+neural_net.fit(layers = 1, neurons = [10])
+
+model = neural_net.getModel()
+
+neural_net.testResult(x_test,y_test)
+
+prediction = neural_net.predict(x_test)
+
+#%%
+
+for i in range(10):
+    if  prediction[i]>0:
+        taylor_dec = omega_squared(model, prediction[i])
+        
+        res = taylor_dec.fit()
+        
+        
+        taylor_dec.printExplainability(feature_name)
+
+
+
+
+
+
+#%%
+
+from z_rule import z_rule
+
+for i in range(10):
+    if  prediction[i]>0:
+        taylor_dec = z_rule(model, prediction[i],x_test[i])
+        
+        res = taylor_dec.fit()
+        print(res)
+        
+        # taylor_dec.printExplainability(feature_name)
+
+
+taylor_dec = z_rule(model, prediction[14],x_test[14])
+        
+res = taylor_dec.fit()
+
+
+

### 2022-05-21 code/omega_squared.py

@@ -1,0 +1,40 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Sun May  1 17:58:19 2022
+
+@author: marce
+"""
+import numpy as np
+from explainability_abstract_class import explainability
+
+class omega_squared(explainability):
+    
+    def fit(self):
+        number_layers = len(self.model.layers)
+        
+        
+        output = self.result
+        for layer in np.arange(number_layers-1, -1, -1):
+            output = self.omegaRule(output, self.model.layers[layer].weights[0].numpy())
+            
+        return output
+    
+    def omegaRule(self, R_j, weights):
+        input_relevance = []
+        
+        summe = sum(weights**2)
+        for in_neuron_index, inputs in enumerate(weights):
+            R_i = 0
+            for out_neuron_index, weight in enumerate(inputs):
+                weight_squared = weight**2
+                weight_sum = summe[out_neuron_index]
+                R_i += weight_squared/weight_sum*R_j[out_neuron_index]
+            
+            
+            input_relevance.append(R_i)
+            
+        return input_relevance
+        
+
+
+

### 2022-05-21 code/z_rule.py

@@ -1,0 +1,78 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Sat May  7 13:10:48 2022
+
+@author: Marcel Pommer
+"""
+
+import numpy as np
+from explainability_abstract_class import explainability
+from tensorflow.keras import backend as K
+
+class z_rule(explainability):
+    
+    def __init__(self, model, result, input_vector):
+        self.model = model
+        self.result = result
+        self.input_vector = input_vector
+        
+    def fit(self):
+        self.getInput_activation()
+        number_layers = len(self.model.layers)
+        
+       
+        output = self.result
+        for layer in np.arange(number_layers-1, -1, -1):
+            layer_output = self.dic[f"{layer}_layer"]
+            output = self.z_Rule(output, self.model.layers[layer].weights[0].numpy(), layer_output)
+            
+        return output
+    
+   
+    def z_Rule(self, R_j, weights,layer_output):
+        try:
+            R_j = [x[0] for x in R_j]
+        except:
+            pass
+        
+        for index in range(len(weights)):
+            weights[index]*=layer_output[index]
+            
+        sums = weights.sum(axis=1)
+
+        for index in range(len(weights)):
+            weights[index]/=sums[index]  
+            weights[np.isnan(weights)] = 0
+            weights[index]*=R_j
+        
+        output = weights.sum(axis=1)
+        
+        return output
+    
+   # def z_Rule(self, R_j, weights,layer_output):
+   #      z =  np.matmul(weights.T,layer_output)
+        
+   #      weights_times_relevenace_div_z = np.matmul(weights,R_j/z)
+        
+   #      times_layer_output = [x*y for (x,y) in zip(layer_output, weights_times_relevenace_div_z)]
+                    
+   #      return times_layer_output
+    
+    def getInput_activation(self):
+        dic = {}
+        dic["0_layer"]= self.input_vector
+        
+        input_array = self.input_vector
+        for layer in np.arange(1,len(self.model.layers)+1):
+            weights = self.model.layers[layer-1].weights[0].numpy()
+            bias = self.model.layers[layer-1].weights[1].numpy()
+            
+            output = np.matmul(input_array,weights)+bias
+            output = np.array([max(0,x) for x in output])
+            dic[f"{layer}_layer"]=output
+            
+            input_array = output
+            
+            
+        self.dic = dic
+        

### 2022-05-22 code/main_execution.py
data directory and data folder

@@ -10,7 +10,7 @@ from omega_squared import omega_squared
 from Neural_Network import NN
 import numpy as np
 
-path = "../../../data/Titanic/titanic"
+path = "data/Titanic"
 
 minmaxscaler=True
 

### 2022-05-22 code/main_execution.py
directory

@@ -10,7 +10,7 @@ from omega_squared import omega_squared
 from Neural_Network import NN
 import numpy as np
 
-path = "data/Titanic"
+path = "dataTitanic/Titanic"
 
 minmaxscaler=True
 

### 2022-05-22 paper/paper_marcel_pommer.tex
update paper

@@
 They demonstrate the results on two image recognition data sets, the MNIST and the ILSVRC, creating heatmaps to display the relevance of the single pixel.
-I recreate the procedure in Python and apply the deep taylor decomposition to a non image recognition data set, namely the titanic dataset.
+I recreate the procedure in Python and apply the deep taylor decomposition to a non image recognition data set, the titanic dataset.
 \end{abstract}
@@
 \section{Introduction}
-The raise of machine learning, combined with steadily growing computational power revolutionized many so far hard to graps tasks like image recognition in order to push the development of self driving cars, help to diagnose deseases or automate classification problems.
+The raise of machine learning, combined with steadily growing computational power revolutionized many so far hard to grasp tasks like image recognition in order to push the development of self driving cars, help to diagnose deseases or automate classification problems.
 One can think of a variety of different models like random forests, boosting or deep neural networks and maybe even of more applications in our daily lives, beginning with the advertisement displayed in our browser, or the netflix recommendations going to automated voice recgonition and translation to comunicate with people all over the world.
-Those new techniques became quite famous during the last decade due to their overperformance in nearly ever field, however due to their complexity, they are not yet fully mathematicaly explained and only few really understand those models in their full depths.
-This leads to one of the major drawback of those comparably new non linear models like deep neural networks.
+Those new techniques became quite famous during the last decade due to their overperformance in nearly ever field, however their complexity makes them mathematicaly hard to understand and explain leading to one of their major drawbacks, missing explainability.
 The paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} [XXX] by Montavon et al.
-tries to tackle this problem by extending the explainability of deep neural networks using taylor expansion.
-The main idea is to backpropagate the relevance of the output back to the input features.
-In the end, each input feature can be assigned a real valued non negative number, expressing its contribution to the output variable.
+tries to tackle this problem by extending the explainability of deep neural networks using taylor expansion, resulting in a mapping of non negative relevance from the output to each input feature.
 The authors apply their technique to a variety of exmaples from the MNIST [XXX] dataset as well as the ILSVRC [XXX] dataset.
-The approach results in relevance distribution from the output variable to the input pixels, which can be graphically displayed in a heatmap, mapping relevance on pixels.
-In figure 1 one can see a tractable example, in which a neural network detects a `0` while distrected by a `5`.
-The contribution of the single neurons of (all) hidden layers to the output is independently distributed on a backward pass to the input pixels.
-We denote the neurons with $x_i$ and the respective contributions with $R_i$.
-The result is a heatmap, indicating which pixels contributed with which intensity to the decision of the neural network.
+In figure 1 one can see a tractable example, in which a neural network detects a `0` while distracted by a `5`.
+We denote the neurons with $x_i$ and the respective contributions with $R_i$, resulting in a graphical representation, i.e.
+a heatmap, indicating which pixels contribut with which intensity to the decision of the neural network.
 \begin{figure}[ht]
 	\centering
-      \includegraphics[width=1\textwidth]{images/fig._1_example}
+      \includegraphics[width=0.5\textwidth]{images/fig._1_example}
 	\caption{Example: Detecting 0 while distrecting other numbers are in place with a neural network}
@@
 The function $f(x):\mathbb{R}^d \to \mathbb{R}^+$ quantifies either the probability of an object in the picture or the quantity of the object in question.
-This means, that a value $f(x)>0$ indicates that either the probability of the obect being in the picture is bigger than $0$ or, that at least one occurence of the object was detected.
 The aim of the deep taylor decomposition is to assign a relevance score $R_p(x)$ to each pixel $p$ in the input space.
@@
 If the result is plotted in an image or to say heatmap as displayed in figure 1 the pixels which led to the classification decision are highligthed.
-The creation of a heatmap is only possible in the context of image recognition.
-If, as in section \ref{sec:experiments}, we have a classical classification problem the output is a table with the feature label and the corresponding relevance.
 In practice some conditions can help to further define and understand the relevance score.
-In the context of heatmaps, but also in other cases, the authors describe three properties.
+In the context of heatmaps, but also in other cases, the authors state three definitions.
 
-\begin{definition}[conservative]\label{thm:conservative}
+\begin{definition}[conservative]
+\label{thm:conservative}
 A heatmapping $R(x)$ is \underline{conservative} if the sum
@@
 Definition \ref{thm:conservative} ensures that all relevance detected by the model can be explained by the input variables.
-There is no classification without explainability by the inputs.
 
-\begin{definition}[positiv]\label{thm:positiv}
+\begin{definition}[positiv]
+\label{thm:positiv}
 A heatmapping $R(x)$ is \underline{positiv} if all values
@@
 This property ensures, that relevance cannot be negative in a sense that two pixels cancel each other out.
-In other words, an input feature either has a positive impact on the desicion made, or no impact at all, but there are no contradictionary evidence.\\
-In the following we verify those two properties for resulting heatmaps, which is why we introduce theroem \ref{thm:consistent}, which defines a heatmap as \textit{consistent} if definition \ref{thm:conservative} and definition \ref{thm:positiv} are both fullfilles, or in other word:
-\begin{definition}[consistent]\label{thm:consistent}
+In other words, an input feature either has a positive impact on the desicion made, or no impact at all, but there is no contradictionary evidence.\\
+
+Since definition \ref{thm:conservative} and definition \ref{thm:positive}are of essence for the evaluation of models we further define:
+\begin{definition}[consistent]
+\label{thm:consistent}
 A heatmapping $R(x)$ is \underline{consistent} if it is \textit{conservative} \underline{and} \textit{positive}.
 \end{definition}
-We will use definition \ref{thm:consistent} to access the correctness of heatmaps, but it has to be mentioned that many relevance rules might confirm with the definition of \textit{consistency}, however its not a measure for the quality of the algorithm, which can be seen in the following example of a uniformly relevance over all pixels:
+We will use definition \ref{thm:consistent} to evaluate heatmaps, but it has to be mentioned that many relevance rules might confirm with the definition of \textit{consistency}, however its not a measure for the quality, which can be seen in the following example of a uniform relevance over all pixels:
 \begin{displaymath}
@@
     f(x)=f(\tilde{x}) + \left( \frac{\partial f}{\partial x}\big|_{x=\tilde{x}}\right)^T \cdot (x-\tilde{x}) + \epsilon
-    = 0 + \sum_p \frac{\partial f}{\partial x_p}\big|_{x=\tilde{x}} \cdot (x_p-\tilde{x_p}) + \epsilon   \label{eq:taylorDecomp},
+    = 0 + \sum_p \frac{\partial f}{\partial x_p}\big|_{x=\tilde{x}} \cdot (x_p-\tilde{x_p}) + \epsilon  
+ \label{eq:taylorDecomp},
 \end{align}
@@
 and $\odot$ is defined as element wise multiplication.
-The finding of the root point is agreat challenge an far from obvious.
+The finding of the root point is a great challenge an far from obvious.
 In figure 2 we can see a picture of the monopterus in Munich, where the root point is simply a variant of the picture where the building is blurrred.
@@
 	\centering
-      \includegraphics[width=1\textwidth]{images/fig._2_example_root_point}
+      \includegraphics[width=0.5\textwidth]{images/fig._2_example_root_point}
 	\caption{Example: Root point in an image.}
@@
 \begin{align*}
-x_j = \max(0, \sum_i x_iw_{i,j} + b_j)
-x_k = \sum_j x_j,
+x_j = \max(0, \sum_i x_iw_{i,j} + b_j),\ x_k = \sum_j x_j,
 \end{align*}
 where $\{x_i\}$ is a d-dimensional input and $\theta = \{w_{i,j},b_j\}$ are weights and bias.
-Tu guarantee the exististence of a root point in the origin $b_j\leq0$.
-the relevance of the top layer is due to the pooling $R_k=\sum_j x_j$ and can be redistributed to the next layer according to the taylor decomposition
+To guarantee the exististence of a root point in the origin $b_j\leq0$.
+The relevance of the top layer is due to the pooling $R_k=\sum_j x_j$ and can be redistributed to the next layer according to the taylor decomposition
 \begin{align*}
-R_j = \frac{\partial R_k}{\partial x_j}|_{\{\tilde{x}_J\}} \cdot (x_j - \tilde{x}_j) 
+R_j = \frac{\partial R_k}{\partial x_j}\Big|_{\{\tilde{x}_J\}} \cdot (x_j - \tilde{x}_j) 
 \end{align*}
-If either $\sum_j\tilde{x}_j=0$ and $\forall j: \tilde{x}_j \geq0$ we need to chose $\{\tilde{x}_j\}$ resulting in $R_j = x_j$, since $\\frac{\partial R_k}{\partial x_j} = 1$.
+If either $\sum_j\tilde{x}_j=0$ and $\forall j: \tilde{x}_j \geq0$ we need to chose $\{\tilde{x}_j\}$ resulting in $R_j = x_j$, since $\frac{\partial R_k}{\partial x_j} = 1$.
 Redistributing the relevance to the next layer using the taylor decomposition leads to
-\begin{align*}
-R_j = \sum_j\frac{\partial R_j}{\partial x_i}|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)}) 
-\end{align*}
+\begin{align}
+R_j = \sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)})
+\label{equ:propagationRule}
+\end{align}
 which is the starting point for the further analysis.
@@
 If we consider an unconstrained input space one can chose the nearest root point in the Euclidean sense.
-Considering the rectified linear activation the intersection of the equation $\sum_i \tilde{x}_i^{(j)} w_{i,j}+b_j$ and the line of maximum descent defined by the derivative $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tw_j$, where $w_i$ ist the weight vector and $t \in \mathbb{R}$.
-The root point is then given by $\{\tilde{x}_i\}^{(j)} = \{x_i - \frac{w_{ij}}{\sum_i w_{ij}^2}(\sum_i x_i w_{ij}+b_j)\}$ which leads by pluggin in the propagation rule to
+Considering the reluctified linear activation the intersection of the equation $\sum_i \tilde{x}_i^{(j)} w_{i,j}+b_j$ and the line of maximum descent defined by the derivative $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tw_j$, where $w_i$ ist the weight vector and $t \in \mathbb{R}$.
+The root point is then given by $\{\tilde{x}_i\}^{(j)} = \{x_i - \frac{w_{ij}}{\sum_i w_{ij}^2}(\sum_i x_i w_{ij}+b_j)\}$ which leads by pluggin in \ref{equ:propagationRule}
 \begin{align*}
@@
 
-\begin{proposition}[w-Rule consistency]\label{prop:wconsistency}
+\begin{proposition}[w-Rule consistency]
+\label{prop:wconsistency}
 $\forall g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent in the sense of Definition 3.
@@
 \label{sec:zRule}
-Since in many cases the input domain is restricted like in the cae of images where usually the value of a pixel is in $[0, 255]$ it is only logical to consider a rule for bounded input spaces as well.Montavon et.
-al present in their paper two possible spaces, first $\mathbb{X} = \mathbb{R}_x^d$, so the space of positive but unbounded values and $\mathbb{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\}$, where $l_i$ and $h_i$ are the respective lower and higher bounds for each input feature.
+Since in many cases the input domain is restricted the authors present a rule for bounded input spaces as well.
+Montavon et.
+al consider in their paper two possible spaces, first $\mathbb{X} = \mathbb{R}_x^d$ and $\mathbb{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\}$, where $l_i$ and $h_i$ are the respective lower and higher bounds for each input feature.
 I will only cover the first case since logic and results are quiet similar and the domain corresponds to the rectified linear activation.
-Hence we already know of one root at the origin we search on the segment $(\{x_i 1_{w_{ij}<0}\},\{x_i\})$ and thus the direction of the segment is given by
-\begin{align*}
-v_i^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}
-\end{align*}
+Hence we already know of the existence of one root at the origin we search on the segment $(\{x_i 1_{w_{ij}<0}\},\{x_i\})$ and thus the direction of the segment is given by $v_i^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$.
 If we follow the same logic is in section but change the line of maximum descent to $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tx_i 1_{w_{ij}\geq0}$ we get the following relevance propagation rule
@@
 \subsection{Deep Neural Networks}
-Many neural network solutions are highly complicated and use coplex deep architectures.
-To also apply the rules from \ref{sec:zRule} and \ref{sec:wRule} we need to make the mapping from the higher to the lower layers, i.e.
-a mapping from given neurons to the relevance of a neuron in a higher layer for which the authors introduce relevance models.
+Since many neural networks use complex deep architectures the authors further show a tractable way for the mapping of relevance from higher to the lower layers and introduce the concept of relevance models.
 The Min-Max and the Training-Free relevance model are introduced in the paper, however I will only cover the first.
@@
 \begin{align*}
-y_j = \max(0, \sum_i x_i v_{ij} + a_j)\\
-\hat{R}_k = \sum_j y_j,
+y_j = \max(0, \sum_i x_i v_{ij} + a_j), \text{  } \hat{R}_k = \sum_j y_j,
 \end{align*}
-where $a_j = min(0,\sum_lR_lv_{lj} + d_j)$ is negative bias where the sum runs over the detection neurons from the upper layer and $R_l$ are the corresponding relevances.
-After estimation of the paramters $\{v_{ij}, v_{lj}, d_j\}$ by minimizing $min\langle(\hat{R}_k - R_k)^2\rangle$, where $R_k$ and $\hat{R}_k$ are the trueand predicted relevance, we end up with the same problem as in section \ref{sec:main}.
-So we end up with the same rules and compute $R_j = y_j$ and $R_i = \sum_j \frac{q_{ij}}{\sum_{i´}q_{i´j}} R_j$, where $q_{ij} = \{v_{ij}^2, x_iv_{ij}\}$ depending on the model.
-In contrast to the problem before we are due to solving of the minimization problem only approximately conservative.
+where $a_j = \min(0,\sum_lR_lv_{lj} + d_j)$ is a negative bias where the sum runs over the detection neurons from the upper layer and $R_l$ are the corresponding relevances.
+After estimation of the paramters $\{v_{ij}, v_{lj}, d_j\}$ by minimizing
+\begin{align}
+min\langle(\hat{R}_k - R_k)^2\rangle 
+\label{min:relevanceModel}
+\end{align}
+, where $R_k$ and $\hat{R}_k$ are the true and predicted relevances, we end up with the same problem as in section \ref{sec:main}.
+Due to the similar structure we can apply the same computations and compute $R_j = y_j$ and $R_i = \sum_j \frac{q_{ij}}{\sum_{i´}q_{i´j}} R_j$, where $q_{ij} = \{v_{ij}^2, x_iv_{ij}\}$ for the $w^2$-rule and z-rule, respectively.
+In contrast to the problem before the resulting heatmap is only approximately conservative, due to the possible errors during the minimization of  \ref{min:relevanceModel}.
 
@@
 
+\subsection{MNIST Example}
+
+\subsection{Titanic Example}
+
 \section{Conclusion}
 \label{sec:conclusions}
+During the last years the importance of explainability of complex machine learning models became more and more present, due to either simple questions of understanding or even leag issues in for example pricing of insurances.
+Montavon et al.
+present in their paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} practical algorithms which can help to tackle the problem of interpreteability for a wide range of deep learning models.
+the authors furthermore substantiate their theory with examples on two very famous image recognition data sets, namely the MNIST and the ILSVRC data sets.
+I myself could also reproduce very reliable results on the titanic data set which is in contrast to the other two a simple supervised binary classification problem.
 

### 2022-05-28 PythonFiles/Neural_Network.py
finished paper

@@ -24,9 +24,9 @@ class NN:
 
         model = keras.Sequential()
         for l in range(layers):
-            model.add(Dense(neurons[l-1], input_dim=self.x_train.shape[1], activation = "ReLU"))
+            model.add(Dense(neurons[l], input_dim=self.x_train.shape[1], activation = "ReLU"))
             
-        model.add(Dense(1, activation='ReLU', name='output'))
+        model.add(Dense(1, activation='sigmoid', name='output'))
 
         model.compile(loss="mean_squared_error", optimizer= "adam", metrics=['mean_absolute_error','mean_squared_error'])
 

### 2022-05-28 PythonFiles/explainability_abstract_class.py

@@ -8,6 +8,7 @@ Created on Sat May  7 12:52:03 2022
 import abc 
 from abc import abstractmethod
 from tabulate import tabulate
+import numpy as np
 
 class explainability(metaclass=abc.ABCMeta):
     
@@ -30,13 +31,12 @@ class explainability(metaclass=abc.ABCMeta):
         
             
     def printExplainability(self, feature_names):
+        relevance_array = self.fit()
         
         table = [["feature", "absolute relevance", "relevance in perc"]]
-        
-        relevance = self.fit()
-        result = self.returnResult()
+
         for index, name in enumerate(feature_names):
-            value = [name, round(relevance[index],4), f"{round(relevance[index]/result[0], 4)*100} %"]
+            value = [name, round(relevance_array[index],4), f"{np.round(relevance_array[index]/self.result, 4)*100} %"]
             table.append(value)
             
         print(tabulate(table))
@@ -68,6 +68,8 @@ class explainability(metaclass=abc.ABCMeta):
             print("The model is consistent!")
         else:
             print("The model is not consistent!")
+            
+            
     
     
     

### 2022-05-28 PythonFiles/innvestigate_titanic.py

@@ -1,0 +1,67 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Thu May 26 17:20:17 2022
+
+@author: Marcel Pommer
+"""
+
+import innvestigate
+from PythonFiles.dataReading import data_reading_transformation
+from PythonFiles.omega_squared import omega_squared
+from PythonFiles.Neural_Network import NN
+import numpy as np
+import tensorflow as tf
+
+
+path = "data/titanic"
+
+minmaxscaler=True
+
+x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(path, minmaxscaler)
+
+neural_net = NN(x_train, y_train)
+
+neural_net.fit(layers = 1, neurons = [10])
+
+model = neural_net.getModel()
+
+neural_net.testResult(x_test,y_test)
+
+prediction = neural_net.predict(x_test)
+
+
+
+#%% 
+
+analyzer = innvestigate.create_analyzer("deep_taylor", model)
+
+analysis = analyzer.analyze(x_test[14])
+
+
+
+#%%
+
+import imp
+import numpy as np
+import os
+
+import keras
+import keras.backend
+import keras.models
+
+import innvestigate
+import innvestigate.utils as iutils
+
+# Use utility libraries to focus on relevant iNNvestigate routines.
+eutils = imp.load_source("utils", "../utils.py")
+mnistutils = imp.load_source("utils_mnist", "../utils_mnist.py")
+
+
+
+
+
+
+
+
+
+

### 2022-05-28 PythonFiles/main_execution.py

@@ -5,12 +5,12 @@ Created on Sun May  1 17:50:10 2022
 @author: Marcel
 """
  
-from dataReading import data_reading_transformation
-from omega_squared import omega_squared
-from Neural_Network import NN
+from PythonFiles.dataReading import data_reading_transformation
+from PythonFiles.omega_squared import omega_squared
+from PythonFiles.Neural_Network import NN
 import numpy as np
 
-path = "dataTitanic/Titanic"
+path = "data/titanic"
 
 minmaxscaler=True
 
@@ -18,7 +18,7 @@ x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(pat
 
 neural_net = NN(x_train, y_train)
 
-neural_net.fit(layers = 1, neurons = [10])
+neural_net.fit(layers = 1, neurons = [5]*5)
 
 model = neural_net.getModel()
 
@@ -28,7 +28,7 @@ prediction = neural_net.predict(x_test)
 
 #%%
 
-for i in range(10):
+for i in range(1):
     if  prediction[i]>0:
         taylor_dec = omega_squared(model, prediction[i])
         

### 2022-05-28 PythonFiles/omega_squared.py

@@ -5,7 +5,7 @@ Created on Sun May  1 17:58:19 2022
 @author: marce
 """
 import numpy as np
-from explainability_abstract_class import explainability
+from PythonFiles.explainability_abstract_class import explainability
 
 class omega_squared(explainability):
     

### 2022-05-28 PythonFiles/z_rule.py

@@ -6,7 +6,7 @@ Created on Sat May  7 13:10:48 2022
 """
 
 import numpy as np
-from explainability_abstract_class import explainability
+from PythonFiles.explainability_abstract_class import explainability
 from tensorflow.keras import backend as K
 
 class z_rule(explainability):

### 2022-05-29 Präsentation/Präsentation_23.06.2020.tex
presentation

\documentclass{beamer}
\setbeamertemplate{navigation symbols}{}
    \addtobeamertemplate{frametitle}{\vspace*{-0.1cm}}{\vspace*{-0.5cm}}

\setbeamercolor{frametitle}{fg=black,bg=white}

\usetheme{CambridgeUS}
\usepackage{ngerman}
\renewcommand{\figurename}{Figure}
\renewcommand{\tablename}{Tabel}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

\begin{document}
\title[Deep Taylor Decomposition]{Explaining NonLinear Classification Decisions with Deep Taylor Decomposition\\
analysis}  
\author{Marcel Pommer}
\institute{LMU M\"unchen}
\date{\today}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle[Explainability]{Explainability}
\begin{center}
\includegraphics[width=0.9\textwidth]{image/introduction_image}
\end{center}
\vspace{0.25cm}
Deep neural networks have great performance on a variety of problems \\
\textbf{but} how can we justify decisions made by complex deep architectures?\\
\end{frame}

\begin{frame}
\frametitle[Table of Contents]{Table of Contents}
\vspace{0.4cm}
\tableofcontents
\end{frame}

\AtBeginSection[]
{
\begin{frame}
\frametitle[Table of Contents]{Table of Contents}
\vspace{0.4cm}
\tableofcontents[currentsection]
\end{frame} 
}

\section[Introduction]{Introduction}
\begin{frame}
\frametitle{Introduction} 
\textbf{Deep neural networks revolutionized amongst others the field of}\\
\vspace{0.25cm}
       \begin{columns}[T]
          \column{0.65\textwidth}
             \centering
             \includegraphics[height=5cm, width=8cm]{image/NLP_chatbot}
           \column{0.35\textwidth}
			\begin{itemize}
			\item[--] Image recognition
			\item[--] Natural language processing
			\item[--] Human action recognition
			\item[--] Physics
			\item[--] Finance
			\item[--] ...
			\end{itemize}
         \end{columns} 
\vspace{0.5cm}
With one major drawback $\rightarrow$ \textbf{lack of transparency}
\end{frame}

\subsection[interpretable classifier]{Interpretable Classifier}
\begin{frame}
\frametitle{Interpretable Classifier} 
\vspace{0.5cm}
Explanation of non-linear classification in terms of the inputs\\
$\rightarrow$ A classifier should not only provide a result but also a reasoning

\begin{center}
\includegraphics[height=5cm, width=8cm]{image/cancer}
\end{center}

We do not only need to know if the patient has cancer but also where exactly it is located

\end{frame}

\subsection[General Idea]{General Idea}

\begin{frame}
\frametitle{General Idea} 
\vspace{0.35cm}
To accomplish the task of explainability we map relevance from the output to the input features

\vspace{0.25cm}

\begin{center}
\begin{figure}
\includegraphics[height=4.5cm, width=11cm]{image/fig._1_example}
\caption{NN detecting 0 while distrected by 5}
\end{figure}
\end{center}

\end{frame}

\section[Pixel-Wise Decomposition]{Pixel-Wise Decomposition}

\subsection[Mathematical Framework and Definitions]{Mathematical Framework and Definitions}

\begin{frame}
\frametitle{Mathematical Framework}
\vspace{0.5cm} 
In the context of image classification we define the following mathematical framework
\begin{itemize}
\item Positive valued function $f:\mathbb{R}^d\to \mathbb{R}^+$, where the output $f(x)$ defines either the probability that the object is present or the quantity of the object in question
\item[$\rightarrow$] $f(x)>0$ expresss the presence of the object  
\item Input $x \in \mathbb{R}^d$, composable in a set of pixel values $x=\{x_p\}$
\item Relevance score $R_p(x)$ indicating the relevance of each pixel
\item[$\rightarrow$] The relevance score can be displayed in a heatmap denoted by $R(x) = \{R_P(x)\}$
\end{itemize}

\begin{figure}
\includegraphics[height=2cm, width=2cm]{image/heatmap_example}
\end{figure}

\end{frame}

\begin{frame}
\frametitle{Definitions}
\begin{block}{Definition 1}
A heatmapping $R(x)$ is \underline{conservative} if the sum of assigned relevances in the pixel space corresponds to the total relevance detected by the model, that is
\begin{equation}
\forall x: f(x)=\sum_pR_p(x)
\end{equation}
\end{block}

\begin{block}{Definition 2}
A heatmapping $R(x)$ is  \underline{positive} if all values forming the heatmap are greater or equal to zero, that is:
\begin{equation}
\forall x,p: R_p(x) \geq 0
\end{equation}
\end{block}

\end{frame}

\begin{frame}
\frametitle{Definitions}
Further we test all algorithms for compliance with definition 1 and 2 why we introduce the definition of consistency which forth on is a measure of correctness of a technique\\
%\vspace{0.1cm}

\begin{block}{Definition 3}
A heatmapping $R(x)$ is  \underline{consistent} if it is  \textit{conservative} and  \textit{positive}. That is, it is consistent if it complies with Definitions 1 and 2.
\end{block}

\vspace{0.5cm}
However consistency is not a measure of quality which can be seen easily on the following example which complies with definition 3
\begin{equation*}
\forall p: R_p(x) =\frac{1}{d} \dot f(x) ,
\end{equation*}
where d denotes the number of pixels
\end{frame}

\subsection[Methodology]{Methodology}

\begin{frame}
\frametitle{Taylor Expansion}
\vspace{0.35cm}
First order taylor expansion at root point $\tilde{x}$
\begin{flalign*}
 f(x) & =f(\tilde{x}) + \left( \frac{\partial f}{\partial x}\Big|_{x=\tilde{x}}\right)^T \cdot (x-\tilde{x}) + \epsilon\\
       & = 0 + \sum_p \underbrace{\frac{\partial f}{\partial x_p}\Big|_{x=\tilde{x}} \cdot (x_p-\tilde{x_p})}_{R_p(x)} + \epsilon  
\end{flalign*}
The challenge of finding a root point
 \begin{columns}
          \begin{column}[T]{5.5cm}
             \begin{figure}
             \includegraphics[height=2.75cm, width=6cm]{image/fig._2_example_root_point}
             \end{figure}
            \end{column} 
            \begin{column}[T]{6.2cm}
			\begin{itemize}
			\item Potentially more than one root point
			\item Remove object but deviate as few as possible
			\item[$\rightarrow$] $\min_{\xi} ||\xi-x||^2 \text{ subject to } f(\xi)=0$
			\end{itemize}
	\end{column}
\end{columns}

\end{frame}

\begin{frame}
\frametitle{Sensitivity Analysis}
Choose a root point at infinitisimally small distance from the actual point, i.e. $\xi = x- \delta \frac{\partial f}{\partial x}$\\
If we assume a locally constant function we get
\begin{flalign*}
 f(x) & =f(\xi) + \left( \frac{\partial f}{\partial x}\Big|_{x=\xi}\right)^T \cdot (x- (x- \delta \frac{\partial f}{\partial x})) + 0\\
       & = f(\xi) + \delta \left( \frac{\partial f}{\partial x}\right)^T  \frac{\partial f}{\partial x} + 0\\
       & = f(\xi) + \sum_p \underbrace{ \delta \left( \frac{\partial f}{\partial x}\right)^2}_{R_p} + 0
\end{flalign*}

\begin{itemize}
\item The heatmap is positive but not conservative
\item Measure local effect
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Deep Taylor Decomposition}
\vspace{0.25cm}
\begin{figure}
\includegraphics[height=2.75cm, width=11cm]{image/deep_taylor_decomposition_example}
 \end{figure}
We view each layer as a seperate function and write the Taylor decomposition of $\sum_j R_j \text{ at } \{x_i\}$ as
\begin{align*}
    \sum_j R_j &= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\Big|_{\{\tilde{x_i}\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}\}) + \epsilon\\
    &= \sum_i \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x_i}) + \epsilon
\end{align*}

\end{frame}

\begin{frame}
\frametitle{Deep Taylor Decomposition}
\vspace{0.25cm}
\begin{figure}
\includegraphics[height=2.75cm, width=11cm]{image/deep_taylor_decomposition_example}
 \end{figure}

\begin{itemize}
\item  If each local Taylor decomposition is \textit{conservative} then the chain of equalitis is also \textit{conservative} (Layer-wise relevance conservation)
\item[$\rightarrow$] $R_f = ...= \sum_i R_i = ... = \sum_p R_p$
\item  If each local Taylor decomposition is \textit{positive} then the chain of equalitis is also \textit{positive} 
\item[$\rightarrow$] $R_f,...,\{R_i\},...,\{R_P\} \geq 0$
\item If each local Taylor decomposition is \textit{consistent} then the chain of equalitis is also \textit{consistent} 
\end{itemize}

\end{frame}

\section[One-Layer Networks]{Application to One-Layer Networks and Root Finding}

\begin{frame}
\frametitle{Setting}
\vspace{0.2cm}
Consider a simple detection-pooling one layer neural network with
 \begin{columns}
          \begin{column}[T]{5.5cm}
		\begin{align*}
		x_j &= \max(0, \sum_i x_iw_{ij} + b_j)\\
		x_k &= \sum_j x_j, \ b_j \leq 0, \forall j
		\end{align*}
            \end{column} 
            \begin{column}[T]{6.5cm}
			\begin{figure}
				\includegraphics[height=2.5cm, width=6cm]{image/one_layer_nn}
			\end{figure}
	\end{column}
\end{columns} 
\begin{enumerate}
\item $R_k = x_k$ and thus $R_k = \sum_j x_j$
\item  Chose a root point and redistribute $R_k$ on neurons $x_j$\\
$\rightarrow$ $R_j = \frac{\partial R_k}{\partial x_j}\Big|_{\{\tilde{x}_j\}} \cdot (x_j - \tilde{x}_j) $, with $\{x_j\}=0$
\item Since $\frac{\partial R}{\partial x_j}=1$ we obtain $R_j = x_j$
\item Apply Taylor decomposition another time and get\\
 $R_i = \sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)})$
\end{enumerate}

\end{frame}

\begin{frame}
\frametitle{Derivation of Propagation Rules}
Given $R_j = \max(0, \sum_i x_iw_{ij} + b_j)$ and $b_j <0$ and a search direction $\{v_i\}^{(j)}$ in the input space such that
\vspace{-0.35cm}
\begin{equation}
\{\tilde{x}\}^{(j)} = \{x_i\} + t \{v_i \} ^{(j)} \Leftrightarrow t = \frac{\tilde{x_i}^{(j)} - x_i}{v_i^{(j)}}
\label{equ:search_direction}
\end{equation}
\vspace{-0.35cm}

If the data point itself is not a root point, i.e. $\sum_i x_i w_{ij} + b_j>0$ the nearest root along $\{v_i\}^{(j)}$ is given by the intersection of equation \eqref{equ:search_direction} and $\sum_i\tilde{ x_i}^{(j)} w_{ij} + b_j=0$ which can be resolved to 
\vspace{-0.25cm}
\begin{align*}
0 &= \sum_i\{x_i\}w_{ij} + b_j + \sum_i v_i^{(j)} t \\
x_i - \tilde{x_i}^{(j)} & = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
\end{align*}

\end{frame}

\begin{frame}
\frametitle{Derivation of Propagation Rules}
\vspace{0.4cm}
Starting from the Taylor expansion we can plug in 
\begin{align*}
x_i - \tilde{x_i}^{(j)} = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
\end{align*}
\vspace{-0.2cm}
To get
\vspace{-0.2cm}
\begin{align*}
R_i & = \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i^{(j)}} \dot (x_i - \tilde{x}_i^{(j)})= \sum_j w_{ij}\frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}\\
&= \sum_j w_{ij}\frac{v_i^{(j)} w_{ij}}{\sum_i v_i^{(j)} w_{ij}} R_j \numberthis \label{equ:relevance_model}
\end{align*}

The relevance propagation rule can now easily be calculated by defining
\begin{enumerate}
	\item Define a segment with search directio $\{v_i\}^{(j)}$
	\item The line lies inside the input domain and contains a root point
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}
\end{frame}

\subsection[$w^2$-rule]{$w^2$-rule}

\begin{frame}
\frametitle{$w^2$-rule $\mathcal{X}=\mathbb{R}^d$}
Choose root point which is nearest in euclidean sense\\
\begin{enumerate}
	\item Search direction $\{v_i\}^{(j)} = w_{ij}$
	\item No domain restriction
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}

\begin{block}{$w^2$-rule}
\begin{equation*}
R_i =\sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)}) =  \sum_j\frac{w_{ij}^2}{\sum_i w_{ij}^2} R_j
\end{equation*}
\end{block}

\end{frame}

\begin{frame}
\frametitle{$w^2$-rule $\mathcal{X}=\mathbb{R}^d$}
\vspace{0.3cm}
\begin{block}{Proposition 1}
For all function $g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent.
\end{block}
\textbf{Proof}\\
\begin{enumerate}
\item \textit{Conservative}
\begin{align*}
\sum_i R_i &= \sum_i\Big(\sum_j \frac{w_{ij}^2}{\sum_iw_{ij}^2}R_j\Big)\\
   		&= \sum_j \frac{\sum_i w_{ij}^2}{\sum_iw_{ij}^2}R_j = \sum_j R_j = \sum_j x_j = f(x)
\end{align*}
\item \textit{Positive}
\begin{align*}
R_i = \sum_j \frac{w_{ij}^2}{\sum_i w_{ij}^2}R_j = \sum_j \underbrace{w_{ij}^2}_{>0}  \underbrace{\frac{1}{\sum_i w_{ij}^2}}_{>0}  \underbrace{R_j}_{\geq 0} \geq 0
\end{align*}
\end{enumerate}

\end{frame}

\subsection[$z^+$-rule]{$z^+$-rule}

\begin{frame}
\frametitle{$z^+$-rule $\mathcal{X}=\mathbb{R}_+^d$}
\vspace{0.25cm}
Search for a root point on the segment $(\{x_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathbb{R}_+^d$\\
\begin{enumerate}
	\item Search direction $\{v_i\}^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$
	\item If $\{x_i\} \in \mathbb{R}_+^d$ so is the whole domain, further for $w_{ij}^-=\min(0,w_{ij})$
	\
	\begin{align*}
		R_j(\{x_i1_{w_{ij}<0}\}) = \max(0, \sum_i x_i 1_{w_{ij}<0} w_{ij} + b_j)\\
		= \max(0, \sum_i x_i  w_{ij}^- + b_j) = 0
	\end{align*}

	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}

\begin{block}{$z^+$-rule}
\begin{equation*}
R_i =  \sum_j \frac{x_i w_{ij}^+}{\sum_{i'} x_{i'} w_{i'j}^+} R_j
\end{equation*}
\end{block}

\end{frame}

\begin{frame}
\frametitle{$z^+$-rule $\mathcal{X}=\mathbb{R}^d_+$}
\vspace{-0.4cm}
\begin{block}{Proposition 2}
For all function $g \in G$ and data points $\{x_i\} \in \mathbb{R}_+^d$, the deep Taylor decomposition with the $z^+$-rule is consistent.
\end{block}
\vspace{0.5cm}
\textbf{Proof}\\
If $\sum_i x_i w_{ij}^+ >0$ the same proof as for the $w^2$-rule applies, if $\sum_i x_i w_{ij}^+ =0$ follows that $\forall i: x_i w_{ij} \leq0$ and

\begin{align*}
 R_j = x_j = 0
\end{align*}
and there is no relevance to redistribute to the lower layers.

\end{frame}

\subsection[$z^b$-rule]{$z^b$-rule}

\begin{frame}
\frametitle{$z^b$-rule $\mathcal{X}=\mathcal{B}$}
\vspace{0.4cm}
Often we have a bounded input space $\mathcal{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\} $ and a segment $(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathcal{B}$\\
\begin{enumerate}
	\item Search direction $\{v_i\}^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$
	\item If $\{x_i\} \in \mathcal{B}$ so is the whole domain, further for $w_{ij}^-=\min(0,w_{ij})$ and $w_{ij}^+=\max(0,w_{ij})$
	\vspace{-0.25cm}
	\begin{align*}
		R_j(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\}) &= \max(0, \sum_i l_i 1_{w_{ij}>0} w_{ij} + h_i 1_{w_{ij}<0} w_{ij} + b_j)\\
		&=\max(0, \sum_i l_i w_{ij}^+ + h_i w_{ij}^- + b_j)= 0
	\end{align*}
	\vspace{-0.25cm}
	\item Inject search direction in equation \eqref{equ:relevance_model}
\end{enumerate}
\vspace{-0.25cm}

\begin{block}{$z^b$-rule}
\begin{equation*}
R_i =  \sum_j \frac{x_i w_{ij} - l_i w_{ij}^+ - h_i w_{ij}^-}{\sum_{i'} x_{i'} w_{i'j}  - l_i w_{i'j}^+ - h_i w_{i'j}^-} R_j
\end{equation*}
\end{block}

\end{frame}

\begin{frame}
\frametitle{$z^b$-rule $\mathcal{X}=\mathcal{B}$}
\vspace{-0.4cm}
\begin{block}{Proposition 3}
For all function $g \in G$ and data points $\{x_i\} \in \mathcal{B}$, the deep Taylor decomposition with the $z^b$-rule is consistent.
\end{block}
\vspace{0.5cm}
\textbf{Proof}\\
Since the proof is similar to the proofs of proposition 1 and 2 but lenghty I refer to the literature.

\end{frame}

\section[ausschlie{\ss}lich Allgemeinwohl]{Die Implementierung des PT ist unm\"oglich, wenn alle Agenten ausschlie{\ss}lich am Allgemeinwohl interessiert sind}

\section[alternatives privates Motiv]{Diskussion: Ein Vorschlag zur Umformulierung des privaten Motivs}

\subsection{Ein alternatives privates Motiv}
\begin{frame}\frametitle{Ein alternatives privates Motiv}
\vspace{-1.2cm}
\textbf{Das alternative private Motiv:} Jeder Agent ist neben dem Allgemeinwohl daran interessiert, dass sich seine Empfehlung ex post als richtig erweist.
\vspace{0.4cm}
\begin{block}{Behauptung}
Der in Kapitel drei definierte Mechanismus implementiert das PT f\"ur jedes Profil von Pr\"aferenzen, das strikt wachsend im PT und dem oben definierten privaten Motiv ist.
\end{block}

\end{frame}

\begin{frame}\frametitle{Beweis}
\vspace{0.4cm}
Der Beweis erfolgt weitestgehend analog zum Beweis von Proposition 2. Im Folgenden die Unterschiede:
\begin{itemize}
\item Es gilt $\pi_1 \geq V(1)$, aber $\pi_{2,1}<1$. Trotzdem steht das private Motiv von Agent 1 dem \"offentlichen nicht entgegen.
\item [$\rightarrow$] Agent 1 maximiert $\pi_{2,1}<1$, indem er $\pi_1$ maximiert, damit w\"ahlt er $S$ so informativ wie m\"oglich.
\item Analog zum Beweis von Proposition 2 folgt damit $S_{NT}=\varnothing$.
\item Mit Hilfslemma 1 folgt ebenfalls, dass $S_c=\varnothing$, da ein Agent durch einen Wechsel von der Strategie ``c'', zur Strategie ``T'', $\pi_{2,i}$ von $\frac{1}{2}$ auf $p$ erh\"oht.
\item Da alle Agenten $i\notin S$ ausschlie{\ss}lich daran interessiert sind, dass sich ihre Empfehlung ex post als richtig erweist, spielen sie ``T''.
\item [$\rightarrow$] Damit folgt, dass Agent 1 $S=N\setminus \{1\}$ w\"ahlt und alle Agenten in $S$ spielen ``T''. Agent 1 folgt der Mehrheit und im Fall eines Unentschieden folgt er seinem eigenen Signal.
\end{itemize}
\end{frame}

\section{Literatur}
\begin{frame}
\frametitle{Literatur}
\footnotesize{
\begin{thebibliography}{99}
\bibitem[wik]{p1} [GR98] Jacob Glazer and Ariel Rubinstein. Motives and implementation: On the design of mechanism to elicit opinions. Journal of economic Theory, 79(2):157-173, 1998.
\end{thebibliography}
}
\end{frame}

\end{document}

### 2022-06-03 Präsentation/Präsentation_23.06.2020.tex
presentation

@@
 
+\subsection[Example MINST]{Example MNIST}
+
+\begin{frame}
+\frametitle{Example MNIST: Setting}
+Training of a neural network to detect a handwritten digit between 0-3 next to a distractor digit from 4-9 given teh following setting:
+\begin{itemize}
+\item images of size 28 x 56 pixels
+\item $28 x 56 = 1568$ input neurons $\{x_i\}$, one hidden layer with 400 neurons $\{x_j\}$ and one output $x_k$
+\item weights are random initializated $\{w_{ij}\}$ and bias $\{b_j\}$ is initialized to zero and non negative during training
+\item Training with 300000 iterations of stochastic gradient descent with a bach size of 20
+\item 
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Example MNIST: Heatmaps}
+\vspace{0.5cm}
+\begin{figure}
+\includegraphics[height=2.5cm, width=12cm]{image/example_mnist_heatmap}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=3.25cm, width=12cm]{image/example_mnist_consistent}
+\vspace{-0.75cm}
+\caption{Heatmap and Empirical Results of Consistency}
+\end{figure}
+
+\end{frame}
+
+\section[Application to Deep Networks]{Application to Deep Networks}
+
+\begin{frame}
+\frametitle{Min-Max Relevance Model}
+Trainable relevnce model designed to incorporate bottom-up and top-down information
+
+\begin{align*}
+y_i &= \max(0,\sum_ix_iv_{ij} + a_j)\\
+\hat{R}_k &= \sum_j y_j,
+\end{align*}
+where $a_j = \min(0,\sum_l R_l V_{lj} + d_j)$ is a negative bias.\\
+$\rightarrow$ Compute $\{v_{ij}, v_{lj},d_j\}$ by minimizing 
+\begin{equation*}
+\min\langle (\hat{R}_k-R_k)^2) \rangle
+\end{equation*}
+\vspace{-1cm}
+\end{frame}
+
+\subsection[Relevance Model]{Relevance Model}
+
+\begin{frame}
+\frametitle{Deep Networks}
+Many problems require very complex deep architectures
+
+\begin{figure}
+\includegraphics[height=6cm, width=11cm]{image/example_deep_network_one}
+\vspace{-0.25cm}
+\caption{Example Deep Network}
+\end{figure}
+
+\vspace{-1cm}
+\end{frame}
+
 \section[ausschlie{\ss}lich Allgemeinwohl]{Die Implementierung des PT ist unm\"oglich, wenn alle Agenten ausschlie{\ss}lich am Allgemeinwohl interessiert sind}

### 2022-06-12 Präsentation/Präsentation_23.06.2020.tex
präsi

--- 2022-05-29 Präsentation/Präsentation_23.06.2020.tex
@@
 \setbeamercolor{frametitle}{fg=black,bg=white}
-
+\setbeamertemplate{caption}[numbered]
 \usetheme{CambridgeUS}
@@
 \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
+\newcommand\norm[1]{\left\lVert#1\right\rVert}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[backend=biber]{biblatex}
+\bibliography{literature_seminar.bib}
+
+% Removes icon in bibliography
+\setbeamertemplate{bibliography item}{}
 
 \begin{document}
-\title[Deep Taylor Decomposition]{Explaining NonLinear Classification Decisions with Deep Taylor Decomposition\\
-analysis}  
+\title[Deep Taylor Decomposition]{Explaining NonLinear Classification Decisions with Deep Taylor Decomposition}  
 \author{Marcel Pommer}
@@
 \frametitle[Explainability]{Explainability}
-\begin{center}
+\vspace{0.25cm}
+\begin{figure}
 \includegraphics[width=0.9\textwidth]{image/introduction_image}
-\end{center}
+\end{figure}
 \vspace{0.25cm}
-Deep neural networks have great performance on a variety of problems \\
-\textbf{but} how can we justify decisions made by complex deep architectures?\\
+Deep neural networks performe great on a variety of problems \nocite{*}\\
+\textbf{but} how can we justify decisions made by complex deep architectures?\cite{Montavon.2017b}\\
 \end{frame}
@@
 
-\subsection[interpretable classifier]{Interpretable Classifier}
 \begin{frame}
@@
 
-\subsection[General Idea]{General Idea}
-
 \begin{frame}
 \frametitle{General Idea} 
-\vspace{0.35cm}
+\vspace{0.5cm}
 To accomplish the task of explainability we map relevance from the output to the input features
@@
 \includegraphics[height=4.5cm, width=11cm]{image/fig._1_example}
-\caption{NN detecting 0 while distrected by 5}
+\caption{Neural Network Detecting 0 while Distrected by 5}
 \end{figure}
@@
 \frametitle{Mathematical Framework}
-\vspace{0.5cm} 
+
 In the context of image classification we define the following mathematical framework
@@
 \item Positive valued function $f:\mathbb{R}^d\to \mathbb{R}^+$, where the output $f(x)$ defines either the probability that the object is present or the quantity of the object in question
-\item[$\rightarrow$] $f(x)>0$ expresss the presence of the object  
+\item[$\rightarrow$] $f(x)>0$ expresses the presence of the object
+
+\end{itemize}
+
+ \begin{columns}
+          \begin{column}[T]{8cm}
+          		\begin{itemize}
           		\item Input $x \in \mathbb{R}^d$, composable in a set of pixel values $x=\{x_p\}$
@@
 
+            \end{column} 
+            \begin{column}[T]{3.5cm}
 			\begin{figure}
-\includegraphics[height=2cm, width=2cm]{image/heatmap_example}
+			\includegraphics[height=2.75cm, width=2.75cm]{image/heatmap_example}
 			\end{figure}
+	\end{column}
+\end{columns}
 
@@
 
+\vspace{0.5cm}
+
 \begin{block}{Definition 2}
@@
 \frametitle{Definitions}
-Further we test all algorithms for compliance with definition 1 and 2 why we introduce the definition of consistency which forth on is a measure of correctness of a technique\\
-%\vspace{0.1cm}
+Further we test all algorithms for compliance with definition 1 and 2 hence we introduce the definition of consistency which forth on is a measure of correctness of a technique\\
+\vspace{0.1cm}
 
@@
 \begin{equation*}
-\forall p: R_p(x) =\frac{1}{d} \dot f(x) ,
+\forall p: R_p(x) =\frac{1}{d} \cdot f(x) ,
 \end{equation*}
@@
 			\item Remove object but deviate as few as possible
-			\item[$\rightarrow$] $\min_{\xi} ||\xi-x||^2 \text{ subject to } f(\xi)=0$
+			\item[$\rightarrow$] $\min_{\xi} \norm{\xi-x}^2 \text{subject to } f(\xi)=0$
 			\end{itemize}
@@
 \frametitle{Sensitivity Analysis}
-Choose a root point at infinitisimally small distance from the actual point, i.e. $\xi = x- \delta \frac{\partial f}{\partial x}$\\
+\vspace{0.25cm}
+Root point at infinitisimally small distance from the actual point, i.e. $\xi = x- \delta \frac{\partial f}{\partial x}$, where $\delta$ is small\\
+\vspace{0.1cm}
 If we assume a locally constant function we get
@@
  f(x) & =f(\xi) + \left( \frac{\partial f}{\partial x}\Big|_{x=\xi}\right)^T \cdot (x- (x- \delta \frac{\partial f}{\partial x})) + 0\\
-       & = f(\xi) + \delta \left( \frac{\partial f}{\partial x}\right)^T  \frac{\partial f}{\partial x} + 0\\
+       & = f(\xi) + \delta \left( \frac{\partial f}{\partial x}\right)^T \cdot  \frac{\partial f}{\partial x} + 0\\
        & = f(\xi) + \sum_p \underbrace{ \delta \left( \frac{\partial f}{\partial x}\right)^2}_{R_p} + 0
@@
 \item The heatmap is positive but not conservative
-\item Measure local effect
+\item The heatmap only measures a local effect
 \end{itemize}
@@
  \end{figure}
+\vspace{0.25cm}
 We view each layer as a seperate function and write the Taylor decomposition of $\sum_j R_j \text{ at } \{x_i\}$ as
@@
     \sum_j R_j &= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\Big|_{\{\tilde{x_i}\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}\}) + \epsilon\\
-    &= \sum_i \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x_i}) + \epsilon
+    &= \sum_i \underbrace{\sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x_i})}_{R_i} + \epsilon
 \end{align*}
+\vspace{-0.25cm}
 
@@
 \begin{itemize}
-\item  If each local Taylor decomposition is \textit{conservative} then the chain of equalitis is also \textit{conservative} (Layer-wise relevance conservation)
+\item  If each local Taylor decomposition is \textit{conservative} then the chain of equalities is also \textit{conservative} (layer-wise relevance conservation)
 \item[$\rightarrow$] $R_f = ...= \sum_i R_i = ... = \sum_p R_p$
-\item  If each local Taylor decomposition is \textit{positive} then the chain of equalitis is also \textit{positive} 
+\item  If each local Taylor decomposition is \textit{positive} then the chain of equalities is also \textit{positive} 
 \item[$\rightarrow$] $R_f,...,\{R_i\},...,\{R_P\} \geq 0$
-\item If each local Taylor decomposition is \textit{consistent} then the chain of equalitis is also \textit{consistent} 
+\item If each local Taylor decomposition is \textit{consistent} then the chain of equalities is also \textit{consistent} 
 \end{itemize}
@@
 \frametitle{Setting}
-\vspace{0.2cm}
+\vspace{0.5cm}
 Consider a simple detection-pooling one layer neural network with
+\vspace{-0.2cm}
  \begin{columns}
@@
 \end{columns} 
+\vspace{0.25cm}
 \begin{enumerate}
@@
 \item  Chose a root point and redistribute $R_k$ on neurons $x_j$\\
-$\rightarrow$ $R_j = \frac{\partial R_k}{\partial x_j}\Big|_{\{\tilde{x}_j\}} \cdot (x_j - \tilde{x}_j) $, with $\{x_j\}=0$
-\item Since $\frac{\partial R}{\partial x_j}=1$ we obtain $R_j = x_j$
+$\rightarrow$ $R_j = \frac{\partial R_k}{\partial x_j}\Big|_{\{\tilde{x}_j\}} \cdot (x_j - \tilde{x}_j) $, with $\{\tilde{x}_j\}=0$
+\item Since $\frac{\partial R_k}{\partial x_j}=1$ we obtain $R_j = x_j$
 \item Apply Taylor decomposition another time and get\\
@@
 \frametitle{Derivation of Propagation Rules}
-Given $R_j = \max(0, \sum_i x_iw_{ij} + b_j)$ and $b_j <0$ and a search direction $\{v_i\}^{(j)}$ in the input space such that
-\vspace{-0.35cm}
+\vspace{0.3cm}
+Given $R_j = \max(0, \sum_i x_iw_{ij} + b_j)$ and $b_j \leq 0$ and a search direction $\{v_i\}^{(j)}$ in the input space such that
+
 \begin{equation}
-\{\tilde{x}\}^{(j)} = \{x_i\} + t \{v_i \} ^{(j)} \Leftrightarrow t = \frac{\tilde{x_i}^{(j)} - x_i}{v_i^{(j)}}
+\tilde{x}^{(j)} = x_i + t v_i ^{(j)} \Leftrightarrow t = \frac{\tilde{x_i}^{(j)} - x_i}{v_i^{(j)}}
 \label{equ:search_direction}
 \end{equation}
-\vspace{-0.35cm}
 
+\vspace{0.2cm}
 If the data point itself is not a root point, i.e.
 $\sum_i x_i w_{ij} + b_j>0$ the nearest root along $\{v_i\}^{(j)}$ is given by the intersection of equation \eqref{equ:search_direction} and $\sum_i\tilde{ x_i}^{(j)} w_{ij} + b_j=0$ which can be resolved to
-\vspace{-0.25cm}
+\vspace{-0.1cm}
 \begin{align*}
-0 &= \sum_i\{x_i\}w_{ij} + b_j + \sum_i v_i^{(j)} t \\
+0 &= \sum_i x_i w_{ij} + b_j + \sum_i v_i^{(j)} t \\
 x_i - \tilde{x_i}^{(j)} & = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
@@
 \begin{align*}
-R_i & = \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i^{(j)}} \dot (x_i - \tilde{x}_i^{(j)})= \sum_j w_{ij}\frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}\\
-&= \sum_j w_{ij}\frac{v_i^{(j)} w_{ij}}{\sum_i v_i^{(j)} w_{ij}} R_j \numberthis \label{equ:relevance_model}
+R_i & = \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)})= \sum_j w_{ij}\frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}\\
+&= \sum_j\frac{v_i^{(j)} w_{ij}}{\sum_i v_i^{(j)} w_{ij}} R_j \numberthis \label{equ:relevance_model}
 \end{align*}
 
-The relevance propagation rule can now easily be calculated by defining
+The relevance propagation rule can be calculated with the following steps
 \begin{enumerate}
-	\item Define a segment with search directio $\{v_i\}^{(j)}$
+	\item Define a segment with search direction $\{v_i\}^{(j)}$
 	\item The line lies inside the input domain and contains a root point
@@
 \frametitle{$w^2$-rule $\mathcal{X}=\mathbb{R}^d$}
-Choose root point which is nearest in euclidean sense\\
+Choose a root point which is nearest in the euclidean sense\\
+
 \begin{enumerate}
-	\item Search direction $\{v_i\}^{(j)} = w_{ij}$
+	\item Search direction $\{v_i\}^{(j)} = w_{ij}$ (gradient of $R_j$)
 	\item No domain restriction
@@
 \end{enumerate}
-
+\vspace{0.25cm}
 \begin{block}{$w^2$-rule}
 \begin{equation*}
-R_i =\sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)}) =  \sum_j\frac{w_{ij}^2}{\sum_i w_{ij}^2} R_j
+R_i =\sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)}) =  \sum_j\frac{w_{ij}^2}{\sum_{i'} w_{i'j}^2} R_j
 \end{equation*}
@@
 \begin{block}{Proposition 1}
-For all function $g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent.
+For all functions $g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent.
 \end{block}
@@
 \begin{align*}
-\sum_i R_i &= \sum_i\Big(\sum_j \frac{w_{ij}^2}{\sum_iw_{ij}^2}R_j\Big)\\
-   		&= \sum_j \frac{\sum_i w_{ij}^2}{\sum_iw_{ij}^2}R_j = \sum_j R_j = \sum_j x_j = f(x)
+\sum_i R_i &= \sum_i\Big(\sum_j \frac{w_{ij}^2}{\sum_{i'}w_{i'j}^2}R_j\Big)\\
+   		&= \sum_j \frac{\sum_i w_{ij}^2}{\sum_{i'} w_{i'j}^2}R_j = \sum_j R_j = \sum_j x_j = f(x)
 \end{align*}
@@
 \begin{align*}
-R_i = \sum_j \frac{w_{ij}^2}{\sum_i w_{ij}^2}R_j = \sum_j \underbrace{w_{ij}^2}_{>0}  \underbrace{\frac{1}{\sum_i w_{ij}^2}}_{>0}  \underbrace{R_j}_{\geq 0} \geq 0
+R_i = \sum_j \frac{w_{ij}^2}{\sum_{i'} w_{i'j}^2}R_j = \sum_j \underbrace{w_{ij}^2}_{\geq 0}  \underbrace{\frac{1}{\sum_{i'} w_{i'j}^2}}_{>0}  \underbrace{R_j}_{\geq 0} \geq 0
 \end{align*}
@@
 \begin{block}{Proposition 2}
-For all function $g \in G$ and data points $\{x_i\} \in \mathbb{R}_+^d$, the deep Taylor decomposition with the $z^+$-rule is consistent.
+For all functions $g \in G$ and data points $\{x_i\} \in \mathbb{R}_+^d$, the deep Taylor decomposition with the $z^+$-rule is consistent.
 \end{block}
@@
 \textbf{Proof}\\
-If $\sum_i x_i w_{ij}^+ >0$ the same proof as for the $w^2$-rule applies, if $\sum_i x_i w_{ij}^+ =0$ follows that $\forall i: x_i w_{ij} \leq0$ and
+If $\sum_i x_i w_{ij}^+ >0$ the same proof as for the $w^2$-rule applies, if $\sum_i x_i w_{ij}^+ =0$ it follows that $\forall i: x_i w_{ij} \leq0$ and
 
@@
 \begin{enumerate}
-	\item Search direction $\{v_i\}^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$
+	\item Search direction $\{v_i\}^{(j)} = x_i - l_i 1_{w_{ij}>0} - h_i 1_{w_{ij}<0}$
 	\item If $\{x_i\} \in \mathcal{B}$ so is the whole domain, further for $w_{ij}^-=\min(0,w_{ij})$ and $w_{ij}^+=\max(0,w_{ij})$
@@
 \end{block}
-
 \end{frame}
@@
 
-\section[ausschlie{\ss}lich Allgemeinwohl]{Die Implementierung des PT ist unm\"oglich, wenn alle Agenten ausschlie{\ss}lich am Allgemeinwohl interessiert sind}
+\subsection[Example MINST]{Example MNIST}
 
-\section[alternatives privates Motiv]{Diskussion: Ein Vorschlag zur Umformulierung des privaten Motivs}
+\begin{frame}
+\frametitle{Example MNIST: Setting}
+\vspace{0.5cm}
+Training of a neural network to detect a handwritten digit between 0-3 next to a distractor digit from 4-9 given the following setting:
+\begin{itemize}
+\item images of size 28 x 56 pixels
+\item 28 x 56 = 1568 input neurons $\{x_i\}$, one hidden layer with 400 neurons $\{x_j\}$ and one output $x_k$
+\item weights are random initialized $\{w_{ij}\}$ and bias $\{b_j\}$ is initialized to zero and non negative during training
+\item Training with 300000 iterations of stochastic gradient descent with a batch size of 20 
+\end{itemize}
+\begin{figure}
+\includegraphics[height=2.5cm, width=8cm]{image/fig._1_example}
 
-\subsection{Ein alternatives privates Motiv}
-\begin{frame}\frametitle{Ein alternatives privates Motiv}
-\vspace{-1.2cm}
-\textbf{Das alternative private Motiv:} Jeder Agent ist neben dem Allgemeinwohl daran interessiert, dass sich seine Empfehlung ex post als richtig erweist.
-\vspace{0.4cm}
-\begin{block}{Behauptung}
-Der in Kapitel drei definierte Mechanismus implementiert das PT f\"ur jedes Profil von Pr\"aferenzen, das strikt wachsend im PT und dem oben definierten privaten Motiv ist.
-\end{block}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+\frametitle{Example MNIST: Heatmaps}
+\vspace{0.5cm}
+\begin{figure}
+\includegraphics[height=2.5cm, width=12cm]{image/example_mnist_heatmap}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=3.25cm, width=12cm]{image/example_mnist_consistent}
+\vspace{-0.75cm}
+\caption{Heatmap and Empirical Results of Consistency}
+\end{figure}
 
@@
 
-\begin{frame}\frametitle{Beweis}
-\vspace{0.4cm}
-Der Beweis erfolgt weitestgehend analog zum Beweis von Proposition 2. Im Folgenden die Unterschiede:
-\begin{itemize}
-\item Es gilt $\pi_1 \geq V(1)$, aber $\pi_{2,1}<1$. Trotzdem steht das private Motiv von Agent 1 dem \"offentlichen nicht entgegen.
-\item [$\rightarrow$] Agent 1 maximiert $\pi_{2,1}<1$, indem er $\pi_1$ maximiert, damit w\"ahlt er $S$ so informativ wie m\"oglich.
-\item Analog zum Beweis von Proposition 2 folgt damit $S_{NT}=\varnothing$.
-\item Mit Hilfslemma 1 folgt ebenfalls, dass $S_c=\varnothing$, da ein Agent durch einen Wechsel von der Strategie ``c'', zur Strategie ``T'', $\pi_{2,i}$ von $\frac{1}{2}$ auf $p$ erh\"oht.
-\item Da alle Agenten $i\notin S$ ausschlie{\ss}lich daran interessiert sind, dass sich ihre Empfehlung ex post als richtig erweist, spielen sie ``T''.
-\item [$\rightarrow$] Damit folgt, dass Agent 1 $S=N\setminus \{1\}$ w\"ahlt und alle Agenten in $S$ spielen ``T''.
-Agent 1 folgt der Mehrheit und im Fall eines Unentschieden folgt er seinem eigenen Signal.
-\end{itemize}
+\section[Application to Deep Networks]{Application to Deep Networks}
+
+\begin{frame}
+\frametitle{Deep Networks}
+Many problems require very complex deep architectures
+
+\begin{figure}
+\label{fig1}
+\includegraphics[height=6cm, width=11cm]{image/example_deep_network_one}
+\vspace{-0.25cm}
+\caption{Example Deep Network}
+
+\end{figure}
+
+\vspace{-1cm}
 \end{frame}
 
-\section{Literatur}
 \begin{frame}
-\frametitle{Literatur}
-\footnotesize{
-\begin{thebibliography}{99}
-\bibitem[wik]{p1} [GR98] Jacob Glazer and Ariel Rubinstein. Motives and implementation: On the design of mechanism to elicit opinions. Journal of economic Theory, 79(2):157-173, 1998.
-\end{thebibliography}
-}
+\frametitle{Relevance Model}
+\vspace{0.25cm}
+In deep architectures as in figure 3 a mapping between two layers may be unknown, even if it exists
+\begin{block}{Definition 1}
+A relevance model is a function that maps a set of neuron activations at a given layer to the relevance of a neuron in a higher layer, and whose output can be redistributed onto its input variables.
+\end{block}
+
+\begin{figure}
+\label{fig1}
+\includegraphics[height=4cm, width=7.75cm]{image/example_deep_network_one}
+\end{figure}
+\vspace{-0.5cm}
+\end{frame}
+
+\begin{frame}
+\frametitle{Min-Max Relevance Model}
+\vspace{0.4cm}
+Trainable relevance model designed to incorporate bottom-up and top-down information
+\begin{align*}
+y_i &= \max(0,\sum_ix_iv_{ij} + a_j)\\
+\hat{R}_k &= \sum_j y_j,
+\end{align*}
+where $a_j = \min(0,\sum_l R_l v_{lj} + d_j)$ is a negative bias
+\vspace{-0.25cm}
+
+ \begin{columns}
+          \begin{column}{5cm}
+          		$\rightarrow$ Compute $\{v_{ij}, v_{lj},d_j\}$ by minimizing 
+			\begin{equation*}
+			\min\langle (\hat{R}_k-R_k)^2) \rangle
+			\end{equation*}
+            \end{column} 
+            \begin{column}{6cm}
+			\begin{figure}
+			\label{fig1}
+			\includegraphics[height=3cm, width=6.5cm]{image/min_max_relevance_model}
+			\end{figure}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Min-Max Relevance Model}
+Due to the similar structure we can apply the propagation rules for the one-layer neural network
+\begin{itemize}
+\item Pooling layer
+\begin{equation*}
+R_j = y_j
+\end{equation*}
+
+\item Detection layer
+\begin{equation*}
+R_i = \sum_j \frac{q_{ij}}{\sum_{i'} q_{i'j}} R_j
+\end{equation*}
+where $q_{ij}= v_{ij}^2$, $q_{ij}= x_i v_{ij}^+$ or $q_{ij}= x_i v_{ij} - l_i v_{ij}^+ - h_i v_{ij}^-$ for the $w^2$-rule, $z^+$-rule and the $z^b$- rule respectively
+\end{itemize}
+\vspace{0.5cm}
+
+$\rightarrow$ The Min-Max relevance model is due to the minimization only approximately consistent
+\end{frame}
+
+\begin{frame}
+\frametitle{Training-Free Relevance Model}
+Consider the original network structure
+\begin{align*}
+x_j &= \max(0,\sum_ix_i w_{ij} + b_j)\\
+x_k &= \norm{\{x_j\}}_p
+\end{align*}
+If the upper layer was explained by the $z^+$-rule, relevance $R_k$ can be written as
+
+ \begin{columns}
+          \begin{column}{5cm}
+			\begin{align*}
+			R_k &= \sum_l \frac{x_k w_{kl}^+}{\sum_{k'} x_{k'} w_{k'l}^+} R_l\\
+			R_k &= (\sum_j x_j) \cdot \frac{\norm{\{x_j\}}_p}{\norm{\{x_j\}}_1}   \sum_l \frac{w_{kl}^+R_l}{\sum_{k'} x_{k'} w_{k'l}^+} 
+			\end{align*}
+            \end{column} 
+            \begin{column}{5cm}
+			\begin{figure}
+			\label{fig1}
+			\includegraphics[height=3cm, width=4cm]{image/training-free_relevance_model_3}
+			\end{figure}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Training-Free Relevance Model}
+\vspace{0.25cm}
+As before we can apply the propagation rules for the one-layer neural network
+\begin{itemize}
+\item Pooling layer
+\begin{equation*}
+R_j = \frac{x_j}{\sum_{j'} x_{j'}}R_k
+\end{equation*}
+
+\item Detection layer
+\begin{equation*}
+R_i = \sum_j \frac{q_{ij}}{\sum_{i'} q_{i'j}} R_j
+\end{equation*}
+where $q_{ij}= v_{ij}^2$, $q_{ij}= x_i v_{ij}^+$ or $q_{ij}= x_i v_{ij} - l_i v_{ij}^+ - h_i v_{ij}^-$ for the $w^2$-rule, $z^+$-rule and the $z^b$- rule respectively
+\end{itemize}
+\vspace{0.1cm}
+$\rightarrow$ The training-free relevance model is consistent\\
+
+\vspace{0.5cm}
+When using the training-free model for the whole network all but the first layer need to be decomposed using the $z^+$-rule
+\end{frame}
+
+\section{Python Programming Example}
+
+\begin{frame}
+\frametitle{Relevance Distribution on the Titanic Dataset}
+\vspace{0.5cm}
+\begin{figure}
+\includegraphics[height=5cm, width=11cm]{image/kaggle_titanic_challenge}
+\end{figure}
+\vspace{0.25cm}
+\url{https://github.com/mpommer/Deep-Taylor-Decomposition-Python}
+\end{frame}
+
+\begin{frame}[allowframebreaks]
+\frametitle{References}
+% This prints the bibliography on the slide
+\printbibliography
 \end{frame}

### 2022-06-12 PythonFiles/Neural_Network.py

@@ -14,6 +14,27 @@ tf.random.set_seed(seed)
 import numpy as np
 np.random.seed(seed)
 
+
+class NonNeg(tf.keras.constraints.Constraint):
+  """Constrains weight tensors to be centered around `ref_value`."""
+
+  def __init__(self):
+      pass
+  def __call__(self, w):
+      
+     w = tf.cast(w < 0, w.dtype) * w
+     return w
+ 
+    
+    # if w[0]<0:
+    #     return w
+    # else:
+    #     return 0
+
+  def get_config(self):
+    return {'ref_value': self.ref_value}
+
+
 class NN:
     
     def __init__(self, x_train, y_train):
@@ -24,7 +45,7 @@ class NN:
 
         model = keras.Sequential()
         for l in range(layers):
-            model.add(Dense(neurons[l], input_dim=self.x_train.shape[1], activation = "ReLU"))
+            model.add(Dense(neurons[l], input_dim=self.x_train.shape[1], activation = "ReLU", bias_constraint=NonNeg()))
             
         model.add(Dense(1, activation='sigmoid', name='output'))
 
@@ -60,4 +81,7 @@ class NN:
         test = [1 if x ==y else 0 for (x,y) in zip(test_result,y_test.iloc[:,1])]
         
         return print(sum(test)/len(test))
+
+
+
 

### 2022-06-12 PythonFiles/main_execution.py

@@ -7,6 +7,9 @@ Created on Sun May  1 17:50:10 2022
  
 from PythonFiles.dataReading import data_reading_transformation
 from PythonFiles.omega_squared import omega_squared
+from PythonFiles.z_rule import z_rule 
+from PythonFiles.z_plusrule import z_plusrule 
+
 from PythonFiles.Neural_Network import NN
 import numpy as np
 
@@ -18,7 +21,7 @@ x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(pat
 
 neural_net = NN(x_train, y_train)
 
-neural_net.fit(layers = 1, neurons = [5]*5)
+neural_net.fit(layers = 1, neurons = [25]*1)
 
 model = neural_net.getModel()
 
@@ -26,39 +29,46 @@ neural_net.testResult(x_test,y_test)
 
 prediction = neural_net.predict(x_test)
 
+t = model.layers[0].weights[0].numpy()
+
+#%% omega ^2- rule
+
+taylor_dec = omega_squared(model, prediction[0])
+        
+res = taylor_dec.fit()
+        
+        
+taylor_dec.printExplainability(feature_name)
+
+
+
+
+
+
 #%%
 
-for i in range(1):
-    if  prediction[i]>0:
-        taylor_dec = omega_squared(model, prediction[i])
-        
-        res = taylor_dec.fit()
-        
-        
-        taylor_dec.printExplainability(feature_name)
 
-
-
-
-
-
-#%%
-
-from z_rule import z_rule
-
-for i in range(10):
+for i in range(5):
     if  prediction[i]>0:
         taylor_dec = z_rule(model, prediction[i],x_test[i])
         
         res = taylor_dec.fit()
         print(res)
         
-        # taylor_dec.printExplainability(feature_name)
+        taylor_dec.printExplainability(feature_name)
 
+#%%
 
 taylor_dec = z_rule(model, prediction[14],x_test[14])
         
 res = taylor_dec.fit()
 
+taylor_dec.printExplainability(feature_name)
 
+#%%
+taylor_dec = z_plusrule(model, prediction[14],x_test[14])
+        
+res = taylor_dec.fit()
+
+taylor_dec.printExplainability(feature_name)
 

### 2022-06-12 PythonFiles/test_file.py

@@ -1,0 +1,12 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Sat Jun 11 18:06:19 2022
+
+@author: marce
+"""
+
+x = 5
+y= 10
+
+print(x+y)
+

### 2022-06-12 PythonFiles/z_plusrule.py

@@ -1,5 +1,12 @@
 # -*- coding: utf-8 -*-
 """
+Created on Sat Jun 11 17:49:28 2022
+
+@author: marce
+"""
+
+# -*- coding: utf-8 -*-
+"""
 Created on Sat May  7 13:10:48 2022
 
 @author: Marcel Pommer
@@ -9,7 +16,7 @@ import numpy as np
 from PythonFiles.explainability_abstract_class import explainability
 from tensorflow.keras import backend as K
 
-class z_rule(explainability):
+class z_plusrule(explainability):
     
     def __init__(self, model, result, input_vector):
         self.model = model
@@ -51,6 +58,7 @@ class z_rule(explainability):
     
     def z_Rule(self, R_j, weights,layer_output):
         
+        weights[weights<0] = 0
         z =  np.matmul(weights.T,layer_output)
         
         weights_times_relevenace_div_z = np.matmul(weights,R_j/z)

### 2022-06-14 paper/paper_marcel_pommer.tex
paper review

@@
 
-\documentclass[hidelinks,onefignum,onetabnum]{siamart220329}
+\documentclass[review,hidelinks,onefignum,onetabnum]{siamart220329}
 % Information that is shared between the article and the supplement
@@
 \hypersetup{
-  pdftitle={Explaining NonLinear Classification Ddecisions with Deep Taylor Decompositions an analyysis},
+  pdftitle={Explaining NonLinear Classification Ddecisions with Deep Taylor Decompositions},
   pdfauthor={Marcel Pommer}
@@
 
+\setlength{\abovedisplayskip}{4pt}
+\setlength{\belowdisplayskip}{4pt}
+\setlength{\abovedisplayshortskip}{4pt}
+\setlength{\belowdisplayshortskip}{4pt}
+
 \maketitle
@@
 \begin{abstract}
-During the last decade Deep Neural Networks (DNNs) as well as other sophisticated machine learning models gained substantially on relevance, due to so far unreached performance in a variety of topics like image recognition, classification or natural language processing, to name only a few.
-Despite their great performance those, mostly non linear models, lack of one important aspect, the explainability of the results.
+During the last decade Deep Neural Networks (DNNs) as well as other sophisticated machine learning models gained substantially on relevance, due to so far unreached performance in a variety of topics like image recognition, finance or natural language processing, to name only a few.
+Despite their great performance, those, mostly non linear models, lack of one important aspect, the explainability of the results.
 Montavon et al.
-introduce in their paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} a new technique, the deep taylor decomposition, to map the relevance of the output on the input features, i.e.
+introduce in their paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} \cite{Montavon.2017b} a new technique, the deep taylor decomposition, to map the relevance of the output on the input features, i.e.
 quantify the influence of each input variable on the output.
-They demonstrate the results on two image recognition data sets, the MNIST and the ILSVRC, creating heatmaps to display the relevance of the single pixel.
-I recreate the procedure in Python and apply the deep taylor decomposition to a non image recognition data set, the titanic dataset.
+They demonstrate the results on two image recognition data sets, the MNIST \cite{lecun2010mnist} and the ILSVRC \cite{Russakovsky.2015}, creating heatmaps to display the relevance of each single pixel.
+I recreate the procedure in Python and apply the deep taylor decomposition to the titanic dataset \cite{Eaton.1998}.
 \end{abstract}
@@
 \section{Introduction}
-The raise of machine learning, combined with steadily growing computational power revolutionized many so far hard to grasp tasks like image recognition in order to push the development of self driving cars, help to diagnose deseases or automate classification problems.
-One can think of a variety of different models like random forests, boosting or deep neural networks and maybe even of more applications in our daily lives, beginning with the advertisement displayed in our browser, or the netflix recommendations going to automated voice recgonition and translation to comunicate with people all over the world.
-Those new techniques became quite famous during the last decade due to their overperformance in nearly ever field, however their complexity makes them mathematicaly hard to understand and explain leading to one of their major drawbacks, missing explainability.
-The paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} [XXX] by Montavon et al.
-tries to tackle this problem by extending the explainability of deep neural networks using taylor expansion, resulting in a mapping of non negative relevance from the output to each input feature.
-The authors apply their technique to a variety of exmaples from the MNIST [XXX] dataset as well as the ILSVRC [XXX] dataset.
-In figure 1 one can see a tractable example, in which a neural network detects a `0` while distracted by a `5`.
+The raise of machine learning, combined with steadily growing computational power revolutionized many so far hard to grasp tasks like image recognition and are highly used in countless areas like self driving cars and diagnoses of deseases.
+Those new techniques became quite famous during the last decade due to their overperformance in nearly every field, however their complexity makes them mathematicaly hard to understand and explain, leading to one of their major drawbacks, missing explainability.
+The paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} \cite{Montavon.2017b} by Montavon et al.
+tries to tackle this problem by extending the explainability of deep neural networks using taylor expansion, resulting in a mapping of non negative relevance from the output to each input features.
+The authors apply their technique to a variety of examples from the MNIST \cite{lecun2010mnist} dataset as well as the ILSVRC \cite{Russakovsky.2015} dataset.
+figure \ref{fig.1} shows a tractable example, in which a neural network detects a `0` while distracted by a `5`.
 We denote the neurons with $x_i$ and the respective contributions with $R_i$, resulting in a graphical representation, i.e.
@@
 \begin{figure}[ht]
+	\vspace{-0.25cm}
 	\centering
       \includegraphics[width=0.5\textwidth]{images/fig._1_example}
-	\caption{Example: Detecting 0 while distrecting other numbers are in place with a neural network}
+	\caption{Example: Detecting 0 with distrecting numbers with a neural network}
 	\label{fig.1}
 \end{figure}
+\vspace{-0.35cm}
 Montavon et al.
-focus on image recognition in their paper, but highlight, that the procedure can be broadcasted to any input space and feature set.
-In my analysis of the application of the algorithm I will focus on the titanic [XXX] dataset which is very tractable and easy to understand and interpret.
+focus on image recognition, but highlight, that the procedure can be broadcasted to any input space and feature set.
+In my analysis of the application of the algorithm I will focus on the titanic \cite{Eaton.1998} dataset which is very tractable and easy to understand and interpret.
 
 % The outline is not required, but we show an example here.
-The paper is organized as follows. The main results are in
-\ref{sec:main}, the application on a simple neural network and algorithms in  section \ref{sec:alg}, examples on the MNIST data set and experiments on the titanic dataset in section \ref{sec:exp}, and the conclusion follows in section \ref{sec:conclusions}.
+%The paper is organized as follows.
+The main results are in \ref{sec:main}, the application on a simple neural network and algorithms in  section \ref{sec:alg}, examples on the MNIST data set and experiments on the titanic dataset in section \ref{sec:exp}, and the conclusion follows in section \ref{sec:conclusions}.
 
@@
 \label{sec:main}
-
-In this section I will describe the general idea of the deep taylor decomposition, present the definitions and theorems as well as some handy examples.
-Since the authors focus on image recognition in their analysis I will follow this methodology, however in section \ref{sec:experiments} I will transfer all results to a simple regression task.
-In the context of image classification, we define the d-dimensional input $x \in\mathbb{R}^d$, where the image pixels ($p$) can be represented as $x=\{x_p\}$.
+The main section summarizes the general idea and presents the definitions and theorems while focusing on image recognition and following the metodology of Montavon et al.
+In the context of image classification, we define a d-dimensional input space $x \in\mathbb{R}^d$, where the image pixels ($p$) can be represented as $x=\{x_p\}$.
 The function $f(x):\mathbb{R}^d \to \mathbb{R}^+$ quantifies either the probability of an object in the picture or the quantity of the object in question.
@@
 total relevance detected by the model, that is
+  \vspace{-0.1cm}
   \begin{displaymath}
@@
 \end{definition}
-In other words, the sum of the relevance of all pixels should align with the output, so the probability or quantity of the object in question.
-Coming back to figure 1, if the output of the neural network defines a probability of 90 \% the sum of the relevance of all pixels should be 90 \% or 0.9 as well.
+  \vspace{-0.1cm}
+In other words, the sum of the relevance of all pixels should align with the output.
 Definition \ref{thm:conservative} ensures that all relevance detected by the model can be explained by the input variables.
 
-\begin{definition}[positiv]
-\label{thm:positiv}
-A heatmapping $R(x)$ is \underline{positiv} if all values
+\begin{definition}[positive]
+\label{thm:positive}
+A heatmapping $R(x)$ is \underline{positive} if all values
 forming the heatmap are greater or equal to zero, that is:
+  \vspace{-0.1cm}
   \begin{displaymath}
@@
 \end{definition}
-This property ensures, that relevance cannot be negative in a sense that two pixels cancel each other out.
-In other words, an input feature either has a positive impact on the desicion made, or no impact at all, but there is no contradictionary evidence.\\
-
-Since definition \ref{thm:conservative} and definition \ref{thm:positive}are of essence for the evaluation of models we further define:
+\vspace{-0.15cm}
+This property ensures, that relevance cannot be negative in the sense that two pixels cancel each other out.
+Since definition \ref{thm:conservative} and definition \ref{thm:positive} are of essence for the evaluation of models we further define:
 \begin{definition}[consistent]
@@
 \end{definition}
-We will use definition \ref{thm:consistent} to evaluate heatmaps, but it has to be mentioned that many relevance rules might confirm with the definition of \textit{consistency}, however its not a measure for the quality, which can be seen in the following example of a uniform relevance over all pixels:
-\begin{displaymath}
-    \forall p: R_p(x) = \frac{1}{d} f(x),
-\end{displaymath}
-where $d$ denotes the number of pixels.
-Although, the heatmap will comply with definition \ref{thm:consistent} it will result in an all black image giving no further information on the relation between input and output.
+We will use definition \ref{thm:consistent} to evaluate heatmaps, however consistency is not necessarily a measure of quality, which can be seen in the following example of a uniform relevance over all $d$ pixels where $\forall p: R_p(x) = \frac{1}{d} f(x)$.
+Although, the heatmap will comply with definition \ref{thm:consistent} it will result in an all black/grey image providing no further information on the relation between input and output.
 
@@
 \begin{align}
-    f(x)=f(\tilde{x}) + \left( \frac{\partial f}{\partial x}\big|_{x=\tilde{x}}\right)^T \cdot (x-\tilde{x}) + \epsilon
-    = 0 + \sum_p \frac{\partial f}{\partial x_p}\big|_{x=\tilde{x}} \cdot (x_p-\tilde{x_p}) + \epsilon  
+    f(x)=f(\tilde{x}) + \left( \frac{\partial f}{\partial x}\Big|_{x=\tilde{x}}\right)^T \cdot (x-\tilde{x}) + \epsilon
+    = 0 + \sum_p \frac{\partial f}{\partial x_p}\Big|_{x=\tilde{x}} \cdot (x_p-\tilde{x_p}) + \epsilon  
  \label{eq:taylorDecomp},
@@
 \begin{align*}
-    R(x)=\frac{\partial f}{\partial x}\big|_{x=\tilde{x}} \odot (x-\tilde{x}),
+    R(x)=\frac{\partial f}{\partial x}\Big|_{x=\tilde{x}} \odot (x-\tilde{x}),
 \end{align*}
 and $\odot$ is defined as element wise multiplication.
-The finding of the root point is a great challenge an far from obvious.
-In figure 2 we can see a picture of the monopterus in Munich, where the root point is simply a variant of the picture where the building is blurrred.
+The finding of the root point is a great challenge and far from obvious.
+In figure 2 we can see an image, where the root point is simply a variant of the picture where the building is blurrred.
 \begin{figure}[ht]
@@
 	\label{fig.2}
+	\vspace{-0.5cm}
 \end{figure}
@@
 \begin{align*}
-    \min_{\xi} ||\xi-x||^2 \text{ subject to } f(\xi) \text{     and   }\xi \in \mathbb{X},
+    \min_{\xi} ||\xi-x||^2 \text{ subject to } f(\xi)=0 \text{     and   }\xi \in \mathbb{X},
+    \vspace{-0.1cm}
 \end{align*}
 where $\mathbb{X}$ is the input domain.\\
+
 Next we focus on the deep taylor decomposition, where we consider the mapping of neurons in one layer to each neuron in the next layer, assuming a relation explainable by some relevance function $R_j(\{x_i\})$.
-If this assumption holds and we further can identify a root point $\{\tilde{x_i}\}$ such that $R_j(\{\tilde{x_i}\}=0$ we can write equation \ref{eq:taylorDecomp}:
+If this assumption holds and we further can identify a root point $\{\tilde{x_i}\}$ such that $R_j(\{\tilde{x_i}\})=0$ we can write equation \ref{eq:taylorDecomp}:
 \begin{align*}
-    \sum_j R_j= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\big|_{\{\tilde{x_i}\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}\}) + \epsilon
-    = \sum_i \sum_j \frac{\partial R_j}{\partial x_i}\big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x_i}) + \epsilon
+    \sum_j R_j= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\Big|_{\{\tilde{x_i}\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}\}) + \epsilon
+    = \sum_i \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x_i}) + \epsilon
 \end{align*}
 If definition \ref{thm:consistent} holds, the relevances is guaranteed to be conserved in each layer, i.e. $R_f=...=\sum_j R_j=...=\sum_p R_p$ and $R_f,...,\{R_j\},...\{R_p\} \geq 0$.\\
-Further I will present two different approaches, the $\omega^2$-rule and the $z$-rule.\\
-As a starting point we consider a simple detection pooling neural network with a reluctified linear activation function, i.e.
+
+Further I will present two different approaches, the $\omega^2$-rule and the $z$-rule.
+As a starting point we consider a simple detection pooling neural network with a rectified linear activation function, i.e.
 \begin{align*}
-x_j = \max(0, \sum_i x_iw_{i,j} + b_j),\ x_k = \sum_j x_j,
+x_j = \max(0, \sum_i x_iw_{ij} + b_j),\ x_k = \sum_j x_j,
 \end{align*}
-where $\{x_i\}$ is a d-dimensional input and $\theta = \{w_{i,j},b_j\}$ are weights and bias.
-To guarantee the exististence of a root point in the origin $b_j\leq0$.
+where $\{x_i\}$ is a d-dimensional input and $\theta = \{w_{ij},b_j\}$ are weights and bias.
+To guarantee the exististence of a root point in the origin we restrict $b_j\leq0$.
 The relevance of the top layer is due to the pooling $R_k=\sum_j x_j$ and can be redistributed to the next layer according to the taylor decomposition
 \begin{align*}
-R_j = \frac{\partial R_k}{\partial x_j}\Big|_{\{\tilde{x}_J\}} \cdot (x_j - \tilde{x}_j) 
+R_j = \frac{\partial R_k}{\partial x_j}\Big|_{\{\tilde{x}_j\}} \cdot (x_j - \tilde{x}_j) 
 \end{align*}
@@
 \begin{align}
-R_j = \sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)})
+R_i = \sum_j\frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i\}^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)})
 \label{equ:propagationRule}
@@
 If we consider an unconstrained input space one can chose the nearest root point in the Euclidean sense.
-Considering the reluctified linear activation the intersection of the equation $\sum_i \tilde{x}_i^{(j)} w_{i,j}+b_j$ and the line of maximum descent defined by the derivative $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tw_j$, where $w_i$ ist the weight vector and $t \in \mathbb{R}$.
-The root point is then given by $\{\tilde{x}_i\}^{(j)} = \{x_i - \frac{w_{ij}}{\sum_i w_{ij}^2}(\sum_i x_i w_{ij}+b_j)\}$ which leads by pluggin in \ref{equ:propagationRule}
+Considering the rectified linear activation the intersection of the equation $\sum_i \tilde{x}_i^{(j)} w_{i,j}+b_j$ and the line of maximum descent defined by the derivative $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tw_j$, where $w_i$ ist the weight vector and $t \in \mathbb{R}$ define the nearest root point which is then given by $\{\tilde{x}_i\}^{(j)} = \{x_i - \frac{w_{ij}}{\sum_i w_{ij}^2}(\sum_i x_i w_{ij}+b_j)\}$.
+Pluggin in equation \ref{equ:propagationRule} leads to
 \begin{align*}
@@
 
-\begin{proposition}[w-Rule consistency]
+\begin{proposition}[$w^2$-Rule consistency]
 \label{prop:wconsistency}
-$\forall g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent in the sense of Definition 3.
+$\forall g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent in the sense of definition 3.
 \end{proposition}
@@
 Since in many cases the input domain is restricted the authors present a rule for bounded input spaces as well.
-Montavon et.
-al consider in their paper two possible spaces, first $\mathbb{X} = \mathbb{R}_x^d$ and $\mathbb{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\}$, where $l_i$ and $h_i$ are the respective lower and higher bounds for each input feature.
+Montavon et al.
+consider $\mathcal{X} = \mathbb{R}_x^d$ and $\mathcal{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\}$, where $l_i$ and $h_i$ are the respective lower and higher bounds for each input feature.
 I will only cover the first case since logic and results are quiet similar and the domain corresponds to the rectified linear activation.
 Hence we already know of the existence of one root at the origin we search on the segment $(\{x_i 1_{w_{ij}<0}\},\{x_i\})$ and thus the direction of the segment is given by $v_i^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$.
-If we follow the same logic is in section but change the line of maximum descent to $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tx_i 1_{w_{ij}\geq0}$ we get the following relevance propagation rule
+If we follow the same logic as in section \ref{sec:wRule} but adjust the line of maximum descent to $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tx_i 1_{w_{ij}\geq0}$ we get the following relevance propagation rule
 \begin{align*}
@@
 \end{align*}
-\begin{proposition}[z-Rule consistency]\label{prop:zconsistency}
+\begin{proposition}[$z$-Rule consistency]\label{prop:zconsistency}
 $\forall g \in G$, the deep Taylor decomposition with the z-rule is consistent in the sense of Definition 3.
@@
 \subsection{Deep Neural Networks}
-Since many neural networks use complex deep architectures the authors further show a tractable way for the mapping of relevance from higher to the lower layers and introduce the concept of relevance models.
+\label{sec:deepNeuralNetworks}
+Since many neural networks use complex deep architectures the authors further show a tractable way for the mapping of relevance from higher to the lower layers if the mapping is not explicit and introduce the concept of relevance models.
 The Min-Max and the Training-Free relevance model are introduced in the paper, however I will only cover the first.
@@
 After estimation of the paramters $\{v_{ij}, v_{lj}, d_j\}$ by minimizing
-\begin{align}
+\begin{equation}
 min\langle(\hat{R}_k - R_k)^2\rangle 
 \label{min:relevanceModel}
-\end{align}
+\end{equation}
 , where $R_k$ and $\hat{R}_k$ are the true and predicted relevances, we end up with the same problem as in section \ref{sec:main}.
-Due to the similar structure we can apply the same computations and compute $R_j = y_j$ and $R_i = \sum_j \frac{q_{ij}}{\sum_{i´}q_{i´j}} R_j$, where $q_{ij} = \{v_{ij}^2, x_iv_{ij}\}$ for the $w^2$-rule and z-rule, respectively.
+Due to the similar structure we can apply the same computations and compute $R_j = y_j$ and $R_i = \sum_j \frac{q_{ij}}{\sum_{i´}q_{i´j}} R_j$, where $q_{ij} = \{w_{ij}^2, x_i w_{ij}1_{w_{ij}>0}\}$ for the $w^2$-rule and $z^+$-rule, respectively.
 In contrast to the problem before the resulting heatmap is only approximately conservative, due to the possible errors during the minimization of  \ref{min:relevanceModel}.
@@
 \label{sec:exp}
-As mentioned in the beginning the authors focus on image recognition and present examples from the MNIST and the ILSVRC data sets.
-I will only present one example from the MNIST data set and conclude with a self made example from the titanic data set.
+As mentioned in the beginning the authors focus on image recognition and present examples from the MNIST \cite{lecun2010mnist} and the ILSVRC \cite{Russakovsky.2015} data sets.
+I will only present one example from the MNIST \cite{lecun2010mnist} data set and conclude with a self made example from the titanic \cite{Eaton.1998} data set.
 
 \subsection{MNIST Example}
+Figure \ref{fig.1} shows how the proposed algorithms can detect pixels with a high relevance for detecting a `0` next to a distracting number.
+Montavon et all show several examples of other numbers as in figure \ref{fig.3} and compare several methods.
+It can be seen that the heatmap clearly identifies the important pixels, i.e.
+correctly assigns relevance to areas where the digit is located.
+Further analysis shows, that especially the $w^2$- and $z$-rule are conservative and positive an thus satisfy the condition for definition \ref{thm:consistent}.
+\begin{figure}[ht]
+	\centering
+      \includegraphics[width=0.75\textwidth]{images/fig._3_MNIST}
+	\caption{Example: Detecting 0 with distrecting other numbers present.}
+	\label{fig.3}
+\end{figure}
+%\vspace{-0.25cm}
 
 \subsection{Titanic Example}
+Neural networks are not only used for image recognition but for a variety of problems like the prominent titanic survival classification which I chose for my personal analysis.
+I build a simple neural network with one hidden layer and 10 neurons resulting in a accuracy of 80 \%.
+Table 1 summarizes the results and clearly shows, that features like sex and age have greater influence on the survival probability than features like the pasenger ID or the port of embarkation.\footnote{Code can be found on: \url{https://github.com/mpommer/Deep-Taylor-Decomposition-Python}}
+
+\begin{table}[h!]
+\centering
+\caption{Relevance of titanic input features}
+\label{table_1}
+\begin{tabular}{ |c||c|c|c|c| }
+
+ \hline 
+  feature & sex& age & parch & passenger id\\
+ \hline
+ relevance in \% & 10 & 10 & 10 & 10\\
+ \hline
+\end{tabular}
+
+\end{table}
 
@@
 \label{sec:conclusions}
-During the last years the importance of explainability of complex machine learning models became more and more present, due to either simple questions of understanding or even leag issues in for example pricing of insurances.
+During the last years the importance of explainability of complex machine learning models became more and more present, due to either simple questions of understanding or even legal issues in for example pricing of insurances.
 Montavon et al.
-present in their paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} practical algorithms which can help to tackle the problem of interpreteability for a wide range of deep learning models.
-the authors furthermore substantiate their theory with examples on two very famous image recognition data sets, namely the MNIST and the ILSVRC data sets.
-I myself could also reproduce very reliable results on the titanic data set which is in contrast to the other two a simple supervised binary classification problem.
+present in their paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} \cite{Montavon.2017b} practical algorithms which can help to tackle the problem of interpreteability for a wide range of deep learning models.
+The authors furthermore substantiate their theory with examples on two very famous image recognition data sets, namely the MNIST \cite{lecun2010mnist} and the ILSVRC \cite{Russakovsky.2015} data sets.
+I myself could also reproduce very reliable results on the titanic \cite{Eaton.1998} data set.
 
 \bibliographystyle{siamplain}
-\bibliography{references}
+\bibliography{literature_seminar}
 \end{document}

### 2022-06-19 Präsentation/Präsentation_23.06.2020.tex
code and presentation finished

@@
 \begin{document}
-\title[Deep Taylor Decomposition]{Explaining NonLinear Classification Decisions with Deep Taylor Decomposition}  
+\title[Deep Taylor Decomposition]{Explaining NonLinear Classification Decisions with Deep Taylor Decomposition by Montavon et al.}  
 \author{Marcel Pommer}
-\institute{LMU M\"unchen}
+\institute[LMU M\"unchen]{Ludwig-Maximilians-Universität M\"unchen}
 \date{\today}
@@
 \vspace{0.25cm}
-Deep neural networks performe great on a variety of problems \nocite{*}\\
-\textbf{but} how can we justify decisions made by complex deep architectures?\cite{Montavon.2017b}\\
+Deep neural networks perform great on a variety of problems \nocite{*}\\
+\textbf{but} how can we justify decisions made by complex deep architectures?\\
 \end{frame}
@@
 
+\iffalse
+
 \begin{frame}
@@
 \vspace{0.5cm}
-Explanation of non-linear classification in terms of the inputs\\
+Explanation of non-linear classifiers\\
 $\rightarrow$ A classifier should not only provide a result but also a reasoning
@@
 \end{frame}
+
+\fi
 
@@
 \includegraphics[height=4.5cm, width=11cm]{image/fig._1_example}
-\caption{Neural Network Detecting 0 while Distrected by 5}
+\caption{Neural Network Detecting 0 while Distracted by 5}
 \end{figure}
@@
           		\begin{itemize}
-          		\item Input $x \in \mathbb{R}^d$, composable in a set of pixel values $x=\{x_p\}$
+          		\item Input $x \in \mathbb{R}^d$, decomposable in a set of pixel values $x=\{x_p\}$
 			\item Relevance score $R_p(x)$ indicating the relevance of each pixel
-			\item[$\rightarrow$] The relevance score can be displayed in a heatmap denoted by $R(x) = \{R_P(x)\}$
+			\item[$\rightarrow$] The relevance score can be displayed in a heatmap denoted by $R(x) = \{R_p(x)\}$
 			\end{itemize}
@@
 \begin{equation}
-\forall x: f(x)=\sum_pR_p(x)
+\forall x: f(x)=\sum_p R_p(x)
 \end{equation}
@@
 \vspace{0.5cm}
-
+\pause
 \begin{block}{Definition 2}
@@
 \frametitle{Definitions}
-Further we test all algorithms for compliance with definition 1 and 2 hence we introduce the definition of consistency which forth on is a measure of correctness of a technique\\
+All algorithms are shall comply with definition 1 and 2\\
 \vspace{0.1cm}
@@
 \vspace{0.5cm}
-However consistency is not a measure of quality which can be seen easily on the following example which complies with definition 3
+
+\pause
+But consistency is not a measure of quality which can be seen on the following example which complies with definition 3
 \begin{equation*}
@@
 \vspace{0.35cm}
-First order taylor expansion at root point $\tilde{x}$
+First order Taylor expansion at root point $\tilde{x}$
 \begin{flalign*}
  f(x) & =f(\tilde{x}) + \left( \frac{\partial f}{\partial x}\Big|_{x=\tilde{x}}\right)^T \cdot (x-\tilde{x}) + \epsilon\\
-       & = 0 + \sum_p \underbrace{\frac{\partial f}{\partial x_p}\Big|_{x=\tilde{x}} \cdot (x_p-\tilde{x_p})}_{R_p(x)} + \epsilon  
+       & = 0 + \sum_p \underbrace{\frac{\partial f}{\partial x_p}\Big|_{x=\tilde{x}} \cdot (x_p-\tilde{x}_p)}_{R_p(x)} +\  \epsilon  
 \end{flalign*}
+
+\pause
 The challenge of finding a root point
@@
 \vspace{0.25cm}
-Root point at infinitisimally small distance from the actual point, i.e. $\xi = x- \delta \frac{\partial f}{\partial x}$, where $\delta$ is small\\
+Root point at infinitesimally small distance from the actual point, i.e. $\xi = x- \delta \frac{\partial f}{\partial x}$, where $\delta$ is small\\
+\pause
 \vspace{0.1cm}
@@
        & = f(\xi) + \delta \left( \frac{\partial f}{\partial x}\right)^T \cdot  \frac{\partial f}{\partial x} + 0\\
-       & = f(\xi) + \sum_p \underbrace{ \delta \left( \frac{\partial f}{\partial x}\right)^2}_{R_p} + 0
+       & = f(\xi) + \sum_p \underbrace{ \delta \left( \frac{\partial f}{\partial x}\right)^2}_{R_p} +\ 0
 \end{flalign*}
 
+\pause
 \begin{itemize}
@@
 \vspace{0.25cm}
-We view each layer as a seperate function and write the Taylor decomposition of $\sum_j R_j \text{ at } \{x_i\}$ as
+
+\pause
+We view each layer as a separate function and write the Taylor decomposition of $\sum_j R_j \text{ at } \{x_i\}$ as
 \begin{align*}
-    \sum_j R_j &= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\Big|_{\{\tilde{x_i}\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}\}) + \epsilon\\
-    &= \sum_i \underbrace{\sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x_i})}_{R_i} + \epsilon
+    \sum_j R_j &= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\Big|_{\{\tilde{x}_i\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}_i\}) + \epsilon\\
+    &= \sum_i \underbrace{\sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\tilde{x}_i} \cdot (x_i-\tilde{x}_i)}_{R_i} +\ \epsilon
 \end{align*}
@@
 \item  If each local Taylor decomposition is \textit{positive} then the chain of equalities is also \textit{positive} 
-\item[$\rightarrow$] $R_f,...,\{R_i\},...,\{R_P\} \geq 0$
+\item[$\rightarrow$] $R_f,...,\{R_i\},...,\{R_p\} \geq 0$
 \item If each local Taylor decomposition is \textit{consistent} then the chain of equalities is also \textit{consistent} 
@@
 \vspace{0.5cm}
+
 Consider a simple detection-pooling one layer neural network with
@@
 		\begin{align*}
-		x_j &= \max(0, \sum_i x_iw_{ij} + b_j)\\
+		x_j &= \max(0, \sum_i x_i w_{ij} + b_j)\\
 		x_k &= \sum_j x_j, \ b_j \leq 0, \forall j
@@
 \vspace{0.25cm}
+
+\pause
 \begin{enumerate}
@@
 $\rightarrow$ $R_j = \frac{\partial R_k}{\partial x_j}\Big|_{\{\tilde{x}_j\}} \cdot (x_j - \tilde{x}_j) $, with $\{\tilde{x}_j\}=0$
-\item Since $\frac{\partial R_k}{\partial x_j}=1$ we obtain $R_j = x_j$
+\item Since $\frac{\partial R_k}{\partial x_j}\Big|_{\{\tilde{x}_j\}}=1$ we obtain $R_j = x_j$
 \item Apply Taylor decomposition another time and get\\
@@
 \vspace{0.3cm}
-Given $R_j = \max(0, \sum_i x_iw_{ij} + b_j)$ and $b_j \leq 0$ and a search direction $\{v_i\}^{(j)}$ in the input space such that
+Given $R_j = \max(0, \sum_i x_i w_{ij} + b_j)$ and $b_j \leq 0$ and a search direction $\{v_i\}^{(j)}$ in the input space such that
 
 \begin{equation}
-\tilde{x}^{(j)} = x_i + t v_i ^{(j)} \Leftrightarrow t = \frac{\tilde{x_i}^{(j)} - x_i}{v_i^{(j)}}
+\tilde{x}^{(j)}_i = x_i + t v_i ^{(j)} \Leftrightarrow t = \frac{\tilde{x}_i^{(j)} - x_i}{v_i^{(j)}}
 \label{equ:search_direction}
@@
 If the data point itself is not a root point, i.e.
-$\sum_i x_i w_{ij} + b_j>0$ the nearest root along $\{v_i\}^{(j)}$ is given by the intersection of equation \eqref{equ:search_direction} and $\sum_i\tilde{ x_i}^{(j)} w_{ij} + b_j=0$ which can be resolved to
+$\sum_i x_i w_{ij} + b_j>0$ the nearest root along $\{v_i\}^{(j)}$ is given by the intersection of equation \eqref{equ:search_direction} and $\sum_i\tilde{x}_i^{(j)} w_{ij} + b_j=0$ which can be resolved to
 \vspace{-0.1cm}
 \begin{align*}
-0 &= \sum_i x_i w_{ij} + b_j + \sum_i v_i^{(j)} t \\
-x_i - \tilde{x_i}^{(j)} & = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
+0 &= \sum_i x_i w_{ij} + b_j + \sum_i v_i^{(j)} t w_{ij} \\
+x_i - \tilde{x}_i^{(j)} & = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
 \end{align*}
@@
 \begin{align*}
-x_i - \tilde{x_i}^{(j)} = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
+x_i - \tilde{x}_i^{(j)} = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
 \end{align*}
@@
 \begin{align*}
-R_i & = \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i^{(j)}} \cdot (x_i - \tilde{x}_i^{(j)})= \sum_j w_{ij}\frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}\\
+R_i & = \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}_i^{(j)}\}} \cdot (x_i - \tilde{x}_i^{(j)})= \sum_j w_{ij}\frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}\\
 &= \sum_j\frac{v_i^{(j)} w_{ij}}{\sum_i v_i^{(j)} w_{ij}} R_j \numberthis \label{equ:relevance_model}
@@
 
+\pause
 The relevance propagation rule can be calculated with the following steps
@@
 
-\subsection[$w^2$-rule]{$w^2$-rule}
+\subsection[$\omega^2$-rule]{$\omega^2$-rule}
 
 \begin{frame}
-\frametitle{$w^2$-rule $\mathcal{X}=\mathbb{R}^d$}
+\frametitle{$\omega^2$-rule $\mathcal{X}=\mathbb{R}^d$}
+\vspace{0.35cm}
 Choose a root point which is nearest in the euclidean sense\\
@@
 	\item Search direction $\{v_i\}^{(j)} = w_{ij}$ (gradient of $R_j$)
-	\item No domain restriction
+	\item No domain restriction and for $\tilde{x}_i^{(j)} = x_i - \frac{R_j}{\sum_{i'}w_{i'j}^2}$
+	\begin{align*}
+		R_j(\tilde{x}) &= \max(0, \sum_i (x_i -\frac{R_j}{\sum_{i'}w_{i'j}^2}) w_{ij}  + b_j) \\
+		&= \max(0, \underbrace{\sum_i (x_i w_{ij} + b_j)}_{=R_j} - R_j \underbrace{\frac{\sum_{i}w_{ij}^2}{\sum_{i'}w_{i'j}^2}}_{=1} )= 0 
+	\end{align*}
+	\vspace{-0.1cm}
 	\item Inject search direction in equation \eqref{equ:relevance_model}
 \end{enumerate}
-\vspace{0.25cm}
-\begin{block}{$w^2$-rule}
+
+\pause
+\vspace{-0.15cm}
+\begin{block}{$\omega^2$-rule}
 \begin{equation*}
@@
 \begin{block}{Proposition 1}
-For all functions $g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent.
+For all functions $g \in G$, the deep Taylor decomposition with the $\omega^2$-rule is consistent.
 \end{block}
+\pause
 \textbf{Proof}\\
@@
 \item \textit{Conservative}
+\vspace{-0.2cm}
 \begin{align*}
 \sum_i R_i &= \sum_i\Big(\sum_j \frac{w_{ij}^2}{\sum_{i'}w_{i'j}^2}R_j\Big)\\
-   		&= \sum_j \frac{\sum_i w_{ij}^2}{\sum_{i'} w_{i'j}^2}R_j = \sum_j R_j = \sum_j x_j = f(x)
+   		&= \sum_j \underbrace{\frac{\sum_i w_{ij}^2}{\sum_{i'} w_{i'j}^2}}_{=1}R_j = \sum_j R_j = \sum_j x_j = f(x)
 \end{align*}
+\vspace{-0.5cm}
 \item \textit{Positive}
@@
 \frametitle{$z^+$-rule $\mathcal{X}=\mathbb{R}_+^d$}
-\vspace{0.25cm}
+\vspace{0.5cm}
 Search for a root point on the segment $(\{x_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathbb{R}_+^d$\\
@@
 	\begin{align*}
-		R_j(\{x_i1_{w_{ij}<0}\}) = \max(0, \sum_i x_i 1_{w_{ij}<0} w_{ij} + b_j)\\
-		= \max(0, \sum_i x_i  w_{ij}^- + b_j) = 0
+		R_j(\{x_i1_{w_{ij}<0}\}) =& \max(0, \sum_i x_i 1_{w_{ij}<0} w_{ij} + b_j)\\
+		=& \max(0, \underbrace{\sum_i x_i  w_{ij}^-}_{\leq 0} +\ b_j) = 0
 	\end{align*}
-
+	\vspace{-0.25cm}
 	\item Inject search direction in equation \eqref{equ:relevance_model}
@@
 
+\pause
 \begin{block}{$z^+$-rule}
@@
 \frametitle{$z^+$-rule $\mathcal{X}=\mathbb{R}^d_+$}
-\vspace{-0.4cm}
+
 \begin{block}{Proposition 2}
@@
 \vspace{0.5cm}
+
+\pause
 \textbf{Proof}\\
@@
 \begin{align*}
- R_j = x_j = 0
+ R_j = x_j = \max(0,\underbrace{\sum_i x_i w_{ij}}_{\leq 0} +\ b_j) = 0
 \end{align*}
@@
 \vspace{0.4cm}
-Often we have a bounded input space $\mathcal{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\} $ and a segment $(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathcal{B}$\\
+Given a bounded input space $\mathcal{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\} $, with $l_i \leq 0$ and $ h_i \geq 0$ and we chose the segment $(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathcal{B}$\\
 \begin{enumerate}
 	\item Search direction $\{v_i\}^{(j)} = x_i - l_i 1_{w_{ij}>0} - h_i 1_{w_{ij}<0}$
-	\item If $\{x_i\} \in \mathcal{B}$ so is the whole domain, further for $w_{ij}^-=\min(0,w_{ij})$ and $w_{ij}^+=\max(0,w_{ij})$
+	\item If $\{x_i\} \in \mathcal{B}$ so is the whole domain and for $w_{ij}^-=\min(0,w_{ij})$, $w_{ij}^+=\max(0,w_{ij})$
 	\vspace{-0.25cm}
@@
 		R_j(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\}) &= \max(0, \sum_i l_i 1_{w_{ij}>0} w_{ij} + h_i 1_{w_{ij}<0} w_{ij} + b_j)\\
-		&=\max(0, \sum_i l_i w_{ij}^+ + h_i w_{ij}^- + b_j)= 0
+		&=\max(0, \sum_i \underbrace{l_i w_{ij}^+}_{\leq 0} + \underbrace{h_i w_{ij}^-}_{\leq 0} + b_j)= 0
 	\end{align*}
-	\vspace{-0.25cm}
+	\vspace{-0.75cm}
 	\item Inject search direction in equation \eqref{equ:relevance_model}
 \end{enumerate}
-\vspace{-0.25cm}
 
+\pause
+\vspace{-0.15cm}
 \begin{block}{$z^b$-rule}
@@
 \textbf{Proof}\\
-Since the proof is similar to the proofs of proposition 1 and 2 but lenghty I refer to the literature.
+Since the proof is similar to the proofs of proposition 1 and 2 but lengthy I refer to the literature.
 
@@
 \vspace{0.5cm}
-Training of a neural network to detect a handwritten digit between 0-3 next to a distractor digit from 4-9 given the following setting:
+Training of a neural network to detect a handwritten digit between 0-3 next to a distracting digit from 4-9 given the following setting:
 \begin{itemize}
-\item images of size 28 x 56 pixels
-\item 28 x 56 = 1568 input neurons $\{x_i\}$, one hidden layer with 400 neurons $\{x_j\}$ and one output $x_k$
-\item weights are random initialized $\{w_{ij}\}$ and bias $\{b_j\}$ is initialized to zero and non negative during training
+\item Images of size 28 x 56 pixels and 1568 input neurons $\{x_i\}$
+\item One hidden layer with 400 neurons $\{x_j\}$ and one output $x_k$
+\item Random initialized weights $\{w_{ij}\}$ and non-negative bias $\{b_j\}$ initialized to zero
 \item Training with 300000 iterations of stochastic gradient descent with a batch size of 20 
@@
 
+\iffalse
 \begin{frame}
@@
 \end{frame}
+\fi
 
@@
 \vspace{0.4cm}
-Trainable relevance model designed to incorporate bottom-up and top-down information
+Trainable relevance model defined as
 \begin{align*}
-y_i &= \max(0,\sum_ix_iv_{ij} + a_j)\\
+y_j &= \max(0,\sum_ix_iv_{ij} + a_j)\\
 \hat{R}_k &= \sum_j y_j,
@@
 			R_k &= \sum_l \frac{x_k w_{kl}^+}{\sum_{k'} x_{k'} w_{k'l}^+} R_l\\
-			R_k &= (\sum_j x_j) \cdot \frac{\norm{\{x_j\}}_p}{\norm{\{x_j\}}_1}   \sum_l \frac{w_{kl}^+R_l}{\sum_{k'} x_{k'} w_{k'l}^+} 
+				&= (\sum_j x_j) \cdot \frac{\norm{\{x_j\}}_p}{\norm{\{x_j\}}_1}   \sum_l \frac{w_{kl}^+R_l}{\sum_{k'} x_{k'} w_{k'l}^+} 
 			\end{align*}

### 2022-06-19 paper/paper_marcel_pommer.tex
code and presentation finished

@@
 
+\usepackage{wrapfig}
+\usepackage{caption} 
+\captionsetup[table]{skip=1pt}
 \input{ex_shared}
@@
 \hypersetup{
-  pdftitle={Explaining NonLinear Classification Ddecisions with Deep Taylor Decompositions},
+  pdftitle={Explaining NonLinear Classification Decisions with Deep Taylor Decompositions},
   pdfauthor={Marcel Pommer}
@@
 Montavon et al.
-introduce in their paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} \cite{Montavon.2017b} a new technique, the deep taylor decomposition, to map the relevance of the output on the input features, i.e.
+introduce in their paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} \cite{Montavon.2017b} a new technique, the deep Taylor decomposition, to map the relevance of the output on the input features, i.e.
 quantify the influence of each input variable on the output.
 They demonstrate the results on two image recognition data sets, the MNIST \cite{lecun2010mnist} and the ILSVRC \cite{Russakovsky.2015}, creating heatmaps to display the relevance of each single pixel.
-I recreate the procedure in Python and apply the deep taylor decomposition to the titanic dataset \cite{Eaton.1998}.
+I recreate the procedure in Python and apply the deep Taylor decomposition to the titanic dataset \cite{Eaton.1998}.
 \end{abstract}
@@
 \section{Introduction}
-The raise of machine learning, combined with steadily growing computational power revolutionized many so far hard to grasp tasks like image recognition and are highly used in countless areas like self driving cars and diagnoses of deseases.
-Those new techniques became quite famous during the last decade due to their overperformance in nearly every field, however their complexity makes them mathematicaly hard to understand and explain, leading to one of their major drawbacks, missing explainability.
+The raise of machine learning, combined with steadily growing computational power revolutionized many so far hard to grasp tasks like image recognition and are highly used in countless areas like self driving cars and diagnoses of diseases.
+Those new techniques became quite famous during the last decade due to their over performance in nearly every field, however their complexity makes them mathematically hard to understand and explain, leading to one of their major drawbacks, missing explainability.
 The paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} \cite{Montavon.2017b} by Montavon et al.
-tries to tackle this problem by extending the explainability of deep neural networks using taylor expansion, resulting in a mapping of non negative relevance from the output to each input features.
+tries to tackle this problem by extending the explainability of deep neural networks using Taylor expansion, resulting in a mapping of non negative relevance from the output to each input feature.
 The authors apply their technique to a variety of examples from the MNIST \cite{lecun2010mnist} dataset as well as the ILSVRC \cite{Russakovsky.2015} dataset.
-figure \ref{fig.1} shows a tractable example, in which a neural network detects a `0` while distracted by a `5`.
+Figure \ref{fig.1} shows a tractable example, in which a neural network detects a `0` while distracted by a `5`.
 We denote the neurons with $x_i$ and the respective contributions with $R_i$, resulting in a graphical representation, i.e.
-a heatmap, indicating which pixels contribut with which intensity to the decision of the neural network.
+a heatmap, indicating which pixels contribute with which intensity to the decision of the neural network.
 \begin{figure}[ht]
@@
       \includegraphics[width=0.5\textwidth]{images/fig._1_example}
-	\caption{Example: Detecting 0 with distrecting numbers with a neural network}
+	\caption{Example: Detecting 0 with distracting numbers with a neural network}
 	\label{fig.1}
@@
 Montavon et al.
-focus on image recognition, but highlight, that the procedure can be broadcasted to any input space and feature set.
+focus on image recognition, but highlight, that the procedure can be broad casted to any input space and feature set.
 In my analysis of the application of the algorithm I will focus on the titanic \cite{Eaton.1998} dataset which is very tractable and easy to understand and interpret.
@@
 \label{sec:main}
-The main section summarizes the general idea and presents the definitions and theorems while focusing on image recognition and following the metodology of Montavon et al.
+The main section summarizes the general idea and presents the definitions and theorems while focusing on image recognition and following the methodology of Montavon et al.
 In the context of image classification, we define a d-dimensional input space $x \in\mathbb{R}^d$, where the image pixels ($p$) can be represented as $x=\{x_p\}$.
 The function $f(x):\mathbb{R}^d \to \mathbb{R}^+$ quantifies either the probability of an object in the picture or the quantity of the object in question.
-The aim of the deep taylor decomposition is to assign a relevance score $R_p(x)$ to each pixel $p$ in the input space.
+The aim of the deep Taylor decomposition is to assign a relevance score $R_p(x)$ to each pixel $p$ in the input space.
 The relevance score quantifies the explanatory power of each pixel, i.e.
 the higher the relevance score the more important was the pixel for the classification.
-If the result is plotted in an image or to say heatmap as displayed in figure 1 the pixels which led to the classification decision are highligthed.
+If the result is plotted in an image or to say heatmap as displayed in figure 1 the pixels which led to the classification decision are highlighted.
 In practice some conditions can help to further define and understand the relevance score.
@@
 We will use definition \ref{thm:consistent} to evaluate heatmaps, however consistency is not necessarily a measure of quality, which can be seen in the following example of a uniform relevance over all $d$ pixels where $\forall p: R_p(x) = \frac{1}{d} f(x)$.
-Although, the heatmap will comply with definition \ref{thm:consistent} it will result in an all black/grey image providing no further information on the relation between input and output.
+Although, the heatmap will comply with definition \ref{thm:consistent} it will result in an all black/gray image providing no further information on the relation between input and output.
 
@@
 \label{sec:alg}
-The deep taylor decomposition is based on the first order taylor expansion at a root point $\tilde{x}$, such that $f(\tilde{x})=0$:
+The deep Taylor decomposition is based on the first order Taylor expansion at a root point $\tilde{x}$, such that $f(\tilde{x})=0$:
 \begin{align}
     f(x)=f(\tilde{x}) + \left( \frac{\partial f}{\partial x}\Big|_{x=\tilde{x}}\right)^T \cdot (x-\tilde{x}) + \epsilon
-    = 0 + \sum_p \frac{\partial f}{\partial x_p}\Big|_{x=\tilde{x}} \cdot (x_p-\tilde{x_p}) + \epsilon  
+    = 0 + \sum_p \frac{\partial f}{\partial x_p}\Big|_{x=\tilde{x}} \cdot (x_p-\tilde{x}_p) + \epsilon  
  \label{eq:taylorDecomp},
 \end{align}
+\begin{wrapfigure}{r}{6cm}
+	\vspace{-0.35cm}
+      \includegraphics[width=6cm]{images/fig._2_example_root_point}
+      \vspace{-0.45cm}
+	\caption{Root point in an image.}
+	\label{fig.2}
+\end{wrapfigure} 
 where the sum over all pixels derivative is defined as the redistributed relevance:
@@
 The finding of the root point is a great challenge and far from obvious.
-In figure 2 we can see an image, where the root point is simply a variant of the picture where the building is blurrred.
-\begin{figure}[ht]
-	\centering
-      \includegraphics[width=0.5\textwidth]{images/fig._2_example_root_point}
-	\caption{Example: Root point in an image.}
-	\label{fig.2}
-	\vspace{-0.5cm}
-\end{figure}
-Since an image possibly can have more than one root point the choice is crucial and a good root point deviates from the original point $x$ as few as possible, i.e. minimizing the obective:
+In figure 2 we can see an image, where the root point is simply a variant of the picture where the building is blurred.
+Since an image possibly can have more than one root point the choice is crucial and a good root point deviates from the original point $x$ as few as possible, i.e.
+minimizing the objective:
 \begin{align*}
@@
 where $\mathbb{X}$ is the input domain.\\
-
-Next we focus on the deep taylor decomposition, where we consider the mapping of neurons in one layer to each neuron in the next layer, assuming a relation explainable by some relevance function $R_j(\{x_i\})$.
-If this assumption holds and we further can identify a root point $\{\tilde{x_i}\}$ such that $R_j(\{\tilde{x_i}\})=0$ we can write equation \ref{eq:taylorDecomp}:
+Next we focus on the deep Taylor decomposition, where we consider the mapping of neurons in one layer to each neuron in the next layer, assuming a relation explainable by some relevance function $R_j(\{x_i\})$.
+If this assumption holds and we further can identify a root point $\{\tilde{x}_i\}$ such that $R_j(\{\tilde{x}_i\})=0$ we can write equation \ref{eq:taylorDecomp}:
 \begin{align*}
-    \sum_j R_j= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\Big|_{\{\tilde{x_i}\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}\}) + \epsilon
-    = \sum_i \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x_i}) + \epsilon
+    \sum_j R_j= \left( \frac{\partial (\sum_j R_j)}{\partial \{x_i\}}\Big|_{\{\tilde{x}_i\}}\right)^T \cdot (\{x_i\}-\{\tilde{x}\}) + \epsilon
+    = \sum_i \sum_j \frac{\partial R_j}{\partial x_i}\Big|_{\{\tilde{x}\}} \cdot (x_i-\tilde{x}_i) + \epsilon
 \end{align*}
@@
 where $\{x_i\}$ is a d-dimensional input and $\theta = \{w_{ij},b_j\}$ are weights and bias.
-To guarantee the exististence of a root point in the origin we restrict $b_j\leq0$.
-The relevance of the top layer is due to the pooling $R_k=\sum_j x_j$ and can be redistributed to the next layer according to the taylor decomposition
+To guarantee the existence of a root point in the origin we restrict $b_j\leq0$.
+The relevance of the top layer is due to the pooling $R_k=\sum_j x_j$ and can be redistributed to the next layer according to the Taylor decomposition
 \begin{align*}
@@
 If either $\sum_j\tilde{x}_j=0$ and $\forall j: \tilde{x}_j \geq0$ we need to chose $\{\tilde{x}_j\}$ resulting in $R_j = x_j$, since $\frac{\partial R_k}{\partial x_j} = 1$.
-Redistributing the relevance to the next layer using the taylor decomposition leads to
+Redistributing the relevance to the next layer using the Taylor decomposition leads to
 \begin{align}
@@
 If we consider an unconstrained input space one can chose the nearest root point in the Euclidean sense.
-Considering the rectified linear activation the intersection of the equation $\sum_i \tilde{x}_i^{(j)} w_{i,j}+b_j$ and the line of maximum descent defined by the derivative $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tw_j$, where $w_i$ ist the weight vector and $t \in \mathbb{R}$ define the nearest root point which is then given by $\{\tilde{x}_i\}^{(j)} = \{x_i - \frac{w_{ij}}{\sum_i w_{ij}^2}(\sum_i x_i w_{ij}+b_j)\}$.
-Pluggin in equation \ref{equ:propagationRule} leads to
+Considering the rectified linear activation the intersection of the equation $\sum_i \tilde{x}_i^{(j)} w_{i,j}+b_j=0$ (root point condition) and the line of maximum descent defined due to the rectified linear unit defined as  $\{\tilde{x}_i\}^{(j)}=\{x_i\} +t w_j$, where $w_j$ ist the weight vector and $t \in \mathbb{R}$ defines the nearest root point which is then given by $\{\tilde{x}_i\}^{(j)} = \{x_i - \frac{w_{ij}}{\sum_i w_{ij}^2}(\sum_i x_i w_{ij}+b_j)\}$.
+If we plug in $\{\tilde{x}_i\}^{(j)}$ in equation \ref{equ:propagationRule} we get the propagation rule for $R_i$
 \begin{align*}
@@
 
-\begin{proposition}[$w^2$-Rule consistency]
+\begin{proposition}[$\omega^2$-Rule consistency]
 \label{prop:wconsistency}
-$\forall g \in G$, the deep Taylor decomposition with the $w^2$-rule is consistent in the sense of definition 3.
+$\forall g \in G$, the deep Taylor decomposition with the $\omega^2$-rule is consistent in the sense of definition 3.
 \end{proposition}
@@
 Montavon et al.
-consider $\mathcal{X} = \mathbb{R}_x^d$ and $\mathcal{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\}$, where $l_i$ and $h_i$ are the respective lower and higher bounds for each input feature.
+consider $\mathcal{X} = \mathbb{R}_x^d$ and $\mathcal{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\}$, where $l_i\leq 0$ and $h_i \geq 0$ are the respective lower and higher bounds for each input feature.
 I will only cover the first case since logic and results are quiet similar and the domain corresponds to the rectified linear activation.
-Hence we already know of the existence of one root at the origin we search on the segment $(\{x_i 1_{w_{ij}<0}\},\{x_i\})$ and thus the direction of the segment is given by $v_i^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$.
+Montavon et al.
+propose the segment $(\{x_i 1_{w_{ij}<0}\},\{x_i\})$, since we already know of the existence of one root point at the origin and thus the direction of the segment is given by $v_i^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$.
 If we follow the same logic as in section \ref{sec:wRule} but adjust the line of maximum descent to $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tx_i 1_{w_{ij}\geq0}$ we get the following relevance propagation rule
@@
 Since many neural networks use complex deep architectures the authors further show a tractable way for the mapping of relevance from higher to the lower layers if the mapping is not explicit and introduce the concept of relevance models.
-The Min-Max and the Training-Free relevance model are introduced in the paper, however I will only cover the first.
-It is defined as
+\begin{wrapfigure}{r}{5cm}
+	\centering
+      \includegraphics[width=5cm]{images/min_max_relevance_model}
+	%\label{fig._min_max_model}
+\end{wrapfigure} 
+The Min-Max and the Training-Free relevance model are introduced in the paper, however I will only cover the first. We define
 \begin{align*}
@@
 where $a_j = \min(0,\sum_lR_lv_{lj} + d_j)$ is a negative bias where the sum runs over the detection neurons from the upper layer and $R_l$ are the corresponding relevances.
-After estimation of the paramters $\{v_{ij}, v_{lj}, d_j\}$ by minimizing
+After estimation of the parameters $\{v_{ij}, v_{lj}, d_j\}$ by minimizing
 \begin{equation}
@@
 , where $R_k$ and $\hat{R}_k$ are the true and predicted relevances, we end up with the same problem as in section \ref{sec:main}.
-Due to the similar structure we can apply the same computations and compute $R_j = y_j$ and $R_i = \sum_j \frac{q_{ij}}{\sum_{i´}q_{i´j}} R_j$, where $q_{ij} = \{w_{ij}^2, x_i w_{ij}1_{w_{ij}>0}\}$ for the $w^2$-rule and $z^+$-rule, respectively.
+Due to the similar structure we can apply the same computations and derive $R_j = y_j$ and $R_i = \sum_j \frac{q_{ij}}{\sum_{i´}q_{i´j}} R_j$, where $q_{ij} = \{w_{ij}^2, x_i w_{ij}1_{w_{ij}>0}\}$ for the $\omega^2$-rule and $z^+$-rule, respectively.
 In contrast to the problem before the resulting heatmap is only approximately conservative, due to the possible errors during the minimization of  \ref{min:relevanceModel}.
@@
 As mentioned in the beginning the authors focus on image recognition and present examples from the MNIST \cite{lecun2010mnist} and the ILSVRC \cite{Russakovsky.2015} data sets.
-I will only present one example from the MNIST \cite{lecun2010mnist} data set and conclude with a self made example from the titanic \cite{Eaton.1998} data set.
+I will only present one example from the MNIST \cite{lecun2010mnist} data set and conclude with an example from the titanic \cite{Eaton.1998} data set.
 
@@
 Figure \ref{fig.1} shows how the proposed algorithms can detect pixels with a high relevance for detecting a `0` next to a distracting number.
-Montavon et all show several examples of other numbers as in figure \ref{fig.3} and compare several methods.
+Montavon et al.
+show several examples of other numbers as in figure \ref{fig.3} and compare several methods.
 It can be seen that the heatmap clearly identifies the important pixels, i.e.
 correctly assigns relevance to areas where the digit is located.
-Further analysis shows, that especially the $w^2$- and $z$-rule are conservative and positive an thus satisfy the condition for definition \ref{thm:consistent}.
+Further analysis shows, that especially the $\omega^2$- and $z$-rule are conservative and positive an thus satisfy the condition of definition \ref{thm:consistent}.
 \begin{figure}[ht]
@@
       \includegraphics[width=0.75\textwidth]{images/fig._3_MNIST}
-	\caption{Example: Detecting 0 with distrecting other numbers present.}
+	\caption{Example: Detecting 0 with distracting other numbers present.}
 	\label{fig.3}
 \end{figure}
-%\vspace{-0.25cm}
+\vspace{-0.25cm}
 
@@
 Neural networks are not only used for image recognition but for a variety of problems like the prominent titanic survival classification which I chose for my personal analysis.
-I build a simple neural network with one hidden layer and 10 neurons resulting in a accuracy of 80 \%.
-Table 1 summarizes the results and clearly shows, that features like sex and age have greater influence on the survival probability than features like the pasenger ID or the port of embarkation.\footnote{Code can be found on: \url{https://github.com/mpommer/Deep-Taylor-Decomposition-Python}}
+I build a simple neural network with one hidden layer and 5 neurons, a bias $b_j\leq0$ and a sum pooling as output layer resulting in a accuracy of 79 \% on the test data and 84 \% on the trainingsdata.
+Table 1 summarizes the results  for a passenger which was classified as surviver with 0.67 in a ver young age.
+The numbers clearly shows, that age has greater influence on the survival probability, but features like the passenger ID does not.\footnote{Code can be found on: \url{https://github.com/mpommer/Deep-Taylor-Decomposition-Python}}
+\vspace{-0.5cm}
+\begin{table}[H]
 
-\begin{table}[h!]
-\centering
-\caption{Relevance of titanic input features}
+\caption{Relevance of Titanic Input Features}
 \label{table_1}
-\begin{tabular}{ |c||c|c|c|c| }
+\begin{tabular}{ |c||c|c|c|c|c|c|c|c|c|c|}
 
  \hline 
-  feature & sex& age & parch & passenger id\\
+  feature& ID & Class & Sex& Age & Sibl. & Parch &Fare & C. & Q. & S.\\
  \hline
- relevance in \% & 10 & 10 & 10 & 10\\
+ rel. \% & 0.01 & 0.81 & 1.45& 48.92 & 10.63 & 5.07 &22.18 & 2.86 & 2.68 & 5.38\\
  \hline
@@
 \label{sec:conclusions}
-During the last years the importance of explainability of complex machine learning models became more and more present, due to either simple questions of understanding or even legal issues in for example pricing of insurances.
+The increasing popularity of machine learning and, with it, complex deep neural networks raised the question of explainability, amongst others on context of legal questions for self driving cars or in pricing for insurance.
 Montavon et al.
-present in their paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} \cite{Montavon.2017b} practical algorithms which can help to tackle the problem of interpreteability for a wide range of deep learning models.
+present in their paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} \cite{Montavon.2017b} practical algorithms which can help to tackle the problem of interpretability for a wide range of deep learning models.
 The authors furthermore substantiate their theory with examples on two very famous image recognition data sets, namely the MNIST \cite{lecun2010mnist} and the ILSVRC \cite{Russakovsky.2015} data sets.
-I myself could also reproduce very reliable results on the titanic \cite{Eaton.1998} data set.
+I myself could reproduce reliable results on the titanic \cite{Eaton.1998} data set.
 

### 2022-06-19 PythonFiles/Neural_Network.py

@@ -7,12 +7,10 @@ Created on Sun May  1 17:57:47 2022
 from tensorflow.keras.callbacks import EarlyStopping
 from tensorflow.keras.layers import Dense
 from tensorflow import keras
+from tensorflow.keras import initializers
 import tensorflow as tf
 import pandas as pd
-seed = 1864
-tf.random.set_seed(seed)
-import numpy as np
-np.random.seed(seed)
+seed = 12345
 
 
 class NonNeg(tf.keras.constraints.Constraint):
@@ -25,11 +23,6 @@ class NonNeg(tf.keras.constraints.Constraint):
      w = tf.cast(w < 0, w.dtype) * w
      return w
  
-    
-    # if w[0]<0:
-    #     return w
-    # else:
-    #     return 0
 
   def get_config(self):
     return {'ref_value': self.ref_value}
@@ -41,19 +34,30 @@ class NN:
         self.x_train = x_train
         self.y_train = y_train
         
-    def fit(self, layers, neurons):
+    def fit(self, layers, neurons, verbose = 0):
+        tf.random.set_seed(seed)
 
         model = keras.Sequential()
-        for l in range(layers):
-            model.add(Dense(neurons[l], input_dim=self.x_train.shape[1], activation = "ReLU", bias_constraint=NonNeg()))
+        model.add(Dense(neurons[0], input_dim=self.x_train.shape[1], activation = "ReLU", bias_constraint=NonNeg()))
+
+        # for l in range(layers):
+        #     model.add(Dense(neurons[l], input_dim=self.x_train.shape[1], activation = "ReLU", bias_constraint=NonNeg()))
             
-        model.add(Dense(1, activation='sigmoid', name='output'))
+        # model.add(Dense(1, input_dim=neurons[-1],activation="ReLU", trainable=False, name='output'))
+        model.add(Dense(1, input_dim=neurons[-1],
+                        kernel_initializer=initializers.RandomNormal(mean=1., stddev=0.),
+                        bias_initializer=initializers.Zeros(),
+                        activation="linear", 
+                        trainable=False, 
+                        name='output'))
 
-        model.compile(loss="mean_squared_error", optimizer= "adam", metrics=['mean_absolute_error','mean_squared_error'])
+        # model.add(AveragePooling1D(pool_size=2, strides=1, name = "output"))
 
-        es = EarlyStopping(monitor='val_loss', mode='min',min_delta=1e-12, patience=100, restore_best_weights=True)
[…]

### 2022-06-19 PythonFiles/dataReading.py

@@ -15,14 +15,18 @@ pd.set_option('display.width', 200)
 pd.set_option('display.float_format', lambda x: "%.2f" % x)
 
 
-def data_reading_transformation(path_url, minmaxscaler=False):
+def data_reading_transformation(path_url, minmaxscaler=False, withName=False):
     df_gender_submission = pd.read_csv(path_url + "/gender_submission.csv")
     y_test = df_gender_submission
     df_train = pd.read_csv(path_url + "/train.csv")
     df_test = pd.read_csv(path_url + "/test.csv")
     
-    df_train_reduced = df_train.drop(labels=['Name', "Ticket", "Cabin"], axis=1)
-    df_test_reduced = df_test.drop(labels=['Name', "Ticket", "Cabin"], axis=1)
+    if withName:
+        df_train_reduced = df_train.drop(labels=["Name", "Cabin", "Ticket"], axis=1)
+        df_test_reduced = df_test.drop(labels=["Name", "Cabin", "Ticket"], axis=1)
+    else:        
+        df_train_reduced = df_train.drop(labels=['Name', "Ticket", "Cabin", "PassengerId"], axis=1)
+        df_test_reduced = df_test.drop(labels=['Name', "Ticket", "Cabin", "PassengerId"], axis=1)
         
     
     ageMeanDad = int(df_train_reduced[(df_train_reduced["Survived"]==0)][[ "Age"]].mean())

### 2022-06-19 PythonFiles/deep_neural_explainability.py

@@ -1,0 +1,7 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Sun Jun 19 11:55:40 2022
+
+@author: marce
+"""
+

### 2022-06-19 PythonFiles/explainability_abstract_class.py

@@ -12,9 +12,10 @@ import numpy as np
 
 class explainability(metaclass=abc.ABCMeta):
     
-    def __init__(self, model, result):
+    def __init__(self, model, result, input_vector):
         self.model = model
         self.result = result
+        self.input_vector = input_vector
         
         
     @abstractmethod

### 2022-06-19 PythonFiles/main_execution.py

@@ -9,19 +9,19 @@ from PythonFiles.dataReading import data_reading_transformation
 from PythonFiles.omega_squared import omega_squared
 from PythonFiles.z_rule import z_rule 
 from PythonFiles.z_plusrule import z_plusrule 
-
+import pandas as pd
 from PythonFiles.Neural_Network import NN
 import numpy as np
 
-path = "data/titanic"
+path_url = "data/titanic"
 
 minmaxscaler=True
 
-x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(path, minmaxscaler)
+x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(path_url, minmaxscaler, withName = True)
 
 neural_net = NN(x_train, y_train)
 
-neural_net.fit(layers = 1, neurons = [25]*1)
+neural_net.fit(layers = 1, neurons = [10]*1)
 
 model = neural_net.getModel()
 
@@ -29,11 +29,15 @@ neural_net.testResult(x_test,y_test)
 
 prediction = neural_net.predict(x_test)
 
-t = model.layers[0].weights[0].numpy()
+w1 = model.layers[0].weights[0].numpy()
+b1 = model.layers[0].weights[1].numpy()
+w2 = model.layers[1].weights[0].numpy()
+b2 = model.layers[1].weights[1].numpy()
 
 #%% omega ^2- rule
 
-taylor_dec = omega_squared(model, prediction[0])
+passenger = 89
+taylor_dec = omega_squared(model, prediction[passenger], x_test[passenger])
         
 res = taylor_dec.fit()
         

### 2022-06-19 PythonFiles/omega_squared.py

@@ -10,31 +10,77 @@ from PythonFiles.explainability_abstract_class import explainability
 class omega_squared(explainability):
     
     def fit(self):
-        number_layers = len(self.model.layers)
+        # from first layer to output
+        self.getInput_activation()
+        R_j = self.dic["1_layer"]
         
-        
-        output = self.result
-        for layer in np.arange(number_layers-1, -1, -1):
-            output = self.omegaRule(output, self.model.layers[layer].weights[0].numpy())
+        R_i = self.omegaRule(R_j, self.model.layers[0].weights[0].numpy())
             
-        return output
+        return R_i
     
     def omegaRule(self, R_j, weights):
-        input_relevance = []
+        w_squared = weights*weights
+        n = w_squared/np.sum(w_squared, axis = 0)
         
-        summe = sum(weights**2)
-        for in_neuron_index, inputs in enumerate(weights):
-            R_i = 0
-            for out_neuron_index, weight in enumerate(inputs):
-                weight_squared = weight**2
-                weight_sum = summe[out_neuron_index]
-                R_i += weight_squared/weight_sum*R_j[out_neuron_index]
-            
-            
-            input_relevance.append(R_i)
-            
-        return input_relevance
+        return np.matmul(n, R_j)
         
+        # summe = sum(weights**2)
+        # for in_neuron_index, inputs in enumerate(weights):
+        #     R_i = 0
+        #     for out_neuron_index, weight in enumerate(inputs):
+        #         weight_squared = weight**2
+        #         weight_sum = summe[out_neuron_index]
+        #         R_i += weight_squared/weight_sum*R_j[out_neuron_index]
+            
+            
+        #     input_relevance.append(R_i)
+            
+        # return input_relevance
+    
+    def getInput_activation(self):
+        dic = {}
+        dic["0_layer"]= self.input_vector
+        
+        input_array = self.input_vector
+        for layer in np.arange(1,len(self.model.layers)+1):
+            weights = self.model.layers[layer-1].weights[0].numpy()
+            bias = self.model.layers[layer-1].weights[1].numpy()
+            
+            output = np.matmul(input_array,weights)+bias
+            output = np.array([max(0,x) for x in output])
+            dic[f"{layer}_layer"]=output
+            
+            input_array = output
+            
+            
+        self.dic = dic
+    
+    
+    # def fit(self):
+    #     number_layers = len(self.model.layers)
+        
+        
[…]

### 2022-06-19 PythonFiles/taylor_decomposition_presentation.py

@@ -1,0 +1,41 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Sun May  1 17:50:10 2022
+
+@author: Marcel Pommer
+"""
+
+from PythonFiles.dataReading import data_reading_transformation
+from PythonFiles.omega_squared import omega_squared
+from PythonFiles.Neural_Network import NN
+
+# preprocess data
+x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(path_url = "data/titanic", minmaxscaler = True, withName = True)
+
+# build the neural network
+neural_network = NN(x_train, y_train)
+neural_network.fit(layers = 1, neurons = [5]*1, verbose = 0)
+
+# print test results
+neural_network.testResult(x_test,y_test)
+neural_network.trainResult()
+
+# get the model
+model = neural_network.getModel()
+
+# get predictions
+prediction = neural_network.predict(x_test)
+
+
+#%% omega ^2- rule
+# choose passenger and create taylor decomposition
+passenger = 89
+taylor_decomposition = omega_squared(model, prediction[passenger], x_test[passenger])
+        
+relevance = taylor_decomposition.fit()
+        
+        
+taylor_decomposition.printExplainability(feature_name)
+
+
+

### 2022-06-19 PythonFiles/z_rule.py

@@ -10,11 +10,6 @@ from PythonFiles.explainability_abstract_class import explainability
 from tensorflow.keras import backend as K
 
 class z_rule(explainability):
-    
-    def __init__(self, model, result, input_vector):
-        self.model = model
-        self.result = result
-        self.input_vector = input_vector
         
     def fit(self):
         self.getInput_activation()

### 2022-06-26 Präsentation/Präsentation_23.06.2020.tex
finish presentation and paper

@@
 Deep neural networks perform great on a variety of problems \nocite{*}\\
-\textbf{but} how can we justify decisions made by complex deep architectures?\\
+\textbf{but} how can we explain decisions made by complex deep architectures?\\
 \end{frame}
@@
        \begin{columns}[T]
-          \column{0.65\textwidth}
+          \column{0.62\textwidth}
              \centering
@@
          \end{columns} 
+\pause
 \vspace{0.5cm}
@@
 
+\pause
 \end{itemize}
@@
 
-\subsection[Methodology]{Methodology}
+\subsection[Taylor Expansion and Sensitivity Analysis]{Taylor Expansion and Sensitivity Analysis}
 
@@
 \frametitle{Sensitivity Analysis}
-\vspace{0.25cm}
-Root point at infinitesimally small distance from the actual point, i.e. $\xi = x- \delta \frac{\partial f}{\partial x}$, where $\delta$ is small\\
+\vspace{0.35cm}
+Choose a point at infinitesimally small distance from the actual point, i.e. $\xi = x- \delta \frac{\partial f}{\partial x}$, where $\delta$ is small\\
 \pause
-\vspace{0.1cm}
+\vspace{0.35cm}
 If we assume a locally constant function we get
@@
 \frametitle{Derivation of Propagation Rules}
-\vspace{0.3cm}
-Given $R_j = \max(0, \sum_i x_i w_{ij} + b_j)$ and $b_j \leq 0$ and a search direction $\{v_i\}^{(j)}$ in the input space such that
+\vspace{0.5cm}
+Given $R_j = \max(0, \sum_i x_i w_{ij} + b_j)$ and $b_j \leq 0$ and a search direction $\{v_i\}^{(j)}$
 
@@
 
-\vspace{0.2cm}
-If the data point itself is not a root point, i.e.
-$\sum_i x_i w_{ij} + b_j>0$ the nearest root along $\{v_i\}^{(j)}$ is given by the intersection of equation \eqref{equ:search_direction} and $\sum_i\tilde{x}_i^{(j)} w_{ij} + b_j=0$ which can be resolved to
-\vspace{-0.1cm}
+\pause
+\vspace{0.1cm}
+If $\sum_i x_i w_{ij} + b_j>0$ the nearest root along the search direction $\{v_i\}^{(j)}$ is given by the intersection of equation \eqref{equ:search_direction} and $\sum_i\tilde{x}_i^{(j)} w_{ij} + b_j=0$
 \begin{align*}
-0 &= \sum_i x_i w_{ij} + b_j + \sum_i v_i^{(j)} t w_{ij} \\
-x_i - \tilde{x}_i^{(j)} & = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
+&               & 			0 &= \sum_i x_i w_{ij} + b_j + \sum_i v_i^{(j)} t w_{ij} \\[0.25em]
+&\Leftrightarrow& -t & = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}}\\[0.5em]
+&\Leftrightarrow& x_i - \tilde{x}_i^{(j)} & = \frac{\sum_i x_i w_{ij} + b_j}{\sum_i v_i^{(j)} w_{ij}} v_i^{(j)}
 \end{align*}
@@
 	\item Search direction $\{v_i\}^{(j)} = w_{ij}$ (gradient of $R_j$)
-	\item No domain restriction and for $\tilde{x}_i^{(j)} = x_i - \frac{R_j}{\sum_{i'}w_{i'j}^2}$
+	\item No domain restriction and for $\tilde{x}_i^{(j)} = x_i - \frac{R_j(x_i)}{\sum_{i'}w_{i'j}^2} w_{ij}$
 	\begin{align*}
-		R_j(\tilde{x}) &= \max(0, \sum_i (x_i -\frac{R_j}{\sum_{i'}w_{i'j}^2}) w_{ij}  + b_j) \\
-		&= \max(0, \underbrace{\sum_i (x_i w_{ij} + b_j)}_{=R_j} - R_j \underbrace{\frac{\sum_{i}w_{ij}^2}{\sum_{i'}w_{i'j}^2}}_{=1} )= 0 
+		R_j(\tilde{x}) &= \max(0, \sum_i (x_i -\frac{R_j(x_i) w_{ij}}{\sum_{i'}w_{i'j}^2}) w_{ij}  + b_j) \\
+		&= \max(0, \underbrace{\sum_i (x_i w_{ij} + b_j)}_{=R_j(x_i)} - R_j (x_i) \underbrace{\frac{\sum_{i}w_{ij}^2}{\sum_{i'}w_{i'j}^2}}_{=1} )= 0 
 	\end{align*}
@@
 \frametitle{$z^+$-rule $\mathcal{X}=\mathbb{R}_+^d$}
-\vspace{0.5cm}
+\vspace{0.35cm}
 Search for a root point on the segment $(\{x_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathbb{R}_+^d$\\
@@
 	\item Search direction $\{v_i\}^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$
-	\item If $\{x_i\} \in \mathbb{R}_+^d$ so is the whole domain, further for $w_{ij}^-=\min(0,w_{ij})$
-	\
+	\item If $\{x_i\} \in \mathbb{R}_+^d$ so is the whole domain, further for $w_{ij}^-=\min(0,w_{ij})$ and $w_{ij}^+ = \max(0, w_{ij})$
+	\vspace{-0.25cm}
 	\begin{align*}
@@
 \end{enumerate}
-
+\vspace{-0.2cm}
 \pause
@@
 \vspace{0.4cm}
-Given a bounded input space $\mathcal{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\} $, with $l_i \leq 0$ and $ h_i \geq 0$ and we chose the segment $(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathcal{B}$\\
+Given a bounded input space $\mathcal{B} = \{\{x_i\} : \forall_{i=1}^d l_i\leq x_i \leq h_i\} $, with $l_i \leq 0$ and $ h_i \geq 0$ and we search on the segment $(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\},\{x_i\})\subset \mathcal{B}$\\
 \begin{enumerate}
@@
 			R_k &= \sum_l \frac{x_k w_{kl}^+}{\sum_{k'} x_{k'} w_{k'l}^+} R_l\\
-				&= (\sum_j x_j) \cdot \frac{\norm{\{x_j\}}_p}{\norm{\{x_j\}}_1}   \sum_l \frac{w_{kl}^+R_l}{\sum_{k'} x_{k'} w_{k'l}^+} 
+				&= \bigl( \sum_j x_j \bigr)\cdot \frac{\norm{\{x_j\}}_p}{\norm{\{x_j\}}_1}   \sum_l \frac{w_{kl}^+R_l}{\sum_{k'} x_{k'} w_{k'l}^+} 
 			\end{align*}
@@
 \end{equation*}
-where $q_{ij}= v_{ij}^2$, $q_{ij}= x_i v_{ij}^+$ or $q_{ij}= x_i v_{ij} - l_i v_{ij}^+ - h_i v_{ij}^-$ for the $w^2$-rule, $z^+$-rule and the $z^b$- rule respectively
+where $q_{ij}= w_{ij}^2$, $q_{ij}= x_i w_{ij}^+$ or $q_{ij}= x_i w_{ij} - l_i w_{ij}^+ - h_i w_{ij}^-$ for the $w^2$-rule, $z^+$-rule and the $z^b$- rule respectively
 \end{itemize}

### 2022-06-26 paper/paper_marcel_pommer.tex
finish presentation and paper

@@
 % directly.
+
+\clubpenalty10000
+\widowpenalty10000
+\displaywidowpenalty10000
 
@@
 focus on image recognition, but highlight, that the procedure can be broad casted to any input space and feature set.
-In my analysis of the application of the algorithm I will focus on the titanic \cite{Eaton.1998} dataset which is very tractable and easy to understand and interpret.
+In contrast to the authors I will focus on a non image recognition task, the titanic (survival)\cite{Eaton.1998} dataset which is very tractable and easy to understand and interpret.
 
@@
 the higher the relevance score the more important was the pixel for the classification.
-If the result is plotted in an image or to say heatmap as displayed in figure 1 the pixels which led to the classification decision are highlighted.
+The result can be displayed in an image or to say heatmap as shown in figure 1 the pixels which led to the classification decision are highlighted.
 In practice some conditions can help to further define and understand the relevance score.
@@
 \end{definition}
-We will use definition \ref{thm:consistent} to evaluate heatmaps, however consistency is not necessarily a measure of quality, which can be seen in the following example of a uniform relevance over all $d$ pixels where $\forall p: R_p(x) = \frac{1}{d} f(x)$.
-Although, the heatmap will comply with definition \ref{thm:consistent} it will result in an all black/gray image providing no further information on the relation between input and output.
+We will use definition \ref{thm:consistent} to evaluate heatmaps, however consistency is not necessarily a measure of quality, which can be seen in the following example of uniform distributed relevance over all $d$ pixels where $\forall p: R_p(x) = \frac{1}{d}\cdot f(x)$.
+Although, the heatmap will comply with definition \ref{thm:consistent} it will result in an all gray/red image providing no further information on the relation between input and output.
 
@@
 \end{align*}
-and $\odot$ is defined as element wise multiplication.
-The finding of the root point is a great challenge and far from obvious.
+and $\odot$ is the element wise multiplication.
+The search of the root point is a great challenge and far from obvious.
 In figure 2 we can see an image, where the root point is simply a variant of the picture where the building is blurred.
@@
 Next we focus on the deep Taylor decomposition, where we consider the mapping of neurons in one layer to each neuron in the next layer, assuming a relation explainable by some relevance function $R_j(\{x_i\})$.
-If this assumption holds and we further can identify a root point $\{\tilde{x}_i\}$ such that $R_j(\{\tilde{x}_i\})=0$ we can write equation \ref{eq:taylorDecomp}:
+If this assumption holds and we further identify a root point $\{\tilde{x}_i\}$ such that $R_j(\{\tilde{x}_i\})=0$ we apply the Taylor decomposition layer-wise:
 \begin{align*}
@@
 \end{align*}
-If definition \ref{thm:consistent} holds, the relevances is guaranteed to be conserved in each layer, i.e. $R_f=...=\sum_j R_j=...=\sum_p R_p$ and $R_f,...,\{R_j\},...\{R_p\} \geq 0$.\\
+If definition \ref{thm:consistent} holds for each local Taylor decomposition, the relevances is guaranteed to be conserved in each layer, i.e.
+$R_f=...=\sum_j R_j=...=\sum_p R_p$ and the relevance propagation rule is positive $R_f,...,\{R_j\},...\{R_p\} \geq 0$.\\
 
@@
 \end{align*}
-If either $\sum_j\tilde{x}_j=0$ and $\forall j: \tilde{x}_j \geq0$ we need to chose $\{\tilde{x}_j\}$ resulting in $R_j = x_j$, since $\frac{\partial R_k}{\partial x_j} = 1$.
+If either $\sum_j\tilde{x}_j=0$ and $\forall j: \tilde{x}_j \geq0$ we need to chose $\{\tilde{x}_j\}=0$ resulting in $R_j = x_j$, since $\frac{\partial R_k}{\partial x_j} = 1$.
 Redistributing the relevance to the next layer using the Taylor decomposition leads to
@@
 \end{align}
-which is the starting point for the further analysis.
+which is the starting point for the further analysis and leaves the question of a suitable root point.
 
+%\vspace{-0.2cm}
 \subsection{Unconstrained Input Space and $\omega^2$-Rule}
 \label{sec:wRule}
-If we consider an unconstrained input space one can chose the nearest root point in the Euclidean sense.
-Considering the rectified linear activation the intersection of the equation $\sum_i \tilde{x}_i^{(j)} w_{i,j}+b_j=0$ (root point condition) and the line of maximum descent defined due to the rectified linear unit defined as  $\{\tilde{x}_i\}^{(j)}=\{x_i\} +t w_j$, where $w_j$ ist the weight vector and $t \in \mathbb{R}$ defines the nearest root point which is then given by $\{\tilde{x}_i\}^{(j)} = \{x_i - \frac{w_{ij}}{\sum_i w_{ij}^2}(\sum_i x_i w_{ij}+b_j)\}$.
+Considering an unconstrained input space we search the nearest root point in the Euclidean sense.
+The intersection of equation $\sum_i \tilde{x}_i^{(j)} w_{ij}+b_j=0$ (root point) and the line of maximum descent $\{\tilde{x}_i\}^{(j)}=\{x_i\} +t w_j$ ($w_j$ as gradient of $R_j$), where $w_j$ is the weight vector and $t \in \mathbb{R}$ defines the nearest root point which is then given by $\{\tilde{x}_i\}^{(j)} = \{x_i - \frac{w_{ij}}{\sum_i w_{ij}^2}(\sum_i x_i w_{ij}+b_j)\}$.
 If we plug in $\{\tilde{x}_i\}^{(j)}$ in equation \ref{equ:propagationRule} we get the propagation rule for $R_i$
@@
 \end{align*}
+
 \begin{proposition}[$z$-Rule consistency]\label{prop:zconsistency}
@@
 , where $R_k$ and $\hat{R}_k$ are the true and predicted relevances, we end up with the same problem as in section \ref{sec:main}.
-Due to the similar structure we can apply the same computations and derive $R_j = y_j$ and $R_i = \sum_j \frac{q_{ij}}{\sum_{i´}q_{i´j}} R_j$, where $q_{ij} = \{w_{ij}^2, x_i w_{ij}1_{w_{ij}>0}\}$ for the $\omega^2$-rule and $z^+$-rule, respectively.
+Due to the similar structure we can apply the same computations and derive $R_j = y_j$ and $R_i = \sum_j \frac{q_{ij}}{\sum_{i´}q_{i´j}} R_j$, where $q_{ij} \in \{w_{ij}^2, x_i w_{ij}1_{w_{ij}>0}\}$ for the $\omega^2$-rule and $z^+$-rule, respectively.
 In contrast to the problem before the resulting heatmap is only approximately conservative, due to the possible errors during the minimization of  \ref{min:relevanceModel}.
@@
 correctly assigns relevance to areas where the digit is located.
-Further analysis shows, that especially the $\omega^2$- and $z$-rule are conservative and positive an thus satisfy the condition of definition \ref{thm:consistent}.
+Further analysis shows, that especially the $\omega^2$- and $z$-rule are conservative and positive and thus satisfy comply with definition \ref{thm:consistent}.
 \begin{figure}[ht]
@@
       \includegraphics[width=0.75\textwidth]{images/fig._3_MNIST}
-	\caption{Example: Detecting 0 with distracting other numbers present.}
+	\caption{Example: Detecting number from 0-3 while distracting by number from 4-9 }
 	\label{fig.3}
@@
 Neural networks are not only used for image recognition but for a variety of problems like the prominent titanic survival classification which I chose for my personal analysis.
-I build a simple neural network with one hidden layer and 5 neurons, a bias $b_j\leq0$ and a sum pooling as output layer resulting in a accuracy of 79 \% on the test data and 84 \% on the trainingsdata.
-Table 1 summarizes the results  for a passenger which was classified as surviver with 0.67 in a ver young age.
-The numbers clearly shows, that age has greater influence on the survival probability, but features like the passenger ID does not.\footnote{Code can be found on: \url{https://github.com/mpommer/Deep-Taylor-Decomposition-Python}}
+I build a simple neural network with one hidden layer and 5 neurons, a bias $b_j\leq0$ and a sum pooling as output layer resulting in a accuracy of 79 \% on the test data and 84 \% on the trainings data.
+Table 1 summarizes the results  for a (very young) passenger which was classified as surviver.
+The numbers clearly show, that th age has a huge influence on the survival probability, but features like the passenger ID does not.\footnote{Code can be found on: \url{https://github.com/mpommer/Deep-Taylor-Decomposition-Python}}
 \vspace{-0.5cm}

### 2022-06-26 PythonFiles/dataReading.py

@@ -15,13 +15,13 @@ pd.set_option('display.width', 200)
 pd.set_option('display.float_format', lambda x: "%.2f" % x)
 
 
-def data_reading_transformation(path_url, minmaxscaler=False, withName=False):
+def data_reading_transformation(path_url, minmaxscaler=False, withID=False):
     df_gender_submission = pd.read_csv(path_url + "/gender_submission.csv")
     y_test = df_gender_submission
     df_train = pd.read_csv(path_url + "/train.csv")
     df_test = pd.read_csv(path_url + "/test.csv")
     
-    if withName:
+    if withID:
         df_train_reduced = df_train.drop(labels=["Name", "Cabin", "Ticket"], axis=1)
         df_test_reduced = df_test.drop(labels=["Name", "Cabin", "Ticket"], axis=1)
     else:        

### 2022-06-26 PythonFiles/explainability_abstract_class.py

@@ -37,7 +37,7 @@ class explainability(metaclass=abc.ABCMeta):
         table = [["feature", "absolute relevance", "relevance in perc"]]
 
         for index, name in enumerate(feature_names):
-            value = [name, round(relevance_array[index],4), f"{np.round(relevance_array[index]/self.result, 4)*100} %"]
+            value = [name, round(relevance_array[index],4), f"{round(relevance_array[index]/float(self.result) *100, 2)} %"]
             table.append(value)
             
         print(tabulate(table))

### 2022-06-26 PythonFiles/innvestigate_titanic.py

@@ -1,67 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Thu May 26 17:20:17 2022
-
-@author: Marcel Pommer
-"""
-
-import innvestigate
-from PythonFiles.dataReading import data_reading_transformation
-from PythonFiles.omega_squared import omega_squared
-from PythonFiles.Neural_Network import NN
-import numpy as np
-import tensorflow as tf
-
-
-path = "data/titanic"
-
-minmaxscaler=True
-
-x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(path, minmaxscaler)
-
-neural_net = NN(x_train, y_train)
-
-neural_net.fit(layers = 1, neurons = [10])
-
-model = neural_net.getModel()
-
-neural_net.testResult(x_test,y_test)
-
-prediction = neural_net.predict(x_test)
-
-
-
-#%% 
-
-analyzer = innvestigate.create_analyzer("deep_taylor", model)
-
-analysis = analyzer.analyze(x_test[14])
-
-
-
-#%%
-
-import imp
-import numpy as np
-import os
-
-import keras
-import keras.backend
-import keras.models
-
-import innvestigate
-import innvestigate.utils as iutils
-
-# Use utility libraries to focus on relevant iNNvestigate routines.
-eutils = imp.load_source("utils", "../utils.py")
-mnistutils = imp.load_source("utils_mnist", "../utils_mnist.py")
-
-
-
-
-
-
-
-
-
-

### 2022-06-26 PythonFiles/taylor_decomposition_presentation.py

@@ -10,7 +10,7 @@ from PythonFiles.omega_squared import omega_squared
 from PythonFiles.Neural_Network import NN
 
 # preprocess data
-x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(path_url = "data/titanic", minmaxscaler = True, withName = True)
+x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(path_url = "data/titanic", minmaxscaler = True, withID = True)
 
 # build the neural network
 neural_network = NN(x_train, y_train)

### 2022-06-26 PythonFiles/test_file.py

@@ -1,12 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Sat Jun 11 18:06:19 2022
-
-@author: marce
-"""
-
-x = 5
-y= 10
-
-print(x+y)
-

### 2022-06-30 Präsentation/Präsentation_23.06.2020.tex
final version presentation
las changes

@@
 	\begin{align*}
-		R_j(\tilde{x}) &= \max(0, \sum_i (x_i -\frac{R_j(x_i) w_{ij}}{\sum_{i'}w_{i'j}^2}) w_{ij}  + b_j) \\
+		R_j(\{\tilde{x}_i^{(j)}\}) &= \max(0, \sum_i (x_i -\frac{R_j(x_i) w_{ij}}{\sum_{i'}w_{i'j}^2}) w_{ij}  + b_j) \\
 		&= \max(0, \underbrace{\sum_i (x_i w_{ij} + b_j)}_{=R_j(x_i)} - R_j (x_i) \underbrace{\frac{\sum_{i}w_{ij}^2}{\sum_{i'}w_{i'j}^2}}_{=1} )= 0 
@@
 		R_j(\{l_i 1_{w_{ij}>0} + h_i 1_{w_{ij}<0}\}) &= \max(0, \sum_i l_i 1_{w_{ij}>0} w_{ij} + h_i 1_{w_{ij}<0} w_{ij} + b_j)\\
-		&=\max(0, \sum_i \underbrace{l_i w_{ij}^+}_{\leq 0} + \underbrace{h_i w_{ij}^-}_{\leq 0} + b_j)= 0
+		&=\max(0, \sum_i \underbrace{l_i w_{ij}^+}_{\leq 0} + \underbrace{h_i w_{ij}^-}_{\leq 0} +\  b_j)= 0
 	\end{align*}
@@
 \item One hidden layer with 400 neurons $\{x_j\}$ and one output $x_k$
-\item Random initialized weights $\{w_{ij}\}$ and non-negative bias $\{b_j\}$ initialized to zero
+\item Random initialized weights $\{w_{ij}\}$ and non-positive bias $\{b_j\}$ initialized to zero
 \item Training with 300000 iterations of stochastic gradient descent with a batch size of 20 
@@
 \end{figure}
-
+\pause
 \begin{figure}
@@
 \frametitle{Deep Networks}
-Many problems require very complex deep architectures
+Many problems require complex deep architectures
 
@@
 			\begin{equation*}
-			\min\langle (\hat{R}_k-R_k)^2) \rangle
+			\min\langle (\hat{R}_k-R_k)^2 \rangle
 			\end{equation*}
@@
 
-$\rightarrow$ The Min-Max relevance model is due to the minimization only approximately consistent
+$\rightarrow$ The Min-Max relevance model is due to the minimization only approximately consistent.
 \end{frame}
@@
 \vspace{0.1cm}
-$\rightarrow$ The training-free relevance model is consistent\\
+$\rightarrow$ The training-free relevance model is consistent.\\
 
 \vspace{0.5cm}
-When using the training-free model for the whole network all but the first layer need to be decomposed using the $z^+$-rule
+When using the training-free model for the whole network, all but the first layer need to be decomposed using the $z^+$-rule.
 \end{frame}

### 2022-06-30 PythonFiles/taylor_decomposition_presentation.py

@@ -9,6 +9,48 @@ from PythonFiles.dataReading import data_reading_transformation
 from PythonFiles.omega_squared import omega_squared
 from PythonFiles.Neural_Network import NN
 
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+#%%
 # preprocess data
 x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(path_url = "data/titanic", minmaxscaler = True, withID = True)
 

### 2022-07-03 paper/paper_marcel_pommer.tex
more algorithms

@@
 introduce in their paper \textit{Explaining NonLinear Classification Decisions with Deep Taylor Decompositions} \cite{Montavon.2017b} a new technique, the deep Taylor decomposition, to map the relevance of the output on the input features, i.e.
-quantify the influence of each input variable on the output.
-They demonstrate the results on two image recognition data sets, the MNIST \cite{lecun2010mnist} and the ILSVRC \cite{Russakovsky.2015}, creating heatmaps to display the relevance of each single pixel.
-I recreate the procedure in Python and apply the deep Taylor decomposition to the titanic dataset \cite{Eaton.1998}.
+quantify the influence of each input feature on the output.
+They demonstrate the results on two image classification data sets, the MNIST \cite{lecun2010mnist} and the ILSVRC \cite{Russakovsky.2015}, creating heatmaps to display the relevance of each single pixel.
+I recreate one of the proposed propagation rules in Python and apply the deep Taylor decomposition to the titanic dataset \cite{Eaton.1998}.
 \end{abstract}
@@
 \vspace{-0.15cm}
-This property ensures, that relevance cannot be negative in the sense that two pixels cancel each other out.
+This property ensures, that two pixels cannot cancel each other out or that a pixel contradicts the classification decision of the neural network.
 Since definition \ref{thm:conservative} and definition \ref{thm:positive} are of essence for the evaluation of models we further define:
@@
 where $\mathbb{X}$ is the input domain.\\
-Next we focus on the deep Taylor decomposition, where we consider the mapping of neurons in one layer to each neuron in the next layer, assuming a relation explainable by some relevance function $R_j(\{x_i\})$.
-If this assumption holds and we further identify a root point $\{\tilde{x}_i\}$ such that $R_j(\{\tilde{x}_i\})=0$ we apply the Taylor decomposition layer-wise:
+Next we focus on the deep Taylor decomposition, where we consider the mapping of neurons in one layer to each neuron in the next layer, instead of considering the whole neural network at once.
+Assuming there is a relation explainable by some relevance function $R_j(\{x_i\})$ and we further identify a root point $\{\tilde{x}_i\}$ such that $R_j(\{\tilde{x}_i\})=0$ we apply the Taylor decomposition layer-wise:
 \begin{align*}
@@
 If definition \ref{thm:consistent} holds for each local Taylor decomposition, the relevances is guaranteed to be conserved in each layer, i.e.
-$R_f=...=\sum_j R_j=...=\sum_p R_p$ and the relevance propagation rule is positive $R_f,...,\{R_j\},...\{R_p\} \geq 0$.\\
+$R_f=...=\sum_j R_j=...=\sum_p R_p$ and the relevance propagation rule is positive $R_f,...,\{R_j\},...,\{R_p\} \geq 0$.\\
 
@@
 \end{align*}
-If either $\sum_j\tilde{x}_j=0$ and $\forall j: \tilde{x}_j \geq0$ we need to chose $\{\tilde{x}_j\}=0$ resulting in $R_j = x_j$, since $\frac{\partial R_k}{\partial x_j} = 1$.
+We chose $\{\tilde{x}_j\}=0$ as a proper root point resulting in $R_j = x_j$, since $\frac{\partial R_k}{\partial x_j} = 1$.
 Redistributing the relevance to the next layer using the Taylor decomposition leads to
@@
 Considering an unconstrained input space we search the nearest root point in the Euclidean sense.
-The intersection of equation $\sum_i \tilde{x}_i^{(j)} w_{ij}+b_j=0$ (root point) and the line of maximum descent $\{\tilde{x}_i\}^{(j)}=\{x_i\} +t w_j$ ($w_j$ as gradient of $R_j$), where $w_j$ is the weight vector and $t \in \mathbb{R}$ defines the nearest root point which is then given by $\{\tilde{x}_i\}^{(j)} = \{x_i - \frac{w_{ij}}{\sum_i w_{ij}^2}(\sum_i x_i w_{ij}+b_j)\}$.
-If we plug in $\{\tilde{x}_i\}^{(j)}$ in equation \ref{equ:propagationRule} we get the propagation rule for $R_i$
+The intersection of equation $\sum_i \tilde{x}_i^{(j)} w_{ij}+b_j=0$ (root point) and the line of maximum descent $\{\tilde{x}_i\}^{(j)}=\{x_i\} +t w_j$ ($w_j$ as gradient of $R_j$), where $w_j$ is the weight vector and $t \in \mathbb{R}$, defines the nearest root point which is then given by $\{\tilde{x}_i\}^{(j)} = \{x_i - \frac{w_{ij}}{\sum_i w_{ij}^2}(\sum_i x_i w_{ij}+b_j)\}$.
+If we plug in $\{\tilde{x}_i\}^{(j)}$ in equation \ref{equ:propagationRule} we get the $w^2$-propagation rule for $R_i$
 \begin{align*}
@@
 propose the segment $(\{x_i 1_{w_{ij}<0}\},\{x_i\})$, since we already know of the existence of one root point at the origin and thus the direction of the segment is given by $v_i^{(j)} = x_i - x_i 1_{w_{ij}<0} = x_i 1_{w_{ij}\geq0}$.
-If we follow the same logic as in section \ref{sec:wRule} but adjust the line of maximum descent to $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tx_i 1_{w_{ij}\geq0}$ we get the following relevance propagation rule
+If we follow the same logic as in section \ref{sec:wRule} but adjust the line of maximum descent to $\{\tilde{x}_i\}^{(j)}=\{x_i\} +tx_i 1_{w_{ij}\geq0}$ we get the $z^+$-propagation rule
 \begin{align*}
@@
 , where $R_k$ and $\hat{R}_k$ are the true and predicted relevances, we end up with the same problem as in section \ref{sec:main}.
-Due to the similar structure we can apply the same computations and derive $R_j = y_j$ and $R_i = \sum_j \frac{q_{ij}}{\sum_{i´}q_{i´j}} R_j$, where $q_{ij} \in \{w_{ij}^2, x_i w_{ij}1_{w_{ij}>0}\}$ for the $\omega^2$-rule and $z^+$-rule, respectively.
+Due to the similar structure we can apply the same computations and derive $R_j = y_j$ and $R_i = \sum_j \frac{q_{ij}}{\sum_{i´}q_{i´j}} R_j$, where $q_{ij} \in \{v_{ij}^2, x_i v_{ij}1_{v_{ij}>0}\}$ for the $\omega^2$-rule and $z^+$-rule, respectively.
 In contrast to the problem before the resulting heatmap is only approximately conservative, due to the possible errors during the minimization of  \ref{min:relevanceModel}.
@@
 correctly assigns relevance to areas where the digit is located.
-Further analysis shows, that especially the $\omega^2$- and $z$-rule are conservative and positive and thus satisfy comply with definition \ref{thm:consistent}.
+Further analysis shows, that especially the $\omega^2$- and $z^b$-rule are conservative and positive and thus comply with definition \ref{thm:consistent}.
 \begin{figure}[ht]
@@
 Table 1 summarizes the results  for a (very young) passenger which was classified as surviver.
-The numbers clearly show, that th age has a huge influence on the survival probability, but features like the passenger ID does not.\footnote{Code can be found on: \url{https://github.com/mpommer/Deep-Taylor-Decomposition-Python}}
+The numbers clearly show, that the age has a huge influence on the survival probability, but features like the passenger ID does not.\footnote{Code can be found on: \url{https://github.com/mpommer/Deep-Taylor-Decomposition-Python}}
 \vspace{-0.5cm}
@@
 \label{sec:conclusions}
-The increasing popularity of machine learning and, with it, complex deep neural networks raised the question of explainability, amongst others on context of legal questions for self driving cars or in pricing for insurance.
+The increasing popularity of machine learning and, with it, complex deep neural networks raised the question of explainability, amongst others in the context of legal questions for self driving cars or insurance pricing.
 Montavon et al.

### 2022-07-03 PythonFiles/Neural_Network.py

@@ -13,7 +13,7 @@ import pandas as pd
 seed = 12345
 
 
-class NonNeg(tf.keras.constraints.Constraint):
+class NonPos(tf.keras.constraints.Constraint):
   """Constrains weight tensors to be centered around `ref_value`."""
 
   def __init__(self):
@@ -38,7 +38,11 @@ class NN:
         tf.random.set_seed(seed)
 
         model = keras.Sequential()
-        model.add(Dense(neurons[0], input_dim=self.x_train.shape[1], activation = "ReLU", bias_constraint=NonNeg()))
+        model.add(Dense(neurons[0], input_dim=self.x_train.shape[1], activation = "ReLU", bias_constraint=NonPos()))
+        if layers>1:
+            for layers in range(layers-1):
+                model.add(Dense(neurons[layers+1], input_dim=neurons[layers], activation = "ReLU", bias_constraint=NonPos()))
+
 
         # for l in range(layers):
         #     model.add(Dense(neurons[l], input_dim=self.x_train.shape[1], activation = "ReLU", bias_constraint=NonNeg()))

### 2022-07-03 PythonFiles/explainability_abstract_class.py

@@ -70,6 +70,24 @@ class explainability(metaclass=abc.ABCMeta):
         else:
             print("The model is not consistent!")
             
+    def getInput_activation(self):
+        dic = {}
+        dic["0_layer"]= self.input_vector
+        
+        input_array = self.input_vector
+        for layer in np.arange(1,len(self.model.layers)+1):
+            weights = self.model.layers[layer-1].weights[0].numpy()
+            bias = self.model.layers[layer-1].weights[1].numpy()
+            
+            output = np.matmul(input_array,weights)+bias
+            output = np.array([max(0,x) for x in output])
+            dic[f"{layer}_layer"]=output
+            
+            input_array = output
+            
+            
+        self.dic = dic
+            
             
     
     

### 2022-07-03 PythonFiles/omega_squared.py

@@ -12,9 +12,16 @@ class omega_squared(explainability):
     def fit(self):
         # from first layer to output
         self.getInput_activation()
-        R_j = self.dic["1_layer"]
         
-        R_i = self.omegaRule(R_j, self.model.layers[0].weights[0].numpy())
+        layers = len(self.model.layers)
+        
+        # for the last hidden layer
+        R_j = self.dic[f"{layers-1}_layer"]
+        
+        for layer in np.arange(layers-2,-1,-1):
+            
+            R_i = self.omegaRule(R_j, self.model.layers[layer].weights[0].numpy())
+            R_j = R_i
             
         return R_i
     
@@ -24,63 +31,7 @@ class omega_squared(explainability):
         
         return np.matmul(n, R_j)
         
-        # summe = sum(weights**2)
-        # for in_neuron_index, inputs in enumerate(weights):
-        #     R_i = 0
-        #     for out_neuron_index, weight in enumerate(inputs):
-        #         weight_squared = weight**2
-        #         weight_sum = summe[out_neuron_index]
-        #         R_i += weight_squared/weight_sum*R_j[out_neuron_index]
-            
-            
-        #     input_relevance.append(R_i)
-            
-        # return input_relevance
-    
-    def getInput_activation(self):
-        dic = {}
-        dic["0_layer"]= self.input_vector
-        
-        input_array = self.input_vector
-        for layer in np.arange(1,len(self.model.layers)+1):
-            weights = self.model.layers[layer-1].weights[0].numpy()
-            bias = self.model.layers[layer-1].weights[1].numpy()
-            
-            output = np.matmul(input_array,weights)+bias
-            output = np.array([max(0,x) for x in output])
-            dic[f"{layer}_layer"]=output
-            
-            input_array = output
-            
-            
-        self.dic = dic
     
     
-    # def fit(self):
-    #     number_layers = len(self.model.layers)
-        
-        
-    #     output = self.result
-    #     for layer in np.arange(number_layers-1, -1, -1):
-    #         output = self.omegaRule(output, self.model.layers[layer].weights[0].numpy())
-            
-    #     return output
-    
-    # def omegaRule(self, R_j, weights):
-    #     input_relevance = []
-        
-    #     summe = sum(weights**2)
-    #     for in_neuron_index, inputs in enumerate(weights):
-    #         R_i = 0
-    #         for out_neuron_index, weight in enumerate(inputs):
-    #             weight_squared = weight**2
[…]

### 2022-07-03 PythonFiles/taylor_decomposition_presentation.py

@@ -9,54 +9,13 @@ from PythonFiles.dataReading import data_reading_transformation
 from PythonFiles.omega_squared import omega_squared
 from PythonFiles.Neural_Network import NN
 
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-#%%
 # preprocess data
-x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(path_url = "data/titanic", minmaxscaler = True, withID = True)
+x_train, y_train, x_test, y_test, feature_name = data_reading_transformation(path_url = "data/titanic", minmaxscaler = False, withID = True)
 
 # build the neural network
 neural_network = NN(x_train, y_train)
-neural_network.fit(layers = 1, neurons = [5]*1, verbose = 0)
+hidden_layers = 2
+neural_network.fit(layers = hidden_layers, neurons = [10]*hidden_layers, verbose = 0)
 
 # print test results
 neural_network.testResult(x_test,y_test)
@@ -80,4 +39,33 @@ relevance = taylor_decomposition.fit()
 taylor_decomposition.printExplainability(feature_name)
 
 
+#%%
 
+from PythonFiles.z_rule import z_rule
+
+# #%%choose passenger and create taylor decomposition
+passenger = 89
+z_ru = z_rule(model, prediction[passenger], x_test[passenger])
+        
+relevance = z_ru.fit()
+        
+        
+z_ru.printExplainability(feature_name)
+
+
+
+#%%
+
+from PythonFiles.z_plusrule import z_plus_rule
+
+# #%%choose passenger and create taylor decomposition
+passenger = 89
+z_ru = z_plus_rule(model, prediction[passenger], x_test[passenger])
+        
+relevance = z_ru.fit()
+        
+        
+z_ru.printExplainability(feature_name)
+
+z_ru.isConservative()
+z_ru.isPositive()

### 2022-07-03 PythonFiles/z_plusrule.py

@@ -1,10 +1,13 @@
 # -*- coding: utf-8 -*-
 """
-Created on Sat Jun 11 17:49:28 2022
+Created on Sat May  7 13:10:48 2022
 
-@author: marce
+@author: Marcel Pommer
 """
 
+import numpy as np
+from PythonFiles.explainability_abstract_class import explainability
+from tensorflow.keras import backend as K
 # -*- coding: utf-8 -*-
 """
 Created on Sat May  7 13:10:48 2022
@@ -16,72 +19,35 @@ import numpy as np
 from PythonFiles.explainability_abstract_class import explainability
 from tensorflow.keras import backend as K
 
-class z_plusrule(explainability):
-    
-    def __init__(self, model, result, input_vector):
-        self.model = model
-        self.result = result
-        self.input_vector = input_vector
+class z_plus_rule(explainability):
         
     def fit(self):
         self.getInput_activation()
-        number_layers = len(self.model.layers)
+        layers = len(self.model.layers)
         
-       
-        output = self.result
-        for layer in np.arange(number_layers-1, -1, -1):
-            layer_output = self.dic[f"{layer}_layer"]
-            output = self.z_Rule(output, self.model.layers[layer].weights[0].numpy(), layer_output)
+        # for the last hidden layer
+        R_j = self.dic[f"{layers-1}_layer"]
+        
+        for layer in np.arange(layers-2,-1,-1):
+            X_i = self.dic[f"{layer}_layer"]
             
-        return output
+            R_i = self.z_Rule(R_j, self.model.layers[layer].weights[0].numpy(), X_i)
+            R_j = R_i
+            
+        return R_i
     
-   
-    # def z_Rule(self, R_j, weights,layer_output):
-    #     try:
-    #         R_j = [x[0] for x in R_j]
-    #     except:
-    #         pass
-        
-    #     for index in range(len(weights)):
-    #         weights[index]*=layer_output[index]
-            
-    #     sums = weights.sum(axis=1)
-
-    #     for index in range(len(weights)):
-    #         weights[index]/=sums[index]  
-    #         weights[np.isnan(weights)] = 0
-    #         weights[index]*=R_j
-        
-    #     output = weights.sum(axis=1)
-        
-    #     return output
     
     def z_Rule(self, R_j, weights,layer_output):
-        
         weights[weights<0] = 0
+        
         z =  np.matmul(weights.T,layer_output)
         
         weights_times_relevenace_div_z = np.matmul(weights,R_j/z)
         
[…]

### 2022-07-03 PythonFiles/z_rule.py

@@ -13,36 +13,19 @@ class z_rule(explainability):
         
     def fit(self):
         self.getInput_activation()
-        number_layers = len(self.model.layers)
+        layers = len(self.model.layers)
         
-       
-        output = self.result
-        for layer in np.arange(number_layers-1, -1, -1):
-            layer_output = self.dic[f"{layer}_layer"]
-            output = self.z_Rule(output, self.model.layers[layer].weights[0].numpy(), layer_output)
+        # for the last hidden layer
+        R_j = self.dic[f"{layers-1}_layer"]
+        
+        for layer in np.arange(layers-2,-1,-1):
+            X_i = self.dic[f"{layer}_layer"]
             
-        return output
+            R_i = self.z_Rule(R_j, self.model.layers[layer].weights[0].numpy(), X_i)
+            R_j = R_i
+            
+        return R_i
     
-   
-    # def z_Rule(self, R_j, weights,layer_output):
-    #     try:
-    #         R_j = [x[0] for x in R_j]
-    #     except:
-    #         pass
-        
-    #     for index in range(len(weights)):
-    #         weights[index]*=layer_output[index]
-            
-    #     sums = weights.sum(axis=1)
-
-    #     for index in range(len(weights)):
-    #         weights[index]/=sums[index]  
-    #         weights[np.isnan(weights)] = 0
-    #         weights[index]*=R_j
-        
-    #     output = weights.sum(axis=1)
-        
-    #     return output
     
     def z_Rule(self, R_j, weights,layer_output):
         
@@ -50,25 +33,8 @@ class z_rule(explainability):
         
         weights_times_relevenace_div_z = np.matmul(weights,R_j/z)
         
-        times_layer_output = [x*y for (x,y) in zip(layer_output, weights_times_relevenace_div_z)]
+        times_layer_output = layer_output*weights_times_relevenace_div_z
                     
         return times_layer_output
     
-    def getInput_activation(self):
-        dic = {}
-        dic["0_layer"]= self.input_vector
-        
-        input_array = self.input_vector
-        for layer in np.arange(1,len(self.model.layers)+1):
-            weights = self.model.layers[layer-1].weights[0].numpy()
-            bias = self.model.layers[layer-1].weights[1].numpy()
-            
-            output = np.matmul(input_array,weights)+bias
-            output = np.array([max(0,x) for x in output])
-            dic[f"{layer}_layer"]=output
-            
-            input_array = output
-            
-            
-        self.dic = dic
         
